### 2020-01-29 sourceSummaries.tex
initial source summary framework

\documentclass[a4paper,12pt]{article}
\begin{document}
    \title{Source Summaries}
    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
    Daniel Capps, Jacob Ruud}
    \date{\today}
    \maketitle

\noindent
\textbf{Citation:}

\noindent
@article\{filizzola2018security,

title=\{Security Analysis of Bluetooth Technology\},

author=\{Filizzola, Daniel and Fraser, Sean and Samsonau, Nikita\},

year=\{2018\},

organization=\{MIT\}

\noindent
\}

\vspace{5mm}
\noindent
\textbf{Main Idea:}

\noindent
Enter main idea paragraph here.

\vspace{5mm}
\noindent
\textbf{Theory:}

\noindent
Enter Theory paragraph here.

\vspace{5mm}   
\noindent
\textbf{Findings:}

\noindent
Enter findings paragraph here

\vspace{5mm}  
\noindent
\textbf{Directions:}

\noindent
Enter directions paragraph here

\end{document}

### 2020-01-29 sourceSummaries.tex
Update sourceSummaries.tex

@@
     \maketitle
+\break
+\tableofcontents
+\break
 
+\break
 \noindent
-\textbf{Citation:}
+\section{Filizzola 2018 Security}
+\subsection{Citation}
 
@@
 
-\vspace{5mm}
-\noindent
-\textbf{Main Idea:}
+\subsection{Main Idea}
 
 \noindent
-Enter main idea paragraph here.
+The authors detail the security methods used in Bluetooth versions 4.X, attempt to show attacks that bypass these methods, and describe ways to harden Bluetooth security against these attacks.
 
-\vspace{5mm}
-\noindent
-\textbf{Theory:}
+\subsection{Theory}
 
 \noindent
-Enter Theory paragraph here.
+Game Theory is the primary theory being tested in this article.
+The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
 
-\vspace{5mm}   
-\noindent
-\textbf{Findings:}
+\subsection{Method}
 
 \noindent
-Enter findings paragraph here
+The researchers theorized and tested primary attacks against the Bluetooth security model: Active Eavesdropping and Passive Eavesdropping.
+Their attacks built upon the works by Da-Zhi Sun et al., Cope et a., Das et al., and Ryan.
+The assets used were a Raspberry Pi running Debian, an Ubertooth, TaoTronics TT-BH07 Bluetooth Headphones, a Logitech MX Master Mouse, and a Galazy S7 Edge.
+The authors modified existing Bluetooth utilities for their attacks and wrote some scripts of their own.
 
-\vspace{5mm}  
-\noindent
-\textbf{Directions:}
+\subsection{Findings}
 
 \noindent
-Enter directions paragraph here
+The authors managed to exploit their theorized vulnerabilities successfully.
+They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
+The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
+They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
+
+\subsection{Future Directions}
+
+\noindent
+The future directions for Active Eavesdropping is to expand and cover more than JustWorks devices, this would include attacks against mice and keyboards.
+The next steps for Passive Easedropping is to use the extrapolated information to decrypt packets for further analysis and to attack other devices like keyboards and medical implants, this can be used to gather sensitive information like passwords and health data.
+They also stated that they could combine the two attack types to inject malicious packets or modify existing ones for other attacks against the devices.
+Finally, they could also do research on the vulnerabilities in Bluetooth 5.0.
 

### 2020-01-31 sourceSummaries.tex
Don't know what I did but it compiles now
updated some styling and my reference
Fixed bibliography/table of contents interaction
Fixed uneven margins
Couple more formatting changes
Added Joshua\'s first source summary

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[letterpaper,12pt]{article}
+\usepackage{natbib}
+\usepackage{bibentry}
+\usepackage[hyphens]{url}
+\usepackage[numbib]{tocbibind}
+\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
+
+\bibliographystyle{plainnat}
+
 \begin{document}
+	\nobibliography*
+
     \title{Source Summaries}
@@
 
-\break
 \noindent
@@
 \noindent
-@article\{filizzola2018security,
 
-title=\{Security Analysis of Bluetooth Technology\},
-
-author=\{Filizzola, Daniel and Fraser, Sean and Samsonau, Nikita\},
-
-year=\{2018\},
-
-organization=\{MIT\}
-
-\noindent
-\}
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{filizzola2018security}
 
@@
 
+\Urlmuskip=0mu plus 1mu\relax
+
+\pagebreak
+
+\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}
+
+\noindent
+
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{8622000}
+
+\subsection{Main Idea}
+
+\noindent
+The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.
+The researchers also look at several BLE devices to analyze their security models.
+\subsection{Theory}
+
+\noindent
+Game Theory is the primary theory being tested in this article.
+The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
+
+\subsection{Method}
+
+\noindent
+The researchers found that many modern fitness trackers use older versions of Bluetooth low energy.
+They also found that these fitness trackers often do not enable optional features that make bluetooth much more secure.
+As a result, most of the encryption was trivial to decrypt.
+The researchers then created an app that uses the Bluetooth sniff log functionality present in the developer section in Android to extract the security features of a bluetooth low energy device.
+
+\subsection{Findings}
+
+\noindent
+The authors managed to exploit their theorized vulnerabilities successfully.
+They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
+The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
+They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
+
+\subsection{Future Directions}
+
+\noindent
+The authors want to make their app much more usable to the average consumer.  Right now it's very oriented toward technical-minded researchers.
+
+\bibliography{references}
+
 \end{document}

### 2020-02-01 sourceSummaries.tex
Fixed a subsection header
hi im clev and I'm too lazy to make a branch

@@
 \noindent
-
+\subsection{Citation}
 \Urlmuskip=0mu plus 1mu\relax
@@
 
+\pagebreak
+
+\section{Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks}
+
+\noindent
+\subsection{Citation}
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{8622000}
+
+\subsection{Main Idea}
+
+\noindent
+The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
+\subsection{Theory}
+
+\noindent
+Game theory is being utilized to test the security of the lock and see where the vulnerabilities in the lock lie.
+
+\subsection{Method}
+
+\noindent
+A threat rating system following the DREAD model is created to accurately represent the threat of the lock.
+Three threat models were created: unauthorized lock access, avoidance of logging, and denial of service.
+A Bluetooth man in the middle attack is carried out to gather information about the lock’s Generic Attribute Profile (GATT), how connections are formed, hosted services, and other characteristics of the lock.
+Using the GATT, a fake lock can be created to connect to the application, and then forward all information onto the actual lock.
+Next, access permission edge cases are tested to see when access can be abused to bypass controls.
+The app was reversed to gather further insight on how the app connected to the lock.
+
+\subsection{Findings}
+
+\noindent
+Not much was able to be done in the way of breaking into the lock.
+Some patterns were found in the communication scheme, but nothing to indicate how the data was being encrypted.
+A replay attack was launched, but this was ineffective.
+Fuzzing was similarly ineffective.
+If an attacker is granted permission to access the lock, disconnects their internet, and then their permission is revoked, the attacker can still access the lock.
+In the app, a possible encryption key for a database was found, but not pursued.
+
+\subsection{Future Directions}
+
+\noindent
+The authors would like to see a more structured method developed to analyze the security of Bluetooth devices, as many of the approaches they took were very time consuming.
+
 \bibliography{references}

### 2020-02-02 sourceSummaries.tex
Changed bibentry
Fixed error's in people's code, it now compiles correctly
Fixed overfull hbox issue

@@
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
+\include{references.bib}
 
@@
 \noindent
-\section{Filizzola 2018 Security}
-\subsection{Citation}
+\section{Security Analysis of Bluetooth Technology}
 
 \noindent
+\subsection{Citation}
 
@@
 
-\pagebreak
-
 \section{Extracting the Security Features Implemented in a Bluetooth LE Connection}
@@
 \noindent
+\subsection{Group member}
+Joshua Niemann
 \subsection{Citation}
+
 \Urlmuskip=0mu plus 1mu\relax
@@
 The researchers also look at several BLE devices to analyze their security models.
+
 \subsection{Theory}
@@
 Game Theory is the primary theory being tested in this article.
-The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
+The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.
+In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.
 
@@
 
-\pagebreak
-
-\section{Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks}
+\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
 
@@
 \subsection{Citation}
+
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{8622000}
+\bibentry{KTH}
 
@@
 The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
+
 \subsection{Theory}
@@
 
+\pagebreak
+
 \bibliography{references}

### 2020-02-02 sourceSummaries.tex
added summary for my source as well as updated references document

@@
 \noindent
-\subsection{Group member}
-Joshua Niemann
 \subsection{Citation}
@@
 Game Theory is the primary theory being tested in this article.
-The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.
-In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.
+The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
 
@@
 
+\section{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
+
+\noindent
+\subsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{rose_2017}
+
+\subsection{Main Idea}
+
+\noindent
+In his thesis, Captian Rose attemps to provide the industry with a wholistic look on the security of the low energy bluetooth protocol.
+He uses four different methods in an attempt to cover a wide range of conigurations and scenarios to really put this protocol to the test.
+
+\subsection{Theory}
+
+\noindent
+Game Theory is the primary theory being tested in this article.
+Captain Rose proposes multiple different scenarios where the bluetooth protocol is vulnerable in order to better understand how to secure it in the future.
+
+\subsection{Method}
+
+\noindent
+Captain Rose and his supporters used multiple different methods to test the strength and security of the Bluetooth protocol.
+First, he used a benchmark open-source range-finding tool to determine the location of Bluetooth devices through a novel distance estimation method, increasing the state-of-the-art device location distance from 50 meters up to 1,000 meters.
+Second, he evaluated 17 individual Bluetooth Low Energy devices for vulnerabilities in their operating system.
+Thirdly, he used user behavior analytics to demonstrate how malicious actors can exploit vulnerabilities for unauthorized device access and obtain sensitive information
+
+\subsection{Findings}
+
+\noindent
+Captain Rose's research revealed that 13 out of 17 (75 percent) of the tested devices contained at least one vulnerability resulting in unauthorized access.
+However, he did find that countermeasures to BLE attacks already exist and most require minimum implementation and development by manufacturers.
+More complex mediation techniques exist for issues that are not solved by the initial mediation techniques.
+
+\subsection{Future Directions}
+
+\noindent
+Since Captain Rose's work was done on an outdated bluetooth protocol (4.1) he mentions that there is room for others or himself to do research on devices implementing the newest protocol.
+He also recommends research into newly release bluetooth devices such as Lockitron or Schlage.
+He also states that he did not do any work with the firmware of the devices he tested so there is room for others to continue his work there.
+Along with that, he states that no research was done on attempting to clone the devices that he was testing, so there is more work to be done there.
+
 \pagebreak

### 2020-02-03 sourceSummaries.tex
I hope this works

@@
 \noindent
+\subsection{Group member}
+Joshua Niemann
 \subsection{Citation}
@@
 
+\noindent
+\section{Security Vulnerabilities in Bluetooth Technology as used in IoT}
+
+\noindent
+\subsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{lonzetta2018security}
+
+\subsection{Main Idea}
+
+\noindent
+This study is about understanding Bluetooth and Iot(Internet of Things) devices.
+They go in depth on the importance of understanding Bluetooth, the differet attacks possible against Bluetooth and IoT devices, and how to mitigate these attacks using different tequniques.
+
+\subsection{Theory}
+
+\noindent
+Game Theory is the primary theory being used in this article.
+The authors gathered information about many vulnerabilities and exploits in Bluetooth/Iot and determined different mitigation tequniques for each of them.
+
+\subsection{Method}
+
+\noindent
+The researchers explained the inner workings of IoT and Bluetooth and then gathered different information on attacks to Bluetooth and Iot.
+Then, by using the information they found they determined different risk mitigation tequniques for users of Bluetooth and IoT devices.
+
+\subsection{Findings}
+
+\noindent
+The authors presented multiple vulnerabilities and attacks against Bluetooth and IoT and risk mitigations to combat them, the most notable of them being more awareness from the user's perspective on security issue with bluetooth.
+The main attacks showcased here are PIN Cracking, Man-in-the-M(MITM), BlueJacking, BlueBorne, Fuzzing, Reflection/Relay, Backdoor, Denial of Service(DOS).
+Many more attacks are mention as well.
+
+\subsection{Future Directions}
+
+\noindent
+Can the analysis tequniques use here be used for any other wireless standard?
+Could there be an attack on BLE that has to do with power consumtion?
+What methods can we use to more properly inform users of the risks of IoT and Bluetooth so that they may mitigate said risks?
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-04 utilities/travis_setup.sh
adding travis ci

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+ # setup script to install texlive and add to path
+ texlive_year="2020"
+
+ sudo apt-get -qq update
+ export PATH=/tmp/texlive/bin/x86_64-linux:$PATH
+
+ if ! command -v pdflatex > /dev/null; then
+     echo "Texlive not installed"
+     echo "Downloading texlive and installing"
+     wget http://mirror.ctan.org/systems/texlive/tlnet/install-tl-unx.tar.gz
+     tar -xzf install-tl-unx.tar.gz
+     ./install-tl-*/install-tl --profile=./utilities/texlive.profile
+
+     echo "Finished install TexLive"
+ fi
+
+ echo "Now updating TexLive"
+ # update texlive
+ tlmgr option -- autobackup 0
+ tlmgr update --self --all --no-auto-install
+
+ echo "Finished updating TexLive"
+
+ echo "Download and setup texmf tree"
+ git clone https://github.com/skulumani/texmf.git ~/texmf

### 2020-02-04 utilities/travis_setup.sh
update to ci

@@ -1,27 +1,0 @@
-#!/bin/bash
-
- # setup script to install texlive and add to path
- texlive_year="2020"
-
- sudo apt-get -qq update
- export PATH=/tmp/texlive/bin/x86_64-linux:$PATH
-
- if ! command -v pdflatex > /dev/null; then
-     echo "Texlive not installed"
-     echo "Downloading texlive and installing"
-     wget http://mirror.ctan.org/systems/texlive/tlnet/install-tl-unx.tar.gz
-     tar -xzf install-tl-unx.tar.gz
-     ./install-tl-*/install-tl --profile=./utilities/texlive.profile
-
-     echo "Finished install TexLive"
- fi
-
- echo "Now updating TexLive"
- # update texlive
- tlmgr option -- autobackup 0
- tlmgr update --self --all --no-auto-install
-
- echo "Finished updating TexLive"
-
- echo "Download and setup texmf tree"
- git clone https://github.com/skulumani/texmf.git ~/texmf

### 2020-02-05 sourceSummaries.tex
Repaired Daniel's section and recompiled
Added Group Member Blockx
fixed ToC

--- 2020-02-02 sourceSummaries.tex
@@
 
-\noindent
-\section{Security Analysis of Bluetooth Technology}
+\section{Week 3}
 
 \noindent
-\subsection{Citation}
+\subsection{Security Analysis of Bluetooth Technology}
+
+\noindent
+\subsubsection{Citation}
 
@@
 
-\subsection{Main Idea}
+\subsubsection{Main Idea}
 
@@
 
-\subsection{Theory}
+\subsubsection{Theory}
 
@@
 
-\subsection{Method}
+\subsubsection{Method}
 
@@
 
-\subsection{Findings}
+\subsubsection{Findings}
 
@@
 
-\subsection{Future Directions}
+\subsubsection{Future Directions}
 
@@
 
-\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}
+\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}
 
 \noindent
-\subsection{Citation}
+\subsubsection{Group member}
+Joshua Niemann
+\subsubsection{Citation}
 
@@
 Game Theory is the primary theory being tested in this article.
-The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
+The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.
+In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.
 
-\subsection{Method}
+\subsubsection{Method}
 
@@
 
-\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
+\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
 
 \noindent
-\subsection{Citation}
+\subsubsection{Citation}
 
@@
 
-\section{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
+\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
 
 \noindent
-\subsection{Citation}
+\subsubsection{Citation}
 

### 2020-02-05 sourceSummaries.tex

--- 2020-02-03 sourceSummaries.tex
@@
 \break
-\tableofcontents
+\setcounter{tocdepth}{2}\tableofcontents
 \break
 
-\noindent
-\section{Security Analysis of Bluetooth Technology}
+\section{Week 3}
 
 \noindent
-\subsection{Citation}
+\subsection{Security Analysis of Bluetooth Technology}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
 
@@
 
-\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}
+\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}
 
 \noindent
-\subsection{Group member}
+\subsubsection{Group member}
 Joshua Niemann
-\subsection{Citation}
+
+\subsubsection{Citation}
 
@@
 
-\section[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
+\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
+
+\subsubsection{Group Member}
 
 \noindent
-\subsection{Citation}
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
 
@@
 
-\section{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
+\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
+
+\subsubsection{Group Member}
 
 \noindent
-\subsection{Citation}
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
 
@@
 \noindent
-\section{Security Vulnerabilities in Bluetooth Technology as used in IoT}
+\subsection{Security Vulnerabilities in Bluetooth Technology as used in IoT}
+
+\subsubsection{Group Member}
 
 \noindent
-\subsection{Citation}
+Daniel Capps
+
+\noindent
+\subsubsection{Citation}
 

### 2020-02-06 paper/sourceSummaries/summary2.tex
folder build

--- 2020-02-05 sourceSummaries.tex
@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{natbib}
-\usepackage{bibentry}
-\usepackage[hyphens]{url}
-\usepackage[numbib]{tocbibind}
-\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
-\include{references.bib}
-
-\bibliographystyle{plainnat}
-
-\begin{document}
-	\nobibliography*
-
-    \title{Source Summaries}
-    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
-    Daniel Capps, Jacob Ruud}
-    \date{\today}
-    \maketitle
-\break
-\tableofcontents
-\break
-
-\section{Week 3}
+\section{Summary 2}
 
 \noindent
-\subsection{Security Analysis of Bluetooth Technology}
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Name of member
 
@@
 \noindent
-The authors detail the security methods used in Bluetooth versions 4.X, attempt to show attacks that bypass these methods, and describe ways to harden Bluetooth security against these attacks.
+Main Idea
 
@@
 \noindent
-Game Theory is the primary theory being tested in this article.
-The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
+Theory
 
@@
 \noindent
-The researchers theorized and tested primary attacks against the Bluetooth security model: Active Eavesdropping and Passive Eavesdropping.
-Their attacks built upon the works by Da-Zhi Sun et al., Cope et a., Das et al., and Ryan.
-The assets used were a Raspberry Pi running Debian, an Ubertooth, TaoTronics TT-BH07 Bluetooth Headphones, a Logitech MX Master Mouse, and a Galazy S7 Edge.
-The authors modified existing Bluetooth utilities for their attacks and wrote some scripts of their own.
+Method
 
@@
 \noindent
-The authors managed to exploit their theorized vulnerabilities successfully.
-They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
-The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
-They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
+Findings
 
@@
 \noindent
-The future directions for Active Eavesdropping is to expand and cover more than JustWorks devices, this would include attacks against mice and keyboards.
-The next steps for Passive Easedropping is to use the extrapolated information to decrypt packets for further analysis and to attack other devices like keyboards and medical implants, this can be used to gather sensitive information like passwords and health data.
-They also stated that they could combine the two attack types to inject malicious packets or modify existing ones for other attacks against the devices.
-Finally, they could also do research on the vulnerabilities in Bluetooth 5.0.
+Future Directions
 
@@
 
-\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}
-
-\noindent
-\subsubsection{Group member}
-Joshua Niemann
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{8622000}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.
-The researchers also look at several BLE devices to analyze their security models.
-
-\subsubsection{Theory}
-
-\noindent
-Game Theory is the primary theory being tested in this article.
-The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.
-In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.
-
-\subsubsection{Method}
-
-\noindent
-The researchers found that many modern fitness trackers use older versions of Bluetooth low energy.
-They also found that these fitness trackers often do not enable optional features that make bluetooth much more secure.
-As a result, most of the encryption was trivial to decrypt.
-The researchers then created an app that uses the Bluetooth sniff log functionality present in the developer section in Android to extract the security features of a bluetooth low energy device.
-
-\subsubsection{Findings}
-
-\noindent
-The authors managed to exploit their theorized vulnerabilities successfully.
-They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
-The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
-They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
-
-\subsubsection{Future Directions}
-
-\noindent
-The authors want to make their app much more usable to the average consumer.  Right now it's very oriented toward technical-minded researchers.
-
-\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{KTH}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
-
-\subsubsection{Theory}
-
-\noindent
-Game theory is being utilized to test the security of the lock and see where the vulnerabilities in the lock lie.
-
-\subsubsection{Method}
-
-\noindent
-A threat rating system following the DREAD model is created to accurately represent the threat of the lock.
-Three threat models were created: unauthorized lock access, avoidance of logging, and denial of service.
-A Bluetooth man in the middle attack is carried out to gather information about the lock’s Generic Attribute Profile (GATT), how connections are formed, hosted services, and other characteristics of the lock.
-Using the GATT, a fake lock can be created to connect to the application, and then forward all information onto the actual lock.
-Next, access permission edge cases are tested to see when access can be abused to bypass controls.
-The app was reversed to gather further insight on how the app connected to the lock.
-
-\subsubsection{Findings}
-
-\noindent
-Not much was able to be done in the way of breaking into the lock.
-Some patterns were found in the communication scheme, but nothing to indicate how the data was being encrypted.
-A replay attack was launched, but this was ineffective.
-Fuzzing was similarly ineffective.
-If an attacker is granted permission to access the lock, disconnects their internet, and then their permission is revoked, the attacker can still access the lock.
-In the app, a possible encryption key for a database was found, but not pursued.
-
-\subsubsection{Future Directions}
-
-\noindent
-The authors would like to see a more structured method developed to analyze the security of Bluetooth devices, as many of the approaches they took were very time consuming.
-
-\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{rose_2017}
-
-\subsubsection{Main Idea}
-
-\noindent
-In his thesis, Captian Rose attemps to provide the industry with a wholistic look on the security of the low energy bluetooth protocol.
-He uses four different methods in an attempt to cover a wide range of conigurations and scenarios to really put this protocol to the test.
-
-\subsubsection{Theory}
-
-\noindent
-Game Theory is the primary theory being tested in this article.
-Captain Rose proposes multiple different scenarios where the bluetooth protocol is vulnerable in order to better understand how to secure it in the future.
-
-\subsubsection{Method}
-
-\noindent
-Captain Rose and his supporters used multiple different methods to test the strength and security of the Bluetooth protocol.
-First, he used a benchmark open-source range-finding tool to determine the location of Bluetooth devices through a novel distance estimation method, increasing the state-of-the-art device location distance from 50 meters up to 1,000 meters.
-Second, he evaluated 17 individual Bluetooth Low Energy devices for vulnerabilities in their operating system.
-Thirdly, he used user behavior analytics to demonstrate how malicious actors can exploit vulnerabilities for unauthorized device access and obtain sensitive information
-
-\subsubsection{Findings}
-
-\noindent
-Captain Rose's research revealed that 13 out of 17 (75 percent) of the tested devices contained at least one vulnerability resulting in unauthorized access.
-However, he did find that countermeasures to BLE attacks already exist and most require minimum implementation and development by manufacturers.
-More complex mediation techniques exist for issues that are not solved by the initial mediation techniques.
-
-\subsubsection{Future Directions}
-
-\noindent
-Since Captain Rose's work was done on an outdated bluetooth protocol (4.1) he mentions that there is room for others or himself to do research on devices implementing the newest protocol.
-He also recommends research into newly release bluetooth devices such as Lockitron or Schlage.
-He also states that he did not do any work with the firmware of the devices he tested so there is room for others to continue his work there.
-Along with that, he states that no research was done on attempting to clone the devices that he was testing, so there is more work to be done there.
-
 \pagebreak
-
-\bibliography{references}
-
-\end{document}

### 2020-02-09 paper/sourceSummaries/summary2.tex
added summary 2

@@
 \noindent
-\subsection{Title}
+\subsection{Wiegand Protocol Access: A Decade of Decryption}
 
@@
 \noindent
-Name of member
+Quintin Walters
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
+%remove % to show citation, change the name to your entry
+\bibentry{chung2017wiegand}
 
@@
 \noindent
-Main Idea
+Brandon Chung covers what the Wiegand Protocol is, the historic vulnerabilities and hacks, what vulnerabilities still exist, and how to protect yourself against them.
+He spends a large amount of time on the historic attacks because most of them are still applicable, the protocol has not been hardened against them and as a result it is still very easy to exploit.
 
@@
 \noindent
-Theory
+Chung applies Game Theory in his work, he treats the security of the Wiegand Protocol as a zero sum game in which any method of bypass is a loss for the defenders.
+He highlights historic vulnerabilities of the protocol that are still in existence to reinforce this belief.
 
@@
 \noindent
-Method
+The author primarily presents the findings of others, he does little original research of his own.
+However, he does use an Arduino device to attack an unnamed Wiegand RFID reader.
+He connects his Arduino device to the Wiegand DATA 0 and DATA 1 wires, then he uses monkeyboard's "Wiegand Protocol Library for Arduino" to verify that the inherent vulnerabilities in the protocol still exist.
+Chung provides instructions and sample code for readers to attempt this on their own devices.
+This attack is the basis of the attacks done by Bernard Mehl (2015) and Zac Franken (2007), two attacks that Chung wrote in depth about.
 
@@
 \noindent
-Findings
+Brandon Chung found that Wiegand devices are still vulnerable to decade old attacks.
+These attacks have been extensively documented and Chung duplicated the early stages of them to prove that they would still work.
+Using an arduino device, or similar microcontroller, an attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server.
+This attack can be used to capture and repeat and authorized card without needing to physically duplicate the card.
 
@@
 \noindent
-Future Directions
+Chung lays out multiple methods that can be implemented in the future to secure Wiegand devices.
+He recommends that the protocol be adapted to allow for encrypted keycards and the rejection of keycards that are not properly encrypted, he also recommends that the actual readers implement hardware methods to detect when the device has been tampered with and to report that tampering immediately to the controller.
+Further upgrades include remote firmware detection and updates, Wiegand devices typically are not able to be updated without direct physical contact which disincentivizes updating the readers unless absolutely necessary.
 

### 2020-02-09 paper/sourceSummaries/summary2.tex
Update summary2.tex

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
 \noindent
-Name of member
+Connor Leavesley
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
+%remove % to show citation, change the name to your entry
+\bibentry{sevier2019securityofble}
 
@@
 \noindent
-Main Idea
+The authors aim to explain how Bluetooth LE protocol works and the cryptographic weaknesses in the protocol.
 
@@
 \noindent
-Theory
+This paper is applying Game Theory. A successful cryptographic attack is a loss for the security of the protocol.
 
@@
 \noindent
-Method
+The authors first sniffed the Bluetooth traffic with a Ubertooth using the BlueZ Bluetooth driver and associated Ubertooth drivers.
+Using the Blueooth handshake, the authors used Crackle to crack the Temporary Key due to its restricted key space.
+The Temporary Key was then used to gain access to the Long Term Key (LTK).
+The LTK was then used to decrypt any future communication traffic in Wireshark.
 
@@
 \noindent
-Findings
+The authors found that the keyspace of the Temporary Key is very restricted, allowing for a very quick brute force attack.
+They also found that Bluetooth Low Energy was susceptible to a number of attacks due to the low power requirements: denial of service and replay attacks.
+It was also found that Ubertooth struggled to capture a complete pairing event.
+The authors suggest that the Ubertooth should be as close as possible to the source transceiver to mitigate this issue.
 
@@
 \noindent
-Future Directions
+Many vendors likely do not implement the Bluetooth stack correctly.
+These vendors may also use the same stack across multiple devices.
+Areas of further research should focus on individual devices from the same vendor to attempt to find vulnerabilities that affect entire product lines.
 

### 2020-02-09 paper/sourceSummaries/summary2.tex
fixed passive voice

--- 2020-02-09 paper/sourceSummaries/summary2.tex
@@
 Using an arduino device, or similar microcontroller, an attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server.
-This attack can be used to capture and repeat and authorized card without needing to physically duplicate the card.
+This attack can capture and repeat and authorized card without needing to physically duplicate the card.
 
@@
 \noindent
-Chung lays out multiple methods that can be implemented in the future to secure Wiegand devices.
+Chung lays out multiple methods for future implementation to secure Wiegand devices.
 He recommends that the protocol be adapted to allow for encrypted keycards and the rejection of keycards that are not properly encrypted, he also recommends that the actual readers implement hardware methods to detect when the device has been tampered with and to report that tampering immediately to the controller.

### 2020-02-09 paper/sourceSummaries/summary1.tex

--- 2020-02-05 sourceSummaries.tex
@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{natbib}
-\usepackage{bibentry}
-\usepackage[hyphens]{url}
-\usepackage[numbib]{tocbibind}
-\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
-\include{references.bib}
-
-\bibliographystyle{plainnat}
-
-\begin{document}
-	\nobibliography*
-
-    \title{Source Summaries}
-    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
-    Daniel Capps, Jacob Ruud}
-    \date{\today}
-    \maketitle
-\break
-\setcounter{tocdepth}{2}\tableofcontents
-\break
-
-\section{Week 3}
+\section{Summary 1}
 
@@
 \noindent
-The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
+The authors outline how to approach attacking Bluetooth locks. They use well documented attacks to discover vulnerabilities in a Bluetooth low energy lock.
 
@@
 \noindent
-A threat rating system following the DREAD model is created to accurately represent the threat of the lock.
-Three threat models were created: unauthorized lock access, avoidance of logging, and denial of service.
-A Bluetooth man in the middle attack is carried out to gather information about the lock’s Generic Attribute Profile (GATT), how connections are formed, hosted services, and other characteristics of the lock.
-Using the GATT, a fake lock can be created to connect to the application, and then forward all information onto the actual lock.
-Next, access permission edge cases are tested to see when access can be abused to bypass controls.
-The app was reversed to gather further insight on how the app connected to the lock.
+The authors create a threat rating system following the DREAD model is to accurately represent the threat of the lock being successfully attacked.
+They make three threat models: unauthorized lock access, avoidance of logging, and denial of service.
+They use a Bluetooth man in the middle attack to gather information about the lock’s Generic Attribute Profile (GATT), how the application connected to the lock, hosted services, and other characteristics of the lock.
+Using the GATT, an attacker could use a fake lock hosted on a Arduino board to connect to the application, and then forward all information to the actual lock.
+Next, the authors test access permission edge cases to see when access could be abused by an attacker to bypass controls.
+The authors then reversed the app to gather further insight on how the app connected to the lock.
 
@@
 Not much was able to be done in the way of breaking into the lock.
-Some patterns were found in the communication scheme, but nothing to indicate how the data was being encrypted.
-A replay attack was launched, but this was ineffective.
+Some patterns were found in the communication scheme, but nothing to indicate how the application was encrypting the connection.
+The authors lauched a replay attack, but this was ineffective.
 Fuzzing was similarly ineffective.
-If an attacker is granted permission to access the lock, disconnects their internet, and then their permission is revoked, the attacker can still access the lock.
+If the owner of the lock granted an attacker permission to access it, disconnects their internet, and then the attacker's permission was revoked, the attacker can still access the lock.
 In the app, a possible encryption key for a database was found, but not pursued.
@@
 \pagebreak
-
-\bibliography{references}
-
-\end{document}

### 2020-02-09 paper/sourceSummaries/summary2.tex

@@
 \section{Summary 2}
+
+\noindent
+\subsection{Wiegand Protocol Access: A Decade of Decryption}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+
+\bibentry{sevier2019securityofble}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors aim to explain how Bluetooth LE protocol works and the cryptographic weaknesses in the protocol.
+
+\subsubsection{Theory}
+
+\noindent
+This paper is applying Game Theory. A successful cryptographic attack is a loss for the security of the protocol.
+
+\subsubsection{Method}
+
+\noindent
+The authors first sniffed the Bluetooth traffic with a Ubertooth using the BlueZ Bluetooth driver and associated Ubertooth drivers.
+Using the Blueooth handshake, the authors used Crackle to crack the Temporary Key due to its restricted key space.
+The Temporary Key was then used to gain access to the Long Term Key (LTK).
+The LTK was then used to decrypt any future communication traffic in Wireshark.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that the keyspace of the Temporary Key is very restricted, allowing for a very quick brute force attack.
+They also found that Bluetooth Low Energy was susceptible to a number of attacks due to the low power requirements: denial of service and replay attacks.
+It was also found that Ubertooth struggled to capture a complete pairing event.
+The authors suggest that the Ubertooth should be as close as possible to the source transceiver to mitigate this issue.
+
+\subsubsection{Future Directions}
+
+\noindent
+Many vendors likely do not implement the Bluetooth stack correctly.
+These vendors may also use the same stack across multiple devices.
+Areas of further research should focus on individual devices from the same vendor to attempt to find vulnerabilities that affect entire product lines.
 

### 2020-02-09 paper/sourceSummaries/summary2.tex
Fixed Connor title
Initial Push for Joshua\'s source summary 2

@@
 \noindent
-\subsection{Wiegand Protocol Access: A Decade of Decryption}
+\subsection{{A}nalyzing the {S}ecurity of {B}luetooth {L}ow {E}nergy}
 
@@
 \noindent
-\subsection{Wiegand Protocol Access: A Decade of Decryption}
+\subsection{{W}iegand {P}rotocol {A}ccess: {A} {D}ecade of {D}ecryption}
 
@@
 
+\noindent
+\subsection{{S}urvey on {V}arious {D}oor {L}ock {A}ccess {C}ontrol {M}echanisms}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{matthewrs2017surveydoorlock}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors compare different types of door lock authentication measures and their overall security.
+
+\subsubsection{Theory}
+
+\noindent
+The authors are applying Game Theory by directly comparing each individual authentication method.
+
+\subsubsection{Method}
+
+\noindent
+The authors directly compare different authentication methods using different factors.
+These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that each system has individual strengths.
+As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.
+Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors suggest using the knowlege of authentication system problems in order to build a new system, taking in mind the strengths and weaknesses for each category of authentication.
+
 \pagebreak

### 2020-02-09 paper/sourceSummaries/summary2.tex
Updated my summary

@@
 \noindent
-The authors directly compare different authentication methods using different factors.
-These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.
+The authors directly compare different authentication methods using different factors using factors that would matter to a user in addition to the overall security of the system.
+For user factors, factors considered include include battery life, ease of use and what happens if a credential is misplaced, stolen or forgotten.
+As for security, factors considered included the a user passing off a credential to an unauthorized party, the ability to spoof a credential, and the ease of bypass for a mechanical system.
 
@@
 \noindent
-The authors found that each system has individual strengths.
-As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.
-Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.
+The authors find that no one current system could be considered the most secure, and that each system has individual strengths.
+As each method does better in different ways, emphasis should be instead placed on ensuring the use of the lock that is most suited for the use case in which it is placed.
 

### 2020-02-10 paper/sourceSummaries/summary2.tex
added my source summerary

@@
 
+\subsection{{B}luetooth {L}ow {E}nergy and {S}martphones for {P}roximity-{B}ased  {A}utomatic {D}oor {L}ocks}
+
+\subsubsection{Group Member}
+
+\noindent
+Daniel Capps
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{andersson2014bluetooth}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors attempt to evaluate Bluetooth Low Energy as a technology by focusing on its use in door locks that automatically unlock based on the proximity of a smartphone.
+
+\subsubsection{Theory}
+
+\noindent
+Game theory. The authors try to determine ways to use the Proximity-based Automatic Door Locks with Bluetooth Low Energy without causing any adversaries to be able to exploit the locks.
+
+\subsubsection{Method}
+
+\noindent
+The author’s main method for testing their hypothesis had two halfs.
+The first half was to implement an application for iOS that would be able to unlock/lock the door lock, and the second half was to measure the Received Signal Strength Indicator (RSSI) between the phone and the door lock in order to ensure that the door would only unlock if the phone was in close enough proximity, and otherwise would be locked.
+
+\subsubsection{Findings}
+
+\noindent
+The authors gained a lot of knowledge pertaining to how suitable Bluetooth Low Energy is for automatic door locks, including what restrictions and possibilities exist on the iOS platform for developing Bluetooth Low Energy applications.
+The authors primarily learned that using this method they determined that they couldn’t differentiate between the two sides of the door the user was located on, that the applications effect on the battery life of the phone was negligible, the connection latency was sufficiently small for use in practice.
+The author's conclusion is that Bluetooth Low Energy is a suitable technology for proximity-based door locks.
+
+\subsubsection{Future Directions}
+
+\noindent
+Can you improve the implemented solution so that there is no limit on how many people can be in close proximity to the lock at once?
+Is there a better alternative to Bluetooth Low Energy in the case of Proximity-based door locks?
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-10 paper/sourceSummaries/summary2.tex
added my summary for week2

--- 2020-02-09 paper/sourceSummaries/summary2.tex
@@
 
-\noindent
-\subsection{{S}urvey on {V}arious {D}oor {L}ock {A}ccess {C}ontrol {M}echanisms}
+\subsection{Security Vulnerabilities of Bluetooth Low Energy Technology (BLE)}
 
@@
 \noindent
-Joshua Niemann
+Jacob Ruud
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{matthewrs2017surveydoorlock}
+%remove % to show citation, change the name to your entry
+\bibentry{o'sullivan}
 
@@
 \noindent
-The authors compare different types of door lock authentication measures and their overall security.
+Author Harry O'Sullivan along with mentor Ming Chow attempt to analyze the security of bluetooth low energy technology.
+They focus specifically on how BLE devices communicate with each other and how the communication between devices could be exploited by attackers.
 
@@
 \noindent
-The authors are applying Game Theory by directly comparing each individual authentication method.
+O'sullivan applies Game Theory in his work on BLE devices. Posing as an attacker he and attempts to simulate attack scenarios treating a compromise of sensitive information as a win.
 
@@
 \noindent
-The authors directly compare different authentication methods using different factors.
-These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.
+The author presents three different methods to compromise BLE as part of his research.
+The first method he attemps is an eavesdropping attack, during which he tries to capture information about a bluetooth host device using a sniffer.
+The second attack method he outlines is Man-in-the-middle, to explain which he refers to research done by lecturers at Marthandam College.
+The third attack scenario he describes is denial of service.
+During his explaination he outlines work done by researchers at University of Utah, as well as an attack technique called fuzzing.
 
@@
 \noindent
-The authors found that each system has individual strengths.
-As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.
-Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.
+The main findings ot this paper present the vulnerabilities of the BD_ADDR field which is present in all BLE communication.
+O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it.
+Not to mention the fact that BD_ADDR's are not globally unique so an attacker could try to spoof their BD_ADDR until packets start flowing in.
 
@@
 \noindent
-The authors suggest using the knowlege of authentication system problems in order to build a new system, taking in mind the strengths and weaknesses for each category of authentication.
+The author does not include any future directions at the end of his work.
+Bluetooth Low Energy has been tested extensively since its inception, and I can only assume that O'Sullivan believes that there is work out there testing every corner or bluetooth low energy.
+I do not necessarily agree with his thoughts but that is all there is to report with this paper.
+
+\Urlmuskip=0mu plus 1mu\relax
 

### 2020-02-10 paper/sourceSummaries/summary2.tex
fixed my summary for week2

@@
 %remove % to show citation, change the name to your entry
-\bibentry{o'sullivan}
+
+\bibentry{osullivan}
 
@@
 \noindent
-The main findings ot this paper present the vulnerabilities of the BD_ADDR field which is present in all BLE communication.
+The main findings ot this paper present the vulnerabilities of the BD ADDR field which is present in all BLE communication.
 O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it.
-Not to mention the fact that BD_ADDR's are not globally unique so an attacker could try to spoof their BD_ADDR until packets start flowing in.
+Not to mention the fact that BD ADDR's are not globally unique so an attacker could try to spoof their BD ADDR until packets start flowing in.
 

### 2020-02-10 paper/sourceSummaries/summary2.tex

--- 2020-02-10 paper/sourceSummaries/summary2.tex
@@
 
+\noindent
 \subsubsection{Group Member}
@@
 \noindent
-The authors directly compare different authentication methods using different factors using factors that would matter to a user in addition to the overall security of the system.
+The authors directly compare different authentication methods using different factors using characteristics that would matter to a user in addition to the overall security of the system.
 For user factors, factors considered include include battery life, ease of use and what happens if a credential is misplaced, stolen or forgotten.
@@
 
-\subsection{{B}luetooth {L}ow {E}nergy and {S}martphones for {P}roximity-{B}ased  {A}utomatic {D}oor {L}ocks}
-
-\subsubsection{Group Member}
-
-\noindent
-Daniel Capps
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-\bibentry{andersson2014bluetooth}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors attempt to evaluate Bluetooth Low Energy as a technology by focusing on its use in door locks that automatically unlock based on the proximity of a smartphone.
-
-\subsubsection{Theory}
-
-\noindent
-Game theory. The authors try to determine ways to use the Proximity-based Automatic Door Locks with Bluetooth Low Energy without causing any adversaries to be able to exploit the locks.
-
-\subsubsection{Method}
-
-\noindent
-The author’s main method for testing their hypothesis had two halfs.
-The first half was to implement an application for iOS that would be able to unlock/lock the door lock, and the second half was to measure the Received Signal Strength Indicator (RSSI) between the phone and the door lock in order to ensure that the door would only unlock if the phone was in close enough proximity, and otherwise would be locked.
-
-\subsubsection{Findings}
-
-\noindent
-The authors gained a lot of knowledge pertaining to how suitable Bluetooth Low Energy is for automatic door locks, including what restrictions and possibilities exist on the iOS platform for developing Bluetooth Low Energy applications.
-The authors primarily learned that using this method they determined that they couldn’t differentiate between the two sides of the door the user was located on, that the applications effect on the battery life of the phone was negligible, the connection latency was sufficiently small for use in practice.
-The author's conclusion is that Bluetooth Low Energy is a suitable technology for proximity-based door locks.
-
-\subsubsection{Future Directions}
-
-\noindent
-Can you improve the implemented solution so that there is no limit on how many people can be in close proximity to the lock at once?
-Is there a better alternative to Bluetooth Low Energy in the case of Proximity-based door locks?
-
-\Urlmuskip=0mu plus 1mu\relax
-
 \pagebreak

### 2020-02-16 paper/sourceSummaries/summary3.tex
prepped for the future summaries
added summary 2
Added Joshua's Source Summary 3

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 3}
 
 \noindent
-\subsection{Title}
+\subsection{Breaking Access Controls with BLEKey}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
+%remove % to show citation, change the name to your entry
+\bibentry{baseggio2015BLEKey}
 
@@
 
+\noindent
+\subsection{Testing Vulnerabilities in Bluetooth Low Energy}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{10.1145/3190645.3190693}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors analyze common weaknesses in Bluetooth connections, and use open-source tools to attack Bluetooth Low Energy keyboards.
+
+\subsubsection{Theory}
+
+\noindent
+Game Theory.  The authors directly attack the Bluetooth Low Energy protocol to gain the ability to read decrypted bluetooth packets from an attacker's perspective.
+
+\subsubsection{Method}
+
+\noindent
+The authors utilize a Bluetooth Low Energy keyboard in addition to a Ubertooth One and the CrackLE tool to decrypt packets from the keyboard.
+The authors captured the pairing sequence between the computer or phone and the keyboard using an ubertooth one.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that classical Bluetooth is still more secure for the time being.
+They also found that Bluetooth Low Energy is very possible to break, albeit very finnicky to get to work at times.
+Capturing a pairing sequence requires the Ubertooth to be on the right channel at the right time, which can be a challenge given Bluetooth Low Energy has multiple pairing channels, and an Ubertooth can only scan one at a time.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors next want to expand their device reach.
+The keyboard was picked because of it's ease of re-pairing the device.
+However, this same technique will work for other Bluetooth Low Energy devices, such as a smartwatch.
+The authors want to try different smartwatches and a few fitness trackers and see if the Ubertooth and Crackle can collectively decrypt the traffic.
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-16 paper/sourceSummaries/summary3.tex

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
 
+\subsection{{S}mart {L}ocks: {L}essons for {S}ecuring {C}ommodity {I}nternet of  {T}hings  {D}evices}
+
+\subsubsection{Group Member}
+
+\noindent
+Daniel Capps
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\bibentry{ho2016smart}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors examine the security of smart locks and present three types of attacks against them.
+The authors also analyze five commercially used locks with their focus being how they fair against these attacks.
+The analysis the authors use revealed flaws in the design, implementation, and interaction models of existing locks can be exploited by multiple adversaries.
+Giving the adversaries capabilities from unauthorized passage to irrevocable control of the lock.
+The authors also propose several mitigation techniques for the attacks they present.
+The author’s goal is informing people about the security challenges in the system design and functionality from new IoT systems.
+
+\subsubsection{Theory}
+
+\noindent
+Game Theory. The authors determine different types of attacks and mitigation techniques for smart locks against different types of adversaries.
+
+\subsubsection{Method}
+
+\noindent
+The authors use different tests for each attack vector using a specific environment.
+The three attack vectors described by the authors are State Consistency attacks, Unwanted Unlocking, and Privacy Leakage.
+The State Consistency attacks exploit the trust between the user’s mobile application and the lock.
+Specifically where the lock needs the user to send data to the server for them and won’t update their privileges if they’re offline.
+This allows revoked users to gain access to a lock even if the owner changed their permissions on the server.
+Unwanted Unlocking deals with certain conditions being met for unlocking the lock, but said conditions having edge cases where adversaries could unlock the door.
+An example of this is a Side-of-the-Door attack where an authorized user gets too close to the door from the inside and the lock either automatically unlocks or simply requires a touch from the adversary right outside the door in order to gain access.
+Privacy Leakage has to do with the server being able to see logs from houses unencrypted on the server side.
+Allowing any adversary with access to the server to see the logs of different people using those smart locks.
+The authors also tested different methods for mitigating these problems.
+
+\subsubsection{Findings}
+
+\noindent
+The authors implemented mitigation techniques for the attack vectors they found against smart locks.
+For State Consistency attacks, the authors used an access control list stored on the lock that would request updates and send log data each time an honest user was nearby.
+They also had the smart lock deny people access if they couldn’t connect to the server and they were determined to be untrustworthy.
+For Privacy Leakage, the authors use a key generated on the lock that’s sent to the user over BLE and upload the encrypted logs to the website.
+Allowing a user to see their logs over the internet without their logs being compromised.
+For Unwanted Unlocking, the authors used Vibrato.
+Which has the lock send a signal through a Body-Area Network(BAN) into the user’s phone and then has the phone send an unlock message through BLE.
+Using a detection threshold of 2 x 10 to the 10th Hz they have the lock opening 100 percent of times it’s touched and 0 percent of the time it’s not touched.
+However, because the technology for BAN isn’t in modern phones this solution wouldn’t be able to be implemented for a while.
+
+\subsubsection{Future Directions}
+
+\noindent
+How could we more accurately triangulate a person's position to avoid Unwanted Unlocking without having to use BAN? Is it possible to make a smart lock immune to traditional lockpicking?
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-16 paper/sourceSummaries/summary3.tex
initial commit

@@
 \noindent
-\subsection{Breaking Access Controls with BLEKey}
+\subsection{{B}reaking {A}ccess {C}ontrols with {BLEK}ey}
 
@@
 \noindent
-Main Idea
+Mark Baseggio and Eric Evenchick outline the simplicity of the Wiegand protocol.
+They then explain the BLEKey, how they built it, and how it is used to attack Wiegand capable card readers.
+The authors indicate that similar research has been done in the past but they wished to improve upon it by implementing Bluetooth communications in order to reduce the risk of discovery by retrieval.
 
@@
 \noindent
-Theory
+The theory applied by the authors is game theory, they demonstrate a vulnerability of the Wiegand protocol and then go about demonstrating a method to exploit it.
 
@@
 \noindent
-Method
+Baseggio and Evenchick custom developed the hardware for the BLEKey using KiCad and a pre-built Bluetooth Low-Energy module.
+They then programmed it with the ARM GCC compiler and the Nordic Firmware updaters.
+The authors then attach the BLEKey to a Wiegand interface using hte insulation displacement connector on the tool.
 
@@
 \noindent
-Findings
+The authors found that they could effectively intercept and store the card data as it is transmitted along the wires.
+They also found that they could remotely connect to the BLEKey to pull the card data from it, do a replay attack with a stored card, or play a custom card number.
+This can be used with great affect by penetration testers with even lower risk of discovery than prior devices.
 
@@
 \noindent
-Future Directions
+Future research and development of the BLEKey can involve the addition of cellular radios, this can allow testers to use the device with even less risk of discovery along with adding the possibility of storing the card data off-site instead of on the BLEKey itself.
+Another path of future development can involve a method to tie the BLEKey into the card reader power supply so that it does not have to rely on a battery.
+This would allow testers to use it on longer term engagements without needing to risk discovery by replacing the battery.
 

### 2020-02-17 paper/sourceSummaries/summary3.tex
summary3 complete

@@
 
+\subsection{Bluetooth Low Energy Mesh Networks: A Survey}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{seyedgomez2017}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors analyze the composition, architecture, and implementation of Bluetooth Low Energy mesh networks.
+Their main goal with this paper is to assess the strengths and weaknesses of mesh networks as they compare to star networks that are beginning to phase out as the industry standard.
+
+\subsubsection{Theory}
+
+\noindent
+
+In the open issues section of the paper, the authors use game theory to describe different scenarios that an attacker may be able to compromise a BLE mesh network.
+
+\subsubsection{Method}
+
+\noindent
+The majority of the work done for this paper was survery of proposed technologies, therefore the methods that the authors used for their conclusions involved reading publishings from other academics, corporations, and organizations and analyzing the architecture the each proposed.
+They used Bluetooth standards 4.0,4.1,4.2, and 5.0 in their comparison.
+
+\subsubsection{Findings}
+
+\noindent
+The main security takaway from this paper is that bluetooth low enerygy was originally designed for a star topology, and therefore there exist a number of flaws in the implementation of mesh networks that still have yet to be sorted out.
+For example, currently data channels are protected by per-hop security; therfore, end-to-end encryption and authentication are not currently supported in BLE mesh networks.
+Also, routing and data packets that are transmitted through advertising channels are not secured unless the application layer provides a security solution.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors suggested that future community work should focus on solving problems in security, multicast, and interoperability.
+They noted that these areas would best help deliver secure and high quality BLE mesh networks.
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-17 paper/sourceSummaries/summary3.tex

--- 2020-02-16 paper/sourceSummaries/summary3.tex
@@
 
+\noindent
+\subsection{{GATT}acking {B}luetooth {S}mart {D}evices}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{GattackingJasek}
+
+\subsubsection{Main Idea}
+The author summarized possible attacks against Bluetooth Low Energy (BLE) using the Generic Attribute Profile (GATT). The security features of BLE are also covered in detail. 
+\noindent
+
+\subsubsection{Theory}
+This is Game Theory. The author abused the GATT to intercept, decrypt, and inject commands in BLE communication.
+\noindent
+
+\subsubsection{Method}
+The author started with a high overview of what BLE is, how it advertises and pairs devices, and how attackers use GATT to transfer characteristics data.
+The specific BLE versions in question are 4.0 and 4.2.
+Then he went over BLE security features: encryption, MAC randomization, and whitelisting.
+Then Jasek discussed possible attacks against BLE, how manufacturers have tried to mitigate these attacks, and the risk of such attacks occurring.
+Finally he covers a tool he developed to assist in assessing BLE devices.
+\noindent
+
+\subsubsection{Findings}
+Many of the in place security features included in BLE are either not used or not implemented correctly.
+Instead, manufacturers use the GATT to transfer data and start secure sessions, often incorrectly.
+BLE advertisements are extremely susceptible to DoS and spoofing.
+Manufacturers use a method called "shuffling", but it is kept secret and likely not implemented correctly.
+Handshakes using the GATT are often not encrypted and passive interception is very profitable for attackers.
+Active interception is also useful due to MAC spoofing and GATT cloning.
+\noindent
+
+\subsubsection{Future Directions}
+The author does not give any indication of where he believes future research should go.
+However, Jasek used BLE 4.0 and BLE 4.2 in this paper.
+Researchers should look into how security practices have changed with the adoption of BLE 5.
+\noindent
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-17 paper/sourceSummaries/summary3.tex

@@
 
+\subsection{Bluetooth Low Energy Mesh Networks: A Survey}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\Urlmuskip=0mu plus 1mu\relax
+\bibentry{seyedgomez2017}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors analyze the composition, architecture, and implementation of Bluetooth Low Energy mesh networks.
+Their main goal with this paper is to assess the strengths and weaknesses of mesh networks as they compare to star networks that are beginning to phase out as the industry standard.
+
+\subsubsection{Theory}
+
+\noindent
+
+In the open issues section of the paper, the authors use game theory to describe different scenarios that an attacker may be able to compromise a BLE mesh network.
+
+\subsubsection{Method}
+
+\noindent
+The majority of the work done for this paper was survery of proposed technologies, therefore the methods that the authors used for their conclusions involved reading publishings from other academics, corporations, and organizations and analyzing the architecture the each proposed.
+They used Bluetooth standards 4.0,4.1,4.2, and 5.0 in their comparison.
+
+\subsubsection{Findings}
+
+\noindent
+The main security takaway from this paper is that bluetooth low enerygy was originally designed for a star topology, and therefore there exist a number of flaws in the implementation of mesh networks that still have yet to be sorted out.
+For example, currently data channels are protected by per-hop security; therfore, end-to-end encryption and authentication are not currently supported in BLE mesh networks.
+Also, routing and data packets that are transmitted through advertising channels are not secured unless the application layer provides a security solution.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors suggested that future community work should focus on solving problems in security, multicast, and interoperability.
+They noted that these areas would best help deliver secure and high quality BLE mesh networks.
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-02-17 paper/sourceSummaries/summary2.tex

@@
 
+\subsection{Security Vulnerabilities of Bluetooth Low Energy Technology (BLE)}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+
+\bibentry{osullivan}
+
+\subsubsection{Main Idea}
+
+\noindent
+Author Harry O'Sullivan along with mentor Ming Chow attempt to analyze the security of bluetooth low energy technology.
+They focus specifically on how BLE devices communicate with each other and how the communication between devices could be exploited by attackers.
+
+\subsubsection{Theory}
+
+\noindent
+O'sullivan applies Game Theory in his work on BLE devices. Posing as an attacker he and attempts to simulate attack scenarios treating a compromise of sensitive information as a win.
+
+\subsubsection{Method}
+
+\noindent
+The author presents three different methods to compromise BLE as part of his research.
+The first method he attemps is an eavesdropping attack, during which he tries to capture information about a bluetooth host device using a sniffer.
+The second attack method he outlines is Man-in-the-middle, to explain which he refers to research done by lecturers at Marthandam College.
+The third attack scenario he describes is denial of service.
+During his explaination he outlines work done by researchers at University of Utah, as well as an attack technique called fuzzing.
+
+\subsubsection{Findings}
+
+\noindent
+The main findings ot this paper present the vulnerabilities of the BD ADDR field which is present in all BLE communication.
+O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it.
+Not to mention the fact that BD ADDR's are not globally unique so an attacker could try to spoof their BD ADDR until packets start flowing in.
+
+\subsubsection{Future Directions}
+
+\noindent
+The author does not include any future directions at the end of his work.
+Bluetooth Low Energy has been tested extensively since its inception, and I can only assume that O'Sullivan believes that there is work out there testing every corner or bluetooth low energy.
+I do not necessarily agree with his thoughts but that is all there is to report with this paper.
+
+\Urlmuskip=0mu plus 1mu\relax
+
 \pagebreak

### 2020-02-17 paper/sourceSummaries/summary3.tex

@@
 
+\noindent
+\subsubsection{Citation}
+
 \Urlmuskip=0mu plus 1mu\relax
@@
 \noindent
-
 In the open issues section of the paper, the authors use game theory to describe different scenarios that an attacker may be able to compromise a BLE mesh network.

### 2020-02-22 paper/sourceSummaries/summary4.tex
prepped for the future summaries
added my section and updated future files
Added citation
Added summary 4

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 4}
 
@@
 \noindent
-Name of member
+Daniel Capps
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
 
@@
 
+\noindent
+\subsection{An Active Man-in-the-Middle Attack on Bluetooth Devices}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{BluetoothMITMTal}
+
+\subsubsection{Main Idea}
+
+\noindent
+The author looks to outline the main issues with BLE security. He focus on a possible architecture for a man-in-the-middle attack and a case study on a MITM'd device and an associated application.
+
+\subsubsection{Theory}
+
+\noindent
+The author is utilizing Game Theory. He is attacking a Bluetooth connection via a MITM.
+
+\subsubsection{Method}
+
+\noindent
+The author uses a Dax-Hub SW-28 Smart Bracelet and its associated app PowerSensor and the subject of the MITM attack.
+He used Kali Linux as the attacker and installed GATTacker and BtleJuice.
+He connected a CSR 4.0 dongle to a VM to transmit data between the app, the bracelet, and the middleman.
+He then uses GATTacker to intercept the BLE advertisements and copy the GATT profile of the bracelet.
+The author uses the GATT to simulate the device.
+Tal was then able to send fake to the device.
+
+\subsubsection{Findings}
+
+\noindent
+The author found that it was far to easy to intercept device communications and take control.
+Due to the inherent insecurities of the BLE protocol, he was able to change data that the device displayed, as well as take control of mobile camera via the app.
+
+\subsubsection{Future Directions}
+
+\noindent
+The author does not give any ideas as to future directions. The security issues with BLE are widely know, and Tal hopes to explain the security issues here and how to exploit them in a unique manner.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-02-23 paper/sourceSummaries/summary4.tex
Added Joshua's Source Summary 4

@@
 \noindent
-\subsection{Title}
+\subsection{{B}luetooth: {W}ith {L}ow {E}nergy comes {L}ow {S}ecurity}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{179196}
 
@@
 \noindent
-Main Idea
+The author of this paper breaks almost all the security measures relating to Bluetooth Low Energy after key generation, and builds an open-source tool that allows for the exposure of the Long-Term Key from a BLE packet if provided the pairing sequence.
+The author also breaks the channel hopping algorithm, allowing for passive attackers to follow Bluetooth packets on air.
 
@@
 \noindent
-Theory
+The author directly attacks the Bluetooth Low Energy protocol and exposes weaknesses in the key generation algorithm, the channel hopping algorithm, and other flaws in the Bluetooth Low Energy protocol.
+Directly attacking the protocol allows this article to resemble Game Theory.
 
@@
 \noindent
-Method
+The authors work backward from the Bluetooth protocol, breaking the security measures of Low Energy.
+An Ubertooth One is used as the intercept device.
+Using this ubertooth, the authors figured out how to calculate the Hop Interval, the Hop Increment, the Access Address, and CRC init.
+Finally, the author works on breaking the key exchange algorithm.
 
@@
 \noindent
-Findings
+The author found that an attacker could both follow a Bluetooth packet through the channel hopping algorithm, which would allow any passive attacker to follow a Bluetooth Stream with readily-available hardware like an Ubertooth.
+The author also found that the key exchange algorithm is extremely broken and can be reversed in under 1 second on a modern computer.
 
@@
 \noindent
-Future Directions
+The author outlined several next steps.
+The first of which details a hypothetical attack that would allow an attacker to force key negotiation, which would use the Bluetooth Low Energy key exchange protocol, of which was already broken in this paper.
+From there, an attacker could effectively decode any live Bluetooth Low Energy communication, even if not present during the initial pairing process.
 
@@
 Jacob Ruud
-
 \noindent

### 2020-02-23 paper/sourceSummaries/summary4.tex

--- 2020-02-22 paper/sourceSummaries/summary4.tex
@@
 \subsection{Title}
+
+\subsection{{O}n {P}rivacy and {S}ecurity {C}hallenges in {S}mart {C}onnected {H}omes}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{bugeja2016privacy}
 
@@
 \noindent
-Main Idea
+The authors give an overview of the privacy and security challenges directed towards the smart home domain.
+The authors discuss different constraints, soulution, challenges, and research issues where further investigation is required.
 
@@
 \noindent
-Theory
+Game Theory. The authors identify different attack vectors for smart homes and give some solutions to these attacks.
 
@@
 \noindent
-Method
+The authors identified different categories of security risks and then listed what a solution would have to look like in order to mitigate the security risks.
 
@@
 \noindent
-Findings
+The authors identified different security risks involved in smart homes.
+For the devices in smart homes they found problems with resource constraints, lack of user interface, and a need for tamper resistant devices and data.
+For the communication used in smart homes they found problems with heterogeneous protocols and devices going in and out of the network.
+The authors also found an issue with devices in smart homes not supporting dynamic patches for various reasons.
 
@@
 \noindent
-Future Directions
+The authors offer multiple future research directions.
+They recommend further investigation into, identity management, risk assessment methods, information flow control, and security management methods relating to smart home environments.
 

### 2020-02-23 paper/sourceSummaries/summary4.tex
initial commit
added summary four

@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{OSDPseiwgDOD}
 
@@
 \noindent
-Main Idea
+The authors review the Open Supervised Device Protocol, how it wworks, what it supports, the messages sent, and the legal implications of using the protocol in DoD facilities.
+They go in depth on the specific functioning of the protocol, the messages it sends, and the wiring necessary for it.
+The authors also compare it to the Wiegand protocol, covering the differences between them and the possible issues with upgrading from Wiegand to OSDP.
 
@@
 \noindent
-Theory
+The authors implement Systems theory in this article.  They observe how OSDP interfaces with other systems and how it has been implemented without attempting to attack it in any way.
 
@@
 \noindent
-Method
+They authors surveyed multiple suppliers of OSDP compatible devices and they reviewed numerous papers on OSDP.  There was no hands on research done.
 
@@
 \noindent
-Findings
+They find that OSDP is "not yet widely adopted" and it is not explicitly called for in various legal compliances.
+They also found that vendors have managed to keep Wiegand relevant but it is not able to support high levels of assurance.
+The authors claim that vendors use "FICAM as a selling point more than OSDP" but if OSDP is associated with FICAM it will be implemented more often.
 
@@
 \noindent
-Future Directions
+The authors indirectly recommend to "more clrealy associate" OSDP with FICAM guidance to increase the usage of it.
 

### 2020-02-24 paper/sourceSummaries/summary4.tex

@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{sandaya_sumithra_devi_2012}
 
@@
 \noindent
-Main Idea
+The authors aim to assess the security features added to bluetooth in the 4.0 security update.
+They specifically focus on the addition of new security association models as well as secure simple paring both in normal and low energy mode.
 
@@
 \noindent
-Theory
+This paper covers multiple scenarios that can be attributed to the standard alice, bob, and oscar method of describing game theory.
+In which oscar attemps to steal sensitive information from the communication between alice and bob treating the leak of any such data as a win.
 
@@
 \noindent
-Method
+The authors break down the protocol based on a framework called "A Bluetooth Threat Taxonomy" previously developed by a man by the name of John Paul Dunning.
+They use this framework to provide a comprehensive risk asssessment of the bluetooth 4.0 protocol and determine what likely attack vectors are.
+The Attack Classifications Include: Surveillance, Range Extension, Obfuscation, Fuzzer, Sniffing, Denial of Service, Malware, Unauthorized Direct Data Access, and Man In the Middle.
+
+Upon furhter reading, the authors dive deeper into the secure simple pairing function to assess its four association models: Numeric Comparison, Just Works, Out of Band, and Passkey Entry.
+Each one of these models is used independantly of each other depending of the IO capabilities of the two connecting devices.
 
@@
 \noindent
-Findings
+The findings of this paper demonstrate the advantages of Bluetooth Low Energy over standard Bluetooth communication.
+The main reason behind this destinction lies in the fact that BLE does not use DHKE in it's exchange of authentication data.
+This means that the protocol is less likely to be compromised due to the fact that potential threat actors are able to compute the shared DH Key and therefore have less trouble bypassing the other security mechanisms in place.
+Therefore, Bluetooth LE is not affected by PFS, KCI, or MitM attacks.
 
@@
 \noindent
-Future Directions
+The authors vaugely recommend at the end of their paper that "version 4.0 undergo a continual security analysis process by people involved." They suggest the possibility of integrated security to help "protect data privacy and to prevent misuse of data."
 

### 2020-02-24 paper/wireframe/wireframe.tex
updated wireframe.tex and .gitignore

--- 2020-02-05 sourceSummaries.tex
@@
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks,
+    citecolor=black,
+    filecolor=black,
+    linkcolor=black,
+    urlcolor=black
+}
 \include{references.bib}
@@
 
-    \title{Source Summaries}
+    \title{Wireframe}
     \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
@@
 \break
-\tableofcontents
+\setcounter{tocdepth}{2}\tableofcontents
 \break
-
-\section{Week 3}
-
-\noindent
-\subsection{Security Analysis of Bluetooth Technology}
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors detail the security methods used in Bluetooth versions 4.X, attempt to show attacks that bypass these methods, and describe ways to harden Bluetooth security against these attacks.
-
-\subsubsection{Theory}
-
-\noindent
-Game Theory is the primary theory being tested in this article.
-The authors attack various vulnerabilities in the Bluetooth protocol in order to determine methods to increase the relative security of the protocol.
-
-\subsubsection{Method}
-
-\noindent
-The researchers theorized and tested primary attacks against the Bluetooth security model: Active Eavesdropping and Passive Eavesdropping.
-Their attacks built upon the works by Da-Zhi Sun et al., Cope et a., Das et al., and Ryan.
-The assets used were a Raspberry Pi running Debian, an Ubertooth, TaoTronics TT-BH07 Bluetooth Headphones, a Logitech MX Master Mouse, and a Galazy S7 Edge.
-The authors modified existing Bluetooth utilities for their attacks and wrote some scripts of their own.
-
-\subsubsection{Findings}
-
-\noindent
-The authors managed to exploit their theorized vulnerabilities successfully.
-They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
-The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
-They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
-
-\subsubsection{Future Directions}
-
-\noindent
-The future directions for Active Eavesdropping is to expand and cover more than JustWorks devices, this would include attacks against mice and keyboards.
-The next steps for Passive Easedropping is to use the extrapolated information to decrypt packets for further analysis and to attack other devices like keyboards and medical implants, this can be used to gather sensitive information like passwords and health data.
-They also stated that they could combine the two attack types to inject malicious packets or modify existing ones for other attacks against the devices.
-Finally, they could also do research on the vulnerabilities in Bluetooth 5.0.
-
-\Urlmuskip=0mu plus 1mu\relax
-
-\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}
-
-\noindent
-\subsubsection{Group member}
-Joshua Niemann
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{8622000}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.
-The researchers also look at several BLE devices to analyze their security models.
-
-\subsubsection{Theory}
-
-\noindent
-Game Theory is the primary theory being tested in this article.
-The authors examine various versions of the Bluetooth protocol to determine which versions have the best security measures in place.
-In addition, the authors analyze BLE devices in an effort to learn which devices and device manufacturers have the best security.
-
-\subsubsection{Method}
-
-\noindent
-The researchers found that many modern fitness trackers use older versions of Bluetooth low energy.
-They also found that these fitness trackers often do not enable optional features that make bluetooth much more secure.
-As a result, most of the encryption was trivial to decrypt.
-The researchers then created an app that uses the Bluetooth sniff log functionality present in the developer section in Android to extract the security features of a bluetooth low energy device.
-
-\subsubsection{Findings}
-
-\noindent
-The authors managed to exploit their theorized vulnerabilities successfully.
-They found that the JustWorks authentication method used by headsets and headphones are insecure against active eavesdropping attacks with unsophisticated hardware.
-The researchers also discovered that, while difficult, passive eavesdropping is still successful against hardware running Bluetooth 4.1 and recommend moving to version 4.2 or greater.
-They also found that devices using LE Secure Connections or Secure Simple Pairings are secure against these specific attacks.
-
-\subsubsection{Future Directions}
-
-\noindent
-The authors want to make their app much more usable to the average consumer.  Right now it's very oriented toward technical-minded researchers.
-
-\subsection[Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks]{Finding Vulnerabilities in IoT Devices: Ethical \\Hacking of Electronic Locks}
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{KTH}
-
-\subsubsection{Main Idea}
-
-\noindent
-The authors outline how to approach attacking Bluetooth locks in a scientific fashion. They use well documented attacks and threat modeling to discover vulnerabilities in a Bluetooth low energy lock.
-
-\subsubsection{Theory}
-
-\noindent
-Game theory is being utilized to test the security of the lock and see where the vulnerabilities in the lock lie.
-
-\subsubsection{Method}
-
-\noindent
-A threat rating system following the DREAD model is created to accurately represent the threat of the lock.
-Three threat models were created: unauthorized lock access, avoidance of logging, and denial of service.
-A Bluetooth man in the middle attack is carried out to gather information about the lock’s Generic Attribute Profile (GATT), how connections are formed, hosted services, and other characteristics of the lock.
-Using the GATT, a fake lock can be created to connect to the application, and then forward all information onto the actual lock.
-Next, access permission edge cases are tested to see when access can be abused to bypass controls.
-The app was reversed to gather further insight on how the app connected to the lock.
-
-\subsubsection{Findings}
-
-\noindent
-Not much was able to be done in the way of breaking into the lock.
-Some patterns were found in the communication scheme, but nothing to indicate how the data was being encrypted.
-A replay attack was launched, but this was ineffective.
-Fuzzing was similarly ineffective.
-If an attacker is granted permission to access the lock, disconnects their internet, and then their permission is revoked, the attacker can still access the lock.
-In the app, a possible encryption key for a database was found, but not pursued.
-
-\subsubsection{Future Directions}
-
-\noindent
-The authors would like to see a more structured method developed to analyze the security of Bluetooth devices, as many of the approaches they took were very time consuming.
-
-\subsection{Security Evaluation and Exploitation of Bluetooth Low Energy Devices}
-
-\noindent
-\subsubsection{Citation}
-
-\Urlmuskip=0mu plus 1mu\relax
-\bibentry{rose_2017}
-
-\subsubsection{Main Idea}
-
-\noindent
-In his thesis, Captian Rose attemps to provide the industry with a wholistic look on the security of the low energy bluetooth protocol.
-He uses four different methods in an attempt to cover a wide range of conigurations and scenarios to really put this protocol to the test.
-
-\subsubsection{Theory}
-
-\noindent
-Game Theory is the primary theory being tested in this article.
-Captain Rose proposes multiple different scenarios where the bluetooth protocol is vulnerable in order to better understand how to secure it in the future.
-
-\subsubsection{Method}
-
-\noindent
-Captain Rose and his supporters used multiple different methods to test the strength and security of the Bluetooth protocol.
-First, he used a benchmark open-source range-finding tool to determine the location of Bluetooth devices through a novel distance estimation method, increasing the state-of-the-art device location distance from 50 meters up to 1,000 meters.
-Second, he evaluated 17 individual Bluetooth Low Energy devices for vulnerabilities in their operating system.
-Thirdly, he used user behavior analytics to demonstrate how malicious actors can exploit vulnerabilities for unauthorized device access and obtain sensitive information
-
-\subsubsection{Findings}
-
-\noindent
-Captain Rose's research revealed that 13 out of 17 (75 percent) of the tested devices contained at least one vulnerability resulting in unauthorized access.
-However, he did find that countermeasures to BLE attacks already exist and most require minimum implementation and development by manufacturers.
-More complex mediation techniques exist for issues that are not solved by the initial mediation techniques.
-
-\subsubsection{Future Directions}
-
-\noindent
-Since Captain Rose's work was done on an outdated bluetooth protocol (4.1) he mentions that there is room for others or himself to do research on devices implementing the newest protocol.
-He also recommends research into newly release bluetooth devices such as Lockitron or Schlage.
-He also states that he did not do any work with the firmware of the devices he tested so there is room for others to continue his work there.
-Along with that, he states that no research was done on attempting to clone the devices that he was testing, so there is more work to be done there.
-
-\pagebreak
 

### 2020-02-25 paper/paper/paper.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{bibentry}
\usepackage[hyphens]{url}
\usepackage[numbib]{tocbibind}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\setlength{\marginparwidth}{2cm}

\include{references.bib}

\title{
		\vspace{-1in} 	
		\usefont{OT1}{bch}{b}{n}
		\normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt]
		\huge A Security Analysis of the Lenel BlueDiamond \\
}

\usepackage{authblk}

\author[1]{Quintin Walters}
\author[1]{Joshua Niemann}
\author[1]{Connor Leavesley}
\author[1]{Daniel Capps}
\author[1]{Jacob Ruud}

\affil[1]{\small{Computing Security, Rochester Institute of Technology}}

\begin{document}
\maketitle
\selectlanguage{english}
\begin{abstract}
The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.

An abstract should be about 300 words long at most, and should act as a clear summary of the paper. It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding. The abstract should be broadly accessible (i.e. able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.

Structure the abstract as follows: background and aims, methods, results and conclusion.

Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
\end{abstract}

\section*{Keywords}
Select keywords with care, because they will help users discover your paper. To determine appropriate keywords, put yourself in the position of someone who is trying to search for a paper like yours. What search terms would you use? From those terms, select a list of at least three and no more than five words. Include these words in the text of the abstract and if at all possible, in the title of the paper.

\section{Introduction}
Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself! Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it.

Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}. Scroll on down to the bibliography section of the \LaTeX\ code if you'd like to see the other end of the built-in references system. The numbering is all handled in-house -- you just have to assign each reference a key, and Overleaf takes care of the rest.

On with the actual introduction! The introduction should provide context and background information appropriate for an academic audience. It should state a focused research question, define the variables being studied, and make clear the objective, importance, and relevance of the work.

Here is where you'd introduce the context surrounding your study. What led you to the question you ended up asking? Why is it relevant? Which fields of science is your question based around? What has previous literature demonstrated?

While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it. Obviously, excessive detail is not necessary (that's what the next section is for). Lastly, be sure to make mention of the potential implications of your findings, but once again remember that you'll be going into more detail about that in the discussion.

\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem. After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.

Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
\begin{enumerate}
   \item What is the central research problem?
   \item What is the topic of study related to that research problem?
    \item What methods should be used to analyze the research problem?
   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
\end{enumerate}

\section{Background \& Significance}
This is where you explain the context of your paper and describe in detail why it's important. It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper. Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do. Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.

To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:

\begin{itemize}
   \item State the research problem and give a more detailed explanation about the purpose of the study than what you stated in the introduction. This is particularly important if the problem is complex or multifaceted.
    \item Present the rationale of your proposed study and clearly indicate why it is worth doing; be sure to answer the "So What? question [i.e., why should anyone care].
    \item Describe the major issues or problems to be addressed by your research. This can be in the form of questions to be addressed. Be sure to note how your proposed study builds on previous assumptions about the research problem.
    \item Explain the methods you plan to use for conducting your research. Clearly identify the key sources you intend to use and explain how they will contribute to your analysis of the topic.
   \item Describe the boundaries of your proposed research in order to provide a clear focus. Where appropriate, state not only what you plan to study, but what aspects of the research problem will be excluded from the study.
   \item If necessary, provide definitions of key concepts or terms.
\end{itemize}

\section{Related Work}

Connected to the background and significance of your study is a section of your paper devoted to a more deliberate review and synthesis of prior studies related to the research problem under investigation. The purpose here is to place your project within the larger whole of what is currently being explored, while demonstrating to your readers that your work is original and innovative. Think about what questions other researchers have asked, what methods they have used, and what is your understanding of their findings and, when stated, their recommendations.

Since a literature review is information dense, it is crucial that this section is intelligently structured to enable a reader to grasp the key arguments underpinning your proposed study in relation to that of other researchers. A good strategy is to break the literature into "conceptual categories" [themes] rather than systematically or chronologically describing groups of materials one at a time. Note that conceptual categories generally reveal themselves after you have read most of the pertinent literature on your topic so adding new categories is an on-going process of discovery as you review more studies. How do you know you've covered the key conceptual categories underlying the research literature? Generally, you can have confidence that all of the significant conceptual categories have been identified if you start to see repetition in the conclusions or recommendations that are being made.

\textbf{NOTE:} Do not shy away from challenging the conclusions made in prior research as a basis for supporting the need for your paper. Assess what you believe is missing and state how previous research has failed to adequately examine the issue that your study addresses. For more information on writing literature reviews, go to: \url{https://libguides.usc.edu/writingguide/literaturereview}.

To help frame your paper's review of prior research, consider the "five C’s" of writing a literature review:
\begin{itemize}
    \item Cite, so as to keep the primary focus on the literature pertinent to your research problem.
    \item Compare the various arguments, theories, methodologies, and findings expressed in the literature: what do the authors agree on? Who applies similar approaches to analyzing the research problem?
    \item Contrast the various arguments, themes, methodologies, approaches, and controversies expressed in the literature: describe what are the major areas of disagreement, controversy, or debate among scholars?
    \item Critique the literature: Which arguments are more persuasive, and why? Which approaches, findings, and methodologies seem most reliable, valid, or appropriate, and why? Pay attention to the verbs you use to describe what an author says/does [e.g., asserts, demonstrates, argues, etc.].
    \item Connect the literature to your own area of research and investigation: how does your own work draw upon, depart from, synthesize, or add a new perspective to what has been said in the literature?
\end{itemize}

%\begin{figure}
%  \centering
%  \includegraphics[width=0.4\textwidth]{test.png}
%  \caption{Notice how \LaTeX\ automatically numbers this figure.}
%\end{figure}

\section{Research Design \& Methods}
This section must be well-written and logically organized because you are not actually doing the research, yet, your reader must have confidence that it is worth pursuing. The reader will never have a study outcome from which to evaluate whether your methodological choices were the correct ones. Thus, the objective here is to convince the reader that your overall research design and proposed methods of analysis will correctly address the problem and that the methods will provide the means to effectively interpret the potential results. Your design and methods should be unmistakably tied to the specific aims of your study.

Describe the overall research design by building upon and drawing examples from your review of the literature. Consider not only methods that other researchers have used but methods of data gathering that have not been used but perhaps could be. Be specific about the methodological approaches you plan to undertake to obtain information, the techniques you would use to analyze the data, and the tests of external validity to which you commit yourself [i.e., the trustworthiness by which you can generalize from your study to other people, places, events, and/or periods of time].

When describing the methods you will use, be sure to cover the following:
\begin{itemize}
    \item Specify the research process you will undertake and the way you will interpret the results obtained in relation to the research problem. Don't just describe what you intend to achieve from applying the methods you choose, but state how you will spend your time while applying these methods [e.g., coding text from interviews to find statements about the need to change school curriculum; running a regression to determine if there is a relationship between campaign advertising on social media sites and election outcomes in Europe].
    \item Keep in mind that the methodology is not just a list of tasks; it is an argument as to why these tasks add up to the best way to investigate the research problem. This is an important point because the mere listing of tasks to be performed does not demonstrate that, collectively, they effectively address the research problem. Be sure you clearly explain this.
    \item Anticipate and acknowledge any potential barriers and pitfalls in carrying out your research design and explain how you plan to address them. No method is perfect so you need to describe where you believe challenges may exist in obtaining data or accessing information. It's always better to acknowledge this than to have it brought up by your professor.
    \end{itemize}
\subsection{Procedures}
\subsection{Timeline}
\subsection{Novel Techniques}

\section{Preliminary Suppositions \& Implications}
Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications. The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation. Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking. Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.

When thinking about the potential implications of your study, ask the following questions:
\begin{itemize}
    \item What might the results mean in regards to challenging the theoretical framework and underlying assumptions that support the study?
    \item What suggestions for subsequent research could arise from the potential outcomes of the study?
    \item What will the results mean to practitioners in the natural settings of their workplace?
    \item Will the results influence programs, methods, and/or forms of intervention?
    \item How might the results contribute to the solution of social, economic, or other types of problems?
    \item Will the results influence policy decisions?
    \item In what way do individuals or groups benefit should your study be pursued?
    \item What will be improved or changed as a result of the proposed research?
    \item How will the results of the study be implemented and what innovations or transformative insights could emerge from the process of implementation?
\end{itemize}

\textbf{NOTE:} This section should not delve into idle speculation, opinion, or be formulated on the basis of unclear evidence. The purpose is to reflect upon gaps or understudied areas of the current literature and describe how your proposed research contributes to a new understanding of the research problem should the study be implemented as designed.

\section{Conclusions}
The conclusion reiterates the importance or significance of your paper and provides a brief summary of the entire study. This section should be only one or two paragraphs long, emphasizing why the research problem is worth investigating, why your research study is unique, and how it should advance existing knowledge.

Someone reading this section should come away with an understanding of:
\begin{itemize}
    \item Why the study should be done,
    \item The specific purpose of the study and the research questions it attempts to answer,
    \item The decision to why the research design and methods used where chosen over other options,
    \item The potential implications emerging from your proposed study of the research problem, and
    \item A sense of how your study fits within the broader scholarship about the research problem.
\end{itemize}

\section{Acknowledgements}
In the Acknowledgements section, the author(s) acknowledge or thank any persons or institutions who helped support the work in any way. In particular, this section must disclose any funding for the research completed, including the grant number (if a grant was awarded).

Anyone to thank/credit for helping your team along the way? This is the place to do it.

\section{Appendix}
Appendices are optional sections that should include additional tables, figures, or other data beyond what is included in the results section. An appendix should be able to stand separately from the prinicpal article. Therefore, no references (callouts) to appendix figures or tables should be made in the principal article. If required, the appendix should have its own bibliographic reference list with citations to that list confined to the appendix. \cite{latexcompanion}

\bibliographystyle{vancouver}
\bibliography{references}

\bibentry{test}

\end{document}

### 2020-02-25 paper/wireframe/wireframe.tex
Fixed crash

@@
-\documentclass[letterpaper,12pt]{article}
-\usepackage{natbib}
+\documentclass[10pt,twocolumn,letterpaper]{article}
+
+\usepackage[spanish,english]{babel}
+\usepackage[utf8x]{inputenc}
+\usepackage[T1]{fontenc}
+
+\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
+
 \usepackage{bibentry}
@@
 \usepackage[numbib]{tocbibind}
-\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks,
-    citecolor=black,
-    filecolor=black,
-    linkcolor=black,
-    urlcolor=black
-}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+\setlength{\marginparwidth}{2cm}
+
 \include{references.bib}
 
-\bibliographystyle{plainnat}
+\title{
+		\vspace{-1in} 	
+		\usefont{OT1}{bch}{b}{n}
+		\normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt]
+		\huge A Security Analysis of the Lenel BlueDiamond \\
+}
+
+\usepackage{authblk}
+
+\author[1]{Quintin Walters}
+\author[1]{Joshua Niemann}
+\author[1]{Connor Leavesley}
+\author[1]{Daniel Capps}
+\author[1]{Jacob Ruud}
+
+\affil[1]{\small{Computing Security, Rochester Institute of Technology}}
 
 \begin{document}
-	\nobibliography*
+\maketitle
+\selectlanguage{english}
+\begin{abstract}
+The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
 
-    \title{Wireframe}
-    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
-    Daniel Capps, Jacob Ruud}
-    \date{\today}
-    \maketitle
-\break
-\setcounter{tocdepth}{2}\tableofcontents
-\break
+An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
+It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding.
+The abstract should be broadly accessible (i.e.
+able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.
 
+Structure the abstract as follows: background and aims, methods, results and conclusion.
+
+Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
+\end{abstract}
+
+\section*{Keywords}
+Select keywords with care, because they will help users discover your paper.
+To determine appropriate keywords, put yourself in the position of someone who is trying to search for a paper like yours.
+What search terms would you use?
+From those terms, select a list of at least three and no more than five words.
+Include these words in the text of the abstract and if at all possible, in the title of the paper.
+
+\section{Introduction}
+Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself!
+Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it.
+
+Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}.
+Scroll on down to the bibliography section of the \LaTeX\ code if you'd like to see the other end of the built-in references system.
+The numbering is all handled in-house -- you just have to assign each reference a key, and Overleaf takes care of the rest.
+
+On with the actual introduction!
+The introduction should provide context and background information appropriate for an academic audience.
+It should state a focused research question, define the variables being studied, and make clear the objective, importance, and relevance of the work.
+
+Here is where you'd introduce the context surrounding your study.
+What led you to the question you ended up asking?
+Why is it relevant?
+Which fields of science is your question based around?
+What has previous literature demonstrated?
+
+While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it.
+Obviously, excessive detail is not necessary (that's what the next section is for).
+Lastly, be sure to make mention of the potential implications of your findings, but once again remember that you'll be going into more detail about that in the discussion.
+
+\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem.
+After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.
+
+Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
+\begin{enumerate}
+   \item What is the central research problem?
+   \item What is the topic of study related to that research problem?
+    \item What methods should be used to analyze the research problem?
+   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
+\end{enumerate}
+
+\section{Background \& Significance}
+This is where you explain the context of your paper and describe in detail why it's important.
+It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper.
+Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do.
+Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.
+
+To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:
+
+\begin{itemize}
+   \item State the research problem and give a more detailed explanation about the purpose of the study than what you stated in the introduction.
+This is particularly important if the problem is complex or multifaceted.
+    \item Present the rationale of your proposed study and clearly indicate why it is worth doing; be sure to answer the "So What? question [i.e., why should anyone care].
+    \item Describe the major issues or problems to be addressed by your research.
+This can be in the form of questions to be addressed.
+Be sure to note how your proposed study builds on previous assumptions about the research problem.
+    \item Explain the methods you plan to use for conducting your research. Clearly identify the key sources you intend to use and explain how they will contribute to your analysis of the topic.
+   \item Describe the boundaries of your proposed research in order to provide a clear focus.
+Where appropriate, state not only what you plan to study, but what aspects of the research problem will be excluded from the study.
+   \item If necessary, provide definitions of key concepts or terms.
+\end{itemize}
+
+\section{Related Work}
+
+Connected to the background and significance of your study is a section of your paper devoted to a more deliberate review and synthesis of prior studies related to the research problem under investigation.
+The purpose here is to place your project within the larger whole of what is currently being explored, while demonstrating to your readers that your work is original and innovative.
+Think about what questions other researchers have asked, what methods they have used, and what is your understanding of their findings and, when stated, their recommendations.
+
+Since a literature review is information dense, it is crucial that this section is intelligently structured to enable a reader to grasp the key arguments underpinning your proposed study in relation to that of other researchers.
+A good strategy is to break the literature into "conceptual categories" [themes] rather than systematically or chronologically describing groups of materials one at a time.
+Note that conceptual categories generally reveal themselves after you have read most of the pertinent literature on your topic so adding new categories is an on-going process of discovery as you review more studies.
+How do you know you've covered the key conceptual categories underlying the research literature?
+Generally, you can have confidence that all of the significant conceptual categories have been identified if you start to see repetition in the conclusions or recommendations that are being made.
+
+\textbf{NOTE:} Do not shy away from challenging the conclusions made in prior research as a basis for supporting the need for your paper.
+Assess what you believe is missing and state how previous research has failed to adequately examine the issue that your study addresses.
+For more information on writing literature reviews, go to: \url{https://libguides.usc.edu/writingguide/literaturereview}.
+
+To help frame your paper's review of prior research, consider the "five C’s" of writing a literature review:
+\begin{itemize}
+    \item Cite, so as to keep the primary focus on the literature pertinent to your research problem.
+    \item Compare the various arguments, theories, methodologies, and findings expressed in the literature: what do the authors agree on?
+Who applies similar approaches to analyzing the research problem?
+    \item Contrast the various arguments, themes, methodologies, approaches, and controversies expressed in the literature: describe what are the major areas of disagreement, controversy, or debate among scholars?
+    \item Critique the literature: Which arguments are more persuasive, and why?
+Which approaches, findings, and methodologies seem most reliable, valid, or appropriate, and why?
+Pay attention to the verbs you use to describe what an author says/does [e.g., asserts, demonstrates, argues, etc.].
+    \item Connect the literature to your own area of research and investigation: how does your own work draw upon, depart from, synthesize, or add a new perspective to what has been said in the literature?
+\end{itemize}
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=0.4\textwidth]{test.png}
+%  \caption{Notice how \LaTeX\ automatically numbers this figure.}
+%\end{figure}
+
+\section{Research Design \& Methods}
+This section must be well-written and logically organized because you are not actually doing the research, yet, your reader must have confidence that it is worth pursuing.
+The reader will never have a study outcome from which to evaluate whether your methodological choices were the correct ones.
+Thus, the objective here is to convince the reader that your overall research design and proposed methods of analysis will correctly address the problem and that the methods will provide the means to effectively interpret the potential results.
+Your design and methods should be unmistakably tied to the specific aims of your study.
+
+Describe the overall research design by building upon and drawing examples from your review of the literature.
+Consider not only methods that other researchers have used but methods of data gathering that have not been used but perhaps could be.
+Be specific about the methodological approaches you plan to undertake to obtain information, the techniques you would use to analyze the data, and the tests of external validity to which you commit yourself [i.e., the trustworthiness by which you can generalize from your study to other people, places, events, and/or periods of time].
+
+When describing the methods you will use, be sure to cover the following:
+\begin{itemize}
+    \item Specify the research process you will undertake and the way you will interpret the results obtained in relation to the research problem.
+Don't just describe what you intend to achieve from applying the methods you choose, but state how you will spend your time while applying these methods [e.g., coding text from interviews to find statements about the need to change school curriculum; running a regression to determine if there is a relationship between campaign advertising on social media sites and election outcomes in Europe].
+    \item Keep in mind that the methodology is not just a list of tasks; it is an argument as to why these tasks add up to the best way to investigate the research problem.
+This is an important point because the mere listing of tasks to be performed does not demonstrate that, collectively, they effectively address the research problem.
+Be sure you clearly explain this.
+    \item Anticipate and acknowledge any potential barriers and pitfalls in carrying out your research design and explain how you plan to address them.
+No method is perfect so you need to describe where you believe challenges may exist in obtaining data or accessing information.
+It's always better to acknowledge this than to have it brought up by your professor.
+    \end{itemize}
+\subsection{Procedures}
+\subsection{Timeline}
+\subsection{Novel Techniques}
+
+\section{Preliminary Suppositions \& Implications}
+Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
+The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation.
+Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking.
+Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.
+
+When thinking about the potential implications of your study, ask the following questions:
+\begin{itemize}
+    \item What might the results mean in regards to challenging the theoretical framework and underlying assumptions that support the study?
+    \item What suggestions for subsequent research could arise from the potential outcomes of the study?
+    \item What will the results mean to practitioners in the natural settings of their workplace?
+    \item Will the results influence programs, methods, and/or forms of intervention?
+    \item How might the results contribute to the solution of social, economic, or other types of problems?
+    \item Will the results influence policy decisions?
+    \item In what way do individuals or groups benefit should your study be pursued?
+    \item What will be improved or changed as a result of the proposed research?
+    \item How will the results of the study be implemented and what innovations or transformative insights could emerge from the process of implementation?
+\end{itemize}
+
+\textbf{NOTE:} This section should not delve into idle speculation, opinion, or be formulated on the basis of unclear evidence.
+The purpose is to reflect upon gaps or understudied areas of the current literature and describe how your proposed research contributes to a new understanding of the research problem should the study be implemented as designed.
+
+\section{Conclusions}
+The conclusion reiterates the importance or significance of your paper and provides a brief summary of the entire study.
+This section should be only one or two paragraphs long, emphasizing why the research problem is worth investigating, why your research study is unique, and how it should advance existing knowledge.
+
+Someone reading this section should come away with an understanding of:
+\begin{itemize}
+    \item Why the study should be done,
+    \item The specific purpose of the study and the research questions it attempts to answer,
+    \item The decision to why the research design and methods used where chosen over other options,
+    \item The potential implications emerging from your proposed study of the research problem, and
+    \item A sense of how your study fits within the broader scholarship about the research problem.
+\end{itemize}
+
+\section{Acknowledgements}
+In the Acknowledgements section, the author(s) acknowledge or thank any persons or institutions who helped support the work in any way.
+In particular, this section must disclose any funding for the research completed, including the grant number (if a grant was awarded).
+
+Anyone to thank/credit for helping your team along the way? This is the place to do it.
+
+\section{Appendix}
+Appendices are optional sections that should include additional tables, figures, or other data beyond what is included in the results section.
+An appendix should be able to stand separately from the prinicpal article.
+Therefore, no references (callouts) to appendix figures or tables should be made in the principal article.
+If required, the appendix should have its own bibliographic reference list with citations to that list confined to the appendix.
+\cite{latexcompanion}
+
+\bibliographystyle{vancouver}
 \bibliography{references}
 
+\bibentry{test}
+
 \end{document}

### 2020-03-01 paper/sourceSummaries/summary5.tex
prepped for the future summaries
added my section and updated future files

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 5}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-\bibentry{filizzola2018security}
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+The authors demonstrate Game Theory by directly comparing different card-cloning prevention techniques and their overall effectiveness.
+
+\subsubsection{Method}
+
+\noindent
+The authors evaluate the practicality of each detection technique or anti-cloning to determine the best option for an organization looking to secure their enviornment.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that card cloning is hard to particularly stop.
+Card cloning prevention requires a secret to be kept, and as long as the secret has to be transmitted to the reader at some point, the secret can be intercepted.
+Encryption isn't often too much help either, due to the low-powered nature of the RFID cards in question.
+Detection on the other hand is often a much better option.
+With detection, you can probalistically determine if a user is likely a clone using enviornmental attributes as well.
+This could entail detection based on a location that is improbable for a legitimate tag to be, or subsequent scans that are too far apart from each other.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors specify no formal future directions for this research, but do mention that further research on how to detect cloning attacks is not only necesary, but required for the security of every RFID system.
+The paper also mentions that more can be done on the hardware security front, such as better readers, better hash algorithms to avoid collision, strengthening the reliability of wireless connections, and better encryption techniques.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
 
@@
 
+\noindent
+\subsection{{Y}ou {C}an {C}lone {B}ut {Y}ou {C}an't {H}ide: {A} {S}urvey of {C}lone {P}revention and {D}etection for {RFID}}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{7888545}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors evaluate RFID cards and the ease of cloning them using various cloning countermeasures.
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-03-01 paper/sourceSummaries/summary5.tex
added summary

@@
 \noindent
-\subsection{Title}
+\subsection{Security Analysis of Vendor Customized Code in Firmware of Embedded Devices}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{liuSecurityAnalysis}
 
@@
 \noindent
-Main Idea
+The authors propose that the vendor customized code within device firmware is the most likely attack vector.
+They cover the tools to analyze this section, methodology to test it, and then analyze five embedded devices.
 
@@
 \noindent
-Theory
+The authors implement Game Theory in this article.  They examine multiple devices for security threats and treat it as a zero sum game.
 
@@
 \noindent
-Method
+The authors assess five devices: the TP-Link WR740nv5, TOTOLINK A850R, HUAQIN HGU421, Thunder Money Maker, and Yi Smart Webcam.
+They check hte device's standard functionality and then test the sections for vulnerabilities.
 
@@
 \noindent
-Findings
+The authors discover that the TP-Link WR740nv5 and the Thunder Money Maker do not perform code integrity checks.
+The TOTOLINK A850R has a vulnerability in its authentication method that can cause a web server crash if an attacker sends a carefully crafted request.
+Finally, the Yi Smart Webcam is vulnerable to Man-In-The-Middle attacks and the camera will respond to anyone on TCP port 38888 with the session key.
+These vulnerabilities were all found in the vendor specific code for the devices, proving the author's point about the possible weakness there.
 
@@
 \noindent
-Future Directions
+The authors recommend further development in current firmware analysis tools.
+Further research can be done to better them and the implementation of standards for vendor code segments in embedded devices.
 

### 2020-03-01 paper/sourceSummaries/summary5.tex
Connor Summary 5

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
 
+\noindent
+\subsection{BLE Injection-Free Attack: A Novel Attack On Bluetooth Low Energy Devices}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{jaihc19}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors propose a new method of attacking the cryptography of BLE devices, called an injection-free attack. The authors propose this attack for when forced key renegotiation is not possible.
+
+\subsubsection{Theory}
+
+\noindent
+The theory being used is Game Theory. The authors are attacking BLE devices in a zero sum game.
+
+\subsubsection{Method}
+
+\noindent
+The authors use a BLE device with enough interfaces to fill the bonding list of a target device.
+An attacker will keep pairing new devices to the target until the bonding list fills up.
+Once this occurs, the next device to join will cause the target device to forget a key and negotiate a new one with the new device.
+Now the target device will need to renegotiate keys with legitimate devices.
+The attacker could carry out this attack without the packet injection needed in other attacks.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that it is remarkably easy to attack BLE devices even without abuse the weak cryptography due to the limited resources of the devices.
+This method could be used by attackers to maliciously pair with devices and remove legitimate devices from the bonding list of devices.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors believe that future research should go into automating injection free attacks and the development of defenses against such attacks.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-03-01 paper/sourceSummaries/summary5.tex
Fix weird merging issue maybe?

--- 2020-03-01 paper/sourceSummaries/summary5.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{S}ecurity analysis of {I}nternet-of-{T}hings: {A} case study of august smart lock}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{ye2017security}
 
@@
 \noindent
-Main Idea
+The authors investigate the security of August smart locks by discussing different threat models for attacking August smart locks.
+The authors then show different attacks on August smart locks including handshake key leakage, owner account leakage, personal information leakage, and denial of service (DoS) attacks.
+The authors alongside each attack show a method for dealing with said attacks.
 
@@
 \noindent
-The authors demonstrate Game Theory by directly comparing different card-cloning prevention techniques and their overall effectiveness.
+Game Theory. The authors determine different types of attacks and mitigation techniques for smart locks against different types of attacks.
 
@@
 \noindent
-The authors evaluate the practicality of each detection technique or anti-cloning to determine the best option for an organization looking to secure their enviornment.
+The authors use different tests for each attack vector using a specific environment.
+The four attack vectors described by the authors are handshake key leakage, owner account leakage, personal information leakage and DoS attacks.
+Handshake key leakage is an attack that makes use of the fact that the owner’s handshake key is in plain text on their phone.
+Allowing them to make covert changes to the owner’s lock.
+The owner account attack allows an adversary to mimic the original owner’s account and send commands to the lock as if they were them.
+They simply have to replace their system file from the app with the owners and they’re in.
+Personal information leakage is just the data on the phone in plaintext.
+DoS attack is when there are multiple users connecting to a single lock, it will suspend the app and no user is able to lock/unlock at the same time.
 
@@
 \noindent
-The authors found that card cloning is hard to particularly stop.
-Card cloning prevention requires a secret to be kept, and as long as the secret has to be transmitted to the reader at some point, the secret can be intercepted.
-Encryption isn't often too much help either, due to the low-powered nature of the RFID cards in question.
-Detection on the other hand is often a much better option.
-With detection, you can probalistically determine if a user is likely a clone using enviornmental attributes as well.
-This could entail detection based on a location that is improbable for a legitimate tag to be, or subsequent scans that are too far apart from each other.
+The authors proposed mitigation methods for the four different attacks.
+The first method is requiring authentication with lock controlling requests.
+Denying the attacker the ability to even with the owner’s handshake key to make covert changes to their lock.
+The second method is to have an authentication mechanism to protect the system files from improper use.
+The authors recommend using FlaskDroid which is mandatory access control for Android.
+The third method is to just encrypt the data on the phone.
+The fourth method is to have a simple priority-based request control mechanism allowing the most authorized party to gain priority instead of having no one be able to control the lock.
 
@@
 \noindent
-The authors specify no formal future directions for this research, but do mention that further research on how to detect cloning attacks is not only necesary, but required for the security of every RFID system.
-The paper also mentions that more can be done on the hardware security front, such as better readers, better hash algorithms to avoid collision, strengthening the reliability of wireless connections, and better encryption techniques.
+Does FlaskDroid have secure file access control?
+Are there any authentication mechanisms for smart locks to detect fake apps?
+How would someone develop a holistic security framework to secure IoT devices?
 

### 2020-03-01 paper/sourceSummaries/summary5.tex
Fixed one more merge issue

--- 2020-03-01 paper/sourceSummaries/summary5.tex
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+ \bibentry{7888545}
 
@@
 \noindent
-Main Idea
+ The authors evaluate RFID cards and the ease of cloning them using various cloning countermeasures.
 
@@
 \noindent
-The authors demonstrate Game Theory by directly comparing different card-cloning prevention techniques and their overall effectiveness.
+Theory
 
@@
 \noindent
-The authors evaluate the practicality of each detection technique or anti-cloning to determine the best option for an organization looking to secure their enviornment.
+Method
 
@@
 \noindent
-The authors found that card cloning is hard to particularly stop.
-Card cloning prevention requires a secret to be kept, and as long as the secret has to be transmitted to the reader at some point, the secret can be intercepted.
-Encryption isn't often too much help either, due to the low-powered nature of the RFID cards in question.
-Detection on the other hand is often a much better option.
-With detection, you can probalistically determine if a user is likely a clone using enviornmental attributes as well.
-This could entail detection based on a location that is improbable for a legitimate tag to be, or subsequent scans that are too far apart from each other.
+Findings
 
@@
 \noindent
-The authors specify no formal future directions for this research, but do mention that further research on how to detect cloning attacks is not only necesary, but required for the security of every RFID system.
-The paper also mentions that more can be done on the hardware security front, such as better readers, better hash algorithms to avoid collision, strengthening the reliability of wireless connections, and better encryption techniques.
+Future Directions
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{7888545}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The authors evaluate RFID cards and the ease of cloning them using various cloning countermeasures.
+Main Idea
 
@@
 \noindent
-Theory
+ The authors demonstrate Game Theory by directly comparing different card-cloning prevention techniques and their overall effectiveness.
 
@@
 \noindent
-Method
+ The authors evaluate the practicality of each detection technique or anti-cloning to determine the best option for an organization looking to secure their enviornment.
 
@@
 \noindent
-Findings
+ The authors found that card cloning is hard to particularly stop.
+Card cloning prevention requires a secret to be kept, and as long as the secret has to be transmitted to the reader at some point, the secret can be intercepted.
+Encryption isn't often too much help either, due to the low-powered nature of the RFID cards in question.
+Detection on the other hand is often a much better option.
+With detection, you can probalistically determine if a user is likely a clone using enviornmental attributes as well.
+This could entail detection based on a location that is improbable for a legitimate tag to be, or subsequent scans that are too far apart from each other.
 
@@
 \noindent
-Future Directions
+ The authors specify no formal future directions for this research, but do mention that further research on how to detect cloning attacks is not only necesary, but required for the security of every RFID system.
+The paper also mentions that more can be done on the hardware security front, such as better readers, better hash algorithms to avoid collision, strengthening the reliability of wireless connections, and better encryption techniques.
 
@@
 \noindent
-\subsection{Security Analysis of Vendor Customized Code in Firmware of Embedded Devices}
+\subsection{Title}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{liuSecurityAnalysis}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The authors propose that the vendor customized code within device firmware is the most likely attack vector.
-They cover the tools to analyze this section, methodology to test it, and then analyze five embedded devices.
+Main Idea
 
@@
 \noindent
-The authors implement Game Theory in this article.  They examine multiple devices for security threats and treat it as a zero sum game.
+Theory
 
@@
 \noindent
-The authors assess five devices: the TP-Link WR740nv5, TOTOLINK A850R, HUAQIN HGU421, Thunder Money Maker, and Yi Smart Webcam.
-They check hte device's standard functionality and then test the sections for vulnerabilities.
+Method
 
@@
 \noindent
-The authors discover that the TP-Link WR740nv5 and the Thunder Money Maker do not perform code integrity checks.
-The TOTOLINK A850R has a vulnerability in its authentication method that can cause a web server crash if an attacker sends a carefully crafted request.
-Finally, the Yi Smart Webcam is vulnerable to Man-In-The-Middle attacks and the camera will respond to anyone on TCP port 38888 with the session key.
-These vulnerabilities were all found in the vendor specific code for the devices, proving the author's point about the possible weakness there.
+Findings
 
@@
 \noindent
-The authors recommend further development in current firmware analysis tools.
-Further research can be done to better them and the implementation of standards for vendor code segments in embedded devices.
+Future Directions
 

### 2020-03-02 paper/sourceSummaries/summary5.tex

@@
 \noindent
-\subsection{Title}
+\subsection{BLE Injection-Free Attack: A Novel Attack On Bluetooth Low Energy Devices}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{jaihc19}
 
@@
 \noindent
-Main Idea
+The authors propose a new method of attacking the cryptography of BLE devices, called an injection-free attack. The authors propose this attack for when forced key renegotiation is not possible.
 
@@
 \noindent
-Theory
+The theory being used is Game Theory. The authors are attacking BLE devices in a zero sum game.
 
@@
 \noindent
-Method
+The authors use a BLE device with enough interfaces to fill the bonding list of a target device.
+An attacker will keep pairing new devices to the target until the bonding list fills up.
+Once this occurs, the next device to join will cause the target device to forget a key and negotiate a new one with the new device.
+Now the target device will need to renegotiate keys with legitimate devices.
+The attacker could carry out this attack without the packet injection needed in other attacks.
 
@@
 \noindent
-Findings
+The authors found that it is remarkably easy to attack BLE devices even without abuse the weak cryptography due to the limited resources of the devices.
+This method could be used by attackers to maliciously pair with devices and remove legitimate devices from the bonding list of devices.
 
@@
 \noindent
-Future Directions
+The authors believe that future research should go into automating injection free attacks and the development of defenses against such attacks.
 

### 2020-03-02 paper/sourceSummaries/summary5.tex
fixed pdf issues
summary5 first commit

@@
 \noindent
-\subsection{Title}
+\subsection{{O}utput {C}haracteristics and {C}ircuit {M}odeling of {W}iegand {S}ensor}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{Sun_Yamada_Takemura_Wiegand}
 
@@
 \noindent
-Main Idea
+In this paper the authors take a deep dive into the circuit design and output characteristics of a sensor using weigand technology as well as propose a new design for the sensor to make it more efficient.
 
@@
 \noindent
-Theory
+Game Theory is the underlying theory behind this paper as the authors propose a situation where a wiegand sensor can use its own pulse voltage as a power source as a win
 
@@
 \noindent
-Method
+The authors first measured the pulse voltage from a test sensor they had in their lab, they then created an equivalent electrical circuit to generate the same numbers generated from the weigand, they then used this circuit to calculate the amount of voltage needed to run the device consistantly and determine whether or not their idea was sound.
+They also used matlab/simulink simulation to help with this process.
 
@@
 \noindent
-Findings
+The authors found that the pulse voltage created by the internals of the wiegand sensor were uniform enough to be used for energy harvesting, and that the simulation numbers agreed with the real world behavior reflected by the test circuit they created.
 
@@
 \noindent
-Future Directions
+The authors propose further testing of their design at abnormal temperatures as they state that the device will behave differently depending on the outside air temperature where the circuit is being operated.
 

### 2020-03-07 paper/wireframe/wireframe.tex
initial wireframe changes

@@
 
-\usepackage[spanish,english]{babel}
+\usepackage[english]{babel}
 \usepackage[utf8x]{inputenc}
@@
 \section{Research Design \& Methods}
-This section must be well-written and logically organized because you are not actually doing the research, yet, your reader must have confidence that it is worth pursuing.
-The reader will never have a study outcome from which to evaluate whether your methodological choices were the correct ones.
-Thus, the objective here is to convince the reader that your overall research design and proposed methods of analysis will correctly address the problem and that the methods will provide the means to effectively interpret the potential results.
-Your design and methods should be unmistakably tied to the specific aims of your study.
+To provide a well rounded analysis of the device we expect three primary areas of research.
+First, we expect to perform attacks against the physical security of the device.
+Second, we will analyze the firmware for vulnerabilities.
+Finally, we plan on testing the application and Bluetooth implementation.
 
-Describe the overall research design by building upon and drawing examples from your review of the literature.
-Consider not only methods that other researchers have used but methods of data gathering that have not been used but perhaps could be.
-Be specific about the methodological approaches you plan to undertake to obtain information, the techniques you would use to analyze the data, and the tests of external validity to which you commit yourself [i.e., the trustworthiness by which you can generalize from your study to other people, places, events, and/or periods of time].
+The phyisical security of the lock, particularly the magnetic antitamper switch, is what protects it from well known attacks against the Wiegand protocol.
+If the physical security can be bypassed than attackers could take advantage of these other attacks to bypass the lock entirely.
 
-When describing the methods you will use, be sure to cover the following:
+Firmware analysis is necessary to discover underlying vulnerabilities.
+The vulnerabilities discovered here may include hardcoded credentials, service backdoors, and poorly implemented authentication methods.
+These vulnerabilites would not be obvious or easily detectible without dissecting the firmware.
+
+The application and Bluetooth implementation are the primary means which users will be interacting with the device.
+Any vulnerabilities here will be exposed to outside attackers on a daily basis.
+Any attacker within 30ft of the device can snoop on the Bluetooth traffic.
+The application is also downbloadable on the Google Play Store for free, any vulnerabilities in it would be easily accessible to an attacker.
+
+\subsection{Firmware Analysis}
 \begin{itemize}
-    \item Specify the research process you will undertake and the way you will interpret the results obtained in relation to the research problem.
-Don't just describe what you intend to achieve from applying the methods you choose, but state how you will spend your time while applying these methods [e.g., coding text from interviews to find statements about the need to change school curriculum; running a regression to determine if there is a relationship between campaign advertising on social media sites and election outcomes in Europe].
-    \item Keep in mind that the methodology is not just a list of tasks; it is an argument as to why these tasks add up to the best way to investigate the research problem.
-This is an important point because the mere listing of tasks to be performed does not demonstrate that, collectively, they effectively address the research problem.
-Be sure you clearly explain this.
-    \item Anticipate and acknowledge any potential barriers and pitfalls in carrying out your research design and explain how you plan to address them.
-No method is perfect so you need to describe where you believe challenges may exist in obtaining data or accessing information.
-It's always better to acknowledge this than to have it brought up by your professor.
+    \item Search for hard-coded credentials.
+    \item Search for vulnerabilities such as buffer overflows, default certificates, debugging services, open ports, etc.
+    \item Search for improperly implemented authentication and cryptographic methods.
+    \item Search for any unpatched vulnerabilities in dependencies and base code such as BlueBorne.
 \end{itemize}
-\subsection{Procedures}
-\subsection{Timeline}
-\subsection{Novel Techniques}
+
+Firmware analysis is a solid foundation for the research to build upon.
+The firmware is the software that runs on and controls the device as a whole, vulnerabilities evident in it reduce the security of the device as a whole and can lead to vulnerabilities in other areas.
+The firmware analysis will be performed with automated tools at first, followed by manual analysis to confirm any discoveries.
+A final pass through with manual analysis will then be done to spot any missed or overlooked vulnerabilities.
+The methods of analysis will vary, depending on if we are supplied with the firmware or if we have to extract it from the device ourselves.
+If we are provided with the firmware source code we can do analysis directly on that, if we need to extract it ourselves we will have to disassemble it and spend a large amount of time reverse engineering in order to find any vulnerabilities.
 
@@
 
-\bibliographystyle{vancouver}
+\bibliographystyle{ieee}
 \bibliography{references}

### 2020-03-08 paper/wireframe/wireframe.tex
Added Bluetooth and Application Methods

@@
 
+\subsection{Bluetooth and Application Analysis}
+\begin{itemize}
+    \item Perform Generic Attribute Protocol (GATT) attacks to gather data about the device and conduct Man-in-the-Middle (MITM) attacks. 
+    \item Perform known cryptographic attacks against Bluetooth Low Energy (BLE) to decrypt intercepted traffic, perform replay attacks and command injection.
+    \item Search for hard-coded credentials, buffer overflows, and other application vulnerabilities. 
+    \item Search for abusable edge cases in the authentication scheme.
+\end{itemize}
+
+BLE is a major part of this research.
+BLE is a Bluetooth protocol variant designed for low energy operations and such has a limited set of computing resources available.
+BLE does not need manual pairing to a device, meaning an application with the correct authentication data can pair automatically.
+Automated tools will gather preliminary data about the device by examining the GATT and Generic Access Profile (GAP) .
+The tool will copy he GATT over to an intermediary device and MITM all communications between the device and the application.
+With the device communication being intercepted, an Injection Free Attack can force a re-pairing and the intermediary device will intercept the Short Term Key.
+With the Short Term Key, we can derive the Long Term Key.
+We can then use the Long Term Key to decrypt communications and send commands on the behalf of the application.
+Automated tools will scan the application to discover hard-coded credentials and vulnerabilities.
+Finally, edge cases in the authentication scheme will be manually explored to see if an attacker could exploit permissions.
+
 \section{Preliminary Suppositions \& Implications}

### 2020-03-08 paper/wireframe/wireframe.tex
added physical section

--- 2020-03-07 paper/wireframe/wireframe.tex
@@
 
+\subsection{Physical Analysis}
+\begin{itemize}
+    \item Search the lock for potential physical bypass attacks 
+    \item Search for issues with the magnetic anti-tamper switch
+    \item Search the lock for easy access to Wiegand protocol leads
+    \item Search for potential areas of destructive entry
+\end{itemize}
+
+Enterprise locks often have many potential types of issues from the perspective of a physical attack.
+The authors expect to find potential implementation errors in areas such as the configuration of the anti-tamper switch, the location of the connectors to the Wiegand network, or access to the locking motor from within the device.
+In order to detect these issues, the authors will analyze the lock from the perspective of a typical wall-mounted installation.
+From there, the authors will look into various ways to both undestructively, and destructively trigger an unlock.
+In a physical test, a vulnerability can take a lot of different forms.
+
 \section{Preliminary Suppositions \& Implications}

### 2020-03-08 paper/wireframe/wireframe.tex

--- 2020-03-08 paper/wireframe/wireframe.tex
@@
 
+\subsection{Physical Analysis}
+\begin{itemize}
+    \item Search the lock for potential physical bypass attacks.
+    \item Search for issues with the magnetic anti-tamper switch.
+    \item Search the lock for easy access to Wiegand protocol leads.
+    \item Search for potential areas of destructive entry.
+\end{itemize}
+
+Enterprise locks often have many potential types of issues from the perspective of a physical attack.
+The authors expect to find potential implementation errors in areas such as the configuration of the anti-tamper switch, the location of the connectors to the Wiegand network, or access to the locking motor from within the device.
+In order to detect these issues, the authors will analyze the lock from the perspective of a typical wall-mounted installation.
+From there, the authors will look into various ways to both non-destructively, and destructively trigger an unlock.
+In a physical test, a vulnerability can take a lot of different forms.
+
 \subsection{Bluetooth and Application Analysis}

### 2020-03-08 paper/wireframe/wireframe.tex

@@
 With the device communication being intercepted, an Injection Free Attack can force a re-pairing and the intermediary device will intercept the Short Term Key.
-With the Short Term Key, we can derive the Long Term Key.
-We can then use the Long Term Key to decrypt communications and send commands on the behalf of the application.
+With the Short Term Key,  An attacker can derive the Long Term Key.
+They can then use the Long Term Key to decrypt communications and send commands on the behalf of the application.
 Automated tools will scan the application to discover hard-coded credentials and vulnerabilities.

### 2020-03-08 paper/wireframe/wireframe.tex
fixed passive voice

@@
 \section{Research Design \& Methods}
-To provide a well rounded analysis of the device we expect three primary areas of research.
-First, we expect to perform attacks against the physical security of the device.
-Second, we will analyze the firmware for vulnerabilities.
-Finally, we plan on testing the application and Bluetooth implementation.
+To provide a well rounded analysis of the device there are three primary areas of research.
+First, attacks against the physical security of the device.
+Second, analysis of the firmware for vulnerabilities.
+Finally, testing the application and Bluetooth implementation.
 
@@
 Any attacker within 30ft of the device can snoop on the Bluetooth traffic.
-The application is also downbloadable on the Google Play Store for free, any vulnerabilities in it would be easily accessible to an attacker.
+The application is also downloadable on the Google Play Store for free, any vulnerabilities in it would be easily accessible to an attacker.
 
@@
 The firmware is the software that runs on and controls the device as a whole, vulnerabilities evident in it reduce the security of the device as a whole and can lead to vulnerabilities in other areas.
-The firmware analysis will be performed with automated tools at first, followed by manual analysis to confirm any discoveries.
-A final pass through with manual analysis will then be done to spot any missed or overlooked vulnerabilities.
-The methods of analysis will vary, depending on if we are supplied with the firmware or if we have to extract it from the device ourselves.
-If we are provided with the firmware source code we can do analysis directly on that, if we need to extract it ourselves we will have to disassemble it and spend a large amount of time reverse engineering in order to find any vulnerabilities.
+Firmware analysis is performed with automated tools at first, followed by manual analysis to confirm any discoveries.
+A final pass through with manual analysis is done to spot any missed or overlooked vulnerabilities.
+The methods of analysis will vary, depending on if the firmware is supplied or if it must be extracted it from the device.
+If the firmware is provided then analysis can be performed directly, otherwise extraction must be performed and the compiled firmware will be analyzed.
 

### 2020-03-08 paper/wireframe/wireframe.tex
Background and Significance

--- 2020-03-08 paper/wireframe/wireframe.tex
@@
 \section{Background \& Significance}
-This is where you explain the context of your paper and describe in detail why it's important.
-It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper.
-Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do.
-Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.
-
-To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:
+Our research problem is to take different discovered and undiscovered exploits and test them against Lenel Blue Diamond readers.
+The purpose of this study is to uncover different vulnerabilities in Lenel Blue Diamond readers so that they can be disclosed properly and eventually patched.
+Lenel has over 1 million Blue Diamond readers deployed in multiple industries, the most notable one being real-estate (https://www.lenel.com/products/bluediamond).
+This study is important because the security of these locks are very important because if someone unauthorized is able to enter through these locked doors, everything on the other side would be compromised including important data, objects, and even people.
+Things which if they were compromised would result in extreme loss.
+For our research the major issues we found fall into three categories, the firmware used on the lock, the physical aspect of the lock, and the usage of the mobile app and bluetooth communication.
+We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers.
+We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers.
+Our research has it bounds inside the Lenel Blue Diamond readers mobile app and lock itself.
+We will not be researching the server side of lenel Blue Diamond readers and are assuming that the server side is secure for this research project.
 

### 2020-03-08 paper/wireframe/wireframe.tex
Added cite and changed first line.

@@
 \section{Background \& Significance}
-Our research problem is to take different discovered and undiscovered exploits and test them against Lenel Blue Diamond readers.
-The purpose of this study is to uncover different vulnerabilities in Lenel Blue Diamond readers so that they can be disclosed properly and eventually patched.
-Lenel has over 1 million Blue Diamond readers deployed in multiple industries, the most notable one being real-estate (https://www.lenel.com/products/bluediamond).
+The purpose of this research is to test the security properties of the Lenel Blue Diamond Readers and to uncover different vulnerabilities in them so that they can be disclosed properly and eventually patched.
+Lenel has over 1 million Blue Diamond readers deployed in multiple industries, the most notable one being real-estate \cite{lenelbluediamondwebsite}.
 This study is important because the security of these locks are very important because if someone unauthorized is able to enter through these locked doors, everything on the other side would be compromised including important data, objects, and even people.
@@
 Our research has it bounds inside the Lenel Blue Diamond readers mobile app and lock itself.
-We will not be researching the server side of lenel Blue Diamond readers and are assuming that the server side is secure for this research project.
+We will
 

### 2020-03-09 paper/wireframe/wireframe.tex
added abstract and introduction to wireframe, excluding content that requires experiment results to complete.

--- 2020-03-08 paper/wireframe/wireframe.tex
@@
 \begin{abstract}
-The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
-
-An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
+%The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
+%
+%An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
 It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding.
@@
 able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.
+%
+%Structure the abstract as follows: background and aims, methods, results and conclusion. 
+%
+%Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
 
-Structure the abstract as follows: background and aims, methods, results and conclusion.
+Bluetooth technology has been around since the mid 1990's.
+It's adoption into consumer technology has made it a mainstream protocol for those developing compatible hardware.
+Unfortunately, weak security in it's underlying design has also made it a target for multiple different forms of attack.
+This can be especially dangerous when the compatible device is used for access control.
+In this paper we study a specific subset of devices from Lenel's new BlueDiamond lineup, testing a variety of methods that have proven affective on similarly designed hardware.
+These methods included assessments of physical hardware, firmware, and connected BlueDiamond mobile app for vulnerabilities and could result in a breach of access control.
+Our testing found that...
+\todo{Put results here}
 
-Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
 \end{abstract}
@@
 \section*{Keywords}
-Select keywords with care, because they will help users discover your paper.
+%Select keywords with care, because they will help users discover your paper.
 To determine appropriate keywords, put yourself in the position of someone who is trying to search for a paper like yours.
@@
 Include these words in the text of the abstract and if at all possible, in the title of the paper.
+\todo{add keywords}
 
 \section{Introduction}
-Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself!
+%Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself!
 Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it.
-
-Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}.
+%
+%Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}.
 Scroll on down to the bibliography section of the \LaTeX\ code if you'd like to see the other end of the built-in references system.
 The numbering is all handled in-house -- you just have to assign each reference a key, and Overleaf takes care of the rest.
-
-On with the actual introduction!
+%
+%On with the actual introduction!
 The introduction should provide context and background information appropriate for an academic audience.
 It should state a focused research question, define the variables being studied, and make clear the objective, importance, and relevance of the work.
-
-Here is where you'd introduce the context surrounding your study.
+%
+%Here is where you'd introduce the context surrounding your study.
 What led you to the question you ended up asking?
@@
 What has previous literature demonstrated?
-
-While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it.
+%
+%While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it.
 Obviously, excessive detail is not necessary (that's what the next section is for).
 Lastly, be sure to make mention of the potential implications of your findings, but once again remember that you'll be going into more detail about that in the discussion.
+%
+%\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem.
+After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.
+%
+%Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
+%\begin{enumerate}
+%   \item What is the central research problem?
+%   \item What is the topic of study related to that research problem?
+%    \item What methods should be used to analyze the research problem?
+%   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
+%\end{enumerate}
 
-\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem.
-After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.
+In the last couple of years, the physical security community has seen an abundace of standard mechanical locks being replaced with \"smart locks\" designed to make accessing secure areas simpler and safer.
+Only to discover that these smart locks can be opened with just as little effort as picking a standard lock requires.
+In response to this, corporations have been rolling out revision after revision of their smart lock technology to try and combat the evolution of access control bypass.
 
-Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
-\begin{enumerate}
-   \item What is the central research problem?
-   \item What is the topic of study related to that research problem?
-    \item What methods should be used to analyze the research problem?
-   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
-\end{enumerate}
+Our research revolves around the latest in smart lock technology from Lenels BlueDiamond range.
+We will use a variety of previously proven methods to attempt to make an unauthorized bypass of the access control upheld be these devices.
+Methods including physical testing of the wiegand hardware within the device, code review of the device firmware, and analysis of the connection between the device and compatible mobile app for potential vulnerabilities.
+
+Smart locks are the future of physical access control technology, and research from us and other likeminded individuals will ensure that the smart locks deployed in the future are free from as many known issues as possible.
+Our results determine that...
+\todo{put results here}
 

### 2020-03-09 paper/wireframe/wireframe.tex

--- 2020-03-09 paper/wireframe/wireframe.tex
@@
 \section{Background \& Significance}
-This is where you explain the context of your paper and describe in detail why it's important.
-It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper.
-Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do.
-Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.
-
-To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:
+The purpose of this research is to test the security properties of the Lenel Blue Diamond Readers and to uncover different vulnerabilities in them so that they can be disclosed properly and eventually patched.
+Lenel has over 1 million Blue Diamond readers deployed in multiple industries, the most notable one being real-estate \cite{lenelbluediamondwebsite}.
+This study is important because the security of these locks are very important because if someone unauthorized is able to enter through these locked doors, everything on the other side would be compromised including important data, objects, and even people.
+Things which if they were compromised would result in extreme loss.
+For our research the major issues we found fall into three categories, the firmware used on the lock, the physical aspect of the lock, and the usage of the mobile app and bluetooth communication.
+We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers.
+We plan to conduct our research by using trusted sources on the subject and testing their conclusions on Lenel Blue Diamond readers.
+Our research has it bounds inside the Lenel Blue Diamond readers mobile app and lock itself.
+We will
 

### 2020-03-09 paper/wireframe/wireframe.tex
Redid bib, removed comments

@@
 \begin{abstract}
-%The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
-%
-%An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
-It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding.
-The abstract should be broadly accessible (i.e.
-able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.
-%
-%Structure the abstract as follows: background and aims, methods, results and conclusion. 
-%
-%Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
 
@@
 These methods included assessments of physical hardware, firmware, and connected BlueDiamond mobile app for vulnerabilities and could result in a breach of access control.
-Our testing found that...
-\todo{Put results here}
 
@@
 
-\section*{Keywords}
-%Select keywords with care, because they will help users discover your paper.
-To determine appropriate keywords, put yourself in the position of someone who is trying to search for a paper like yours.
-What search terms would you use?
-From those terms, select a list of at least three and no more than five words.
-Include these words in the text of the abstract and if at all possible, in the title of the paper.
-\todo{add keywords}
+\section{Keywords}
+
+Bluetooth
 
 \section{Introduction}
-%Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself!
-Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it.
-%
-%Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}.
-Scroll on down to the bibliography section of the \LaTeX\ code if you'd like to see the other end of the built-in references system.
-The numbering is all handled in-house -- you just have to assign each reference a key, and Overleaf takes care of the rest.
-%
-%On with the actual introduction!
-The introduction should provide context and background information appropriate for an academic audience.
-It should state a focused research question, define the variables being studied, and make clear the objective, importance, and relevance of the work.
-%
-%Here is where you'd introduce the context surrounding your study.
-What led you to the question you ended up asking?
-Why is it relevant?
-Which fields of science is your question based around?
-What has previous literature demonstrated?
-%
-%While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it.
-Obviously, excessive detail is not necessary (that's what the next section is for).
-Lastly, be sure to make mention of the potential implications of your findings, but once again remember that you'll be going into more detail about that in the discussion.
-%
-%\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem.
-After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.
-%
-%Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
-%\begin{enumerate}
-%   \item What is the central research problem?
-%   \item What is the topic of study related to that research problem?
-%    \item What methods should be used to analyze the research problem?
-%   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
-%\end{enumerate}
 
@@
 Smart locks are the future of physical access control technology, and research from us and other likeminded individuals will ensure that the smart locks deployed in the future are free from as many known issues as possible.
-Our results determine that...
-\todo{put results here}
 
@@
 Our research has it bounds inside the Lenel Blue Diamond readers mobile app and lock itself.
-We will
-
-\begin{itemize}
-   \item State the research problem and give a more detailed explanation about the purpose of the study than what you stated in the introduction.
-This is particularly important if the problem is complex or multifaceted.
-    \item Present the rationale of your proposed study and clearly indicate why it is worth doing; be sure to answer the "So What? question [i.e., why should anyone care].
-    \item Describe the major issues or problems to be addressed by your research.
-This can be in the form of questions to be addressed.
-Be sure to note how your proposed study builds on previous assumptions about the research problem.
-    \item Explain the methods you plan to use for conducting your research. Clearly identify the key sources you intend to use and explain how they will contribute to your analysis of the topic.
-   \item Describe the boundaries of your proposed research in order to provide a clear focus.
-Where appropriate, state not only what you plan to study, but what aspects of the research problem will be excluded from the study.
-   \item If necessary, provide definitions of key concepts or terms.
-\end{itemize}
 
@@
 \end{itemize}
-
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=0.4\textwidth]{test.png}
-%  \caption{Notice how \LaTeX\ automatically numbers this figure.}
-%\end{figure}
 
@@
 \section{Acknowledgements}
-In the Acknowledgements section, the author(s) acknowledge or thank any persons or institutions who helped support the work in any way.
-In particular, this section must disclose any funding for the research completed, including the grant number (if a grant was awarded).
-
-Anyone to thank/credit for helping your team along the way? This is the place to do it.
-
-\section{Appendix}
-Appendices are optional sections that should include additional tables, figures, or other data beyond what is included in the results section.
-An appendix should be able to stand separately from the prinicpal article.
-Therefore, no references (callouts) to appendix figures or tables should be made in the principal article.
-If required, the appendix should have its own bibliographic reference list with citations to that list confined to the appendix.
-\cite{latexcompanion}
+We would like to thank Lenel for access to their BlueDiamond lock and permission to conduct a test of its security.
 
@@
 
-\bibentry{test}
+\bibentry{lenelbluediamondwebsite}
 

### 2020-03-09 paper/wireframe/wireframe.tex
added preliminary suppositions

@@
 \section{Preliminary Suppositions \& Implications}
-Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
+\begin{itemize}
+    \item A lot of research appears to be out of date in the field of lock security.
+    \item This research will cover Carrier/Lenel's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
+    \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
+    \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
+    \item This research will provide a baseline for future work in evaluating locks from different vendors
+\end{itemize}
+#Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
 The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation.

### 2020-03-09 paper/wireframe/wireframe.tex
updated conclusion, preliminary suppositions

@@
     \item A lot of research appears to be out of date in the field of lock security.
-    \item This research will cover Carrier/Lenel's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
+    \item This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
     \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
     \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
-    \item This research will provide a baseline for future work in evaluating locks from different vendors
-\end{itemize}
-#Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
-The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation.
-Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking.
-Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.
-
-When thinking about the potential implications of your study, ask the following questions:
-\begin{itemize}
-    \item What might the results mean in regards to challenging the theoretical framework and underlying assumptions that support the study?
-    \item What suggestions for subsequent research could arise from the potential outcomes of the study?
-    \item What will the results mean to practitioners in the natural settings of their workplace?
-    \item Will the results influence programs, methods, and/or forms of intervention?
-    \item How might the results contribute to the solution of social, economic, or other types of problems?
-    \item Will the results influence policy decisions?
-    \item In what way do individuals or groups benefit should your study be pursued?
-    \item What will be improved or changed as a result of the proposed research?
-    \item How will the results of the study be implemented and what innovations or transformative insights could emerge from the process of implementation?
+    \item This research will provide a baseline for future work in evaluating locks from different vendors.
+    \item If critical vulnerabilities are discovered, these vulnerabilities could potentially be used to take over many organizations that rely on Lenel/BlueDiamond technology for access control. 
 \end{itemize}
 
-\textbf{NOTE:} This section should not delve into idle speculation, opinion, or be formulated on the basis of unclear evidence.
-The purpose is to reflect upon gaps or understudied areas of the current literature and describe how your proposed research contributes to a new understanding of the research problem should the study be implemented as designed.
-
 \section{Conclusions}
-The conclusion reiterates the importance or significance of your paper and provides a brief summary of the entire study.
-This section should be only one or two paragraphs long, emphasizing why the research problem is worth investigating, why your research study is unique, and how it should advance existing knowledge.
-
-Someone reading this section should come away with an understanding of:
 \begin{itemize}
-    \item Why the study should be done,
-    \item The specific purpose of the study and the research questions it attempts to answer,
-    \item The decision to why the research design and methods used where chosen over other options,
-    \item The potential implications emerging from your proposed study of the research problem, and
-    \item A sense of how your study fits within the broader scholarship about the research problem.
+    \item Go over the conclusions found in the paper.
+    \item Remark on the potential implications of the findings.
+    \item Express a baseline on how other researchers can start to go about testing other IOT lock technology.
+    \item Document the ease of finding such vulnerabilities.
 \end{itemize}

### 2020-03-09 paper/wireframe/wireframe.tex
update wireframe to latest

@@
     \item A lot of research appears to be out of date in the field of lock security.
-    \item This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
+    \item This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the author's knowledge has not been tested in an academic enviornment before.
     \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.

### 2020-03-09 paper/wireframe/wireframe.tex

--- 2020-03-09 paper/wireframe/wireframe.tex
@@
 
-Connected to the background and significance of your study is a section of your paper devoted to a more deliberate review and synthesis of prior studies related to the research problem under investigation.
-The purpose here is to place your project within the larger whole of what is currently being explored, while demonstrating to your readers that your work is original and innovative.
-Think about what questions other researchers have asked, what methods they have used, and what is your understanding of their findings and, when stated, their recommendations.
-
-Since a literature review is information dense, it is crucial that this section is intelligently structured to enable a reader to grasp the key arguments underpinning your proposed study in relation to that of other researchers.
-A good strategy is to break the literature into "conceptual categories" [themes] rather than systematically or chronologically describing groups of materials one at a time.
-Note that conceptual categories generally reveal themselves after you have read most of the pertinent literature on your topic so adding new categories is an on-going process of discovery as you review more studies.
-How do you know you've covered the key conceptual categories underlying the research literature?
-Generally, you can have confidence that all of the significant conceptual categories have been identified if you start to see repetition in the conclusions or recommendations that are being made.
-
-\textbf{NOTE:} Do not shy away from challenging the conclusions made in prior research as a basis for supporting the need for your paper.
-Assess what you believe is missing and state how previous research has failed to adequately examine the issue that your study addresses.
-For more information on writing literature reviews, go to: \url{https://libguides.usc.edu/writingguide/literaturereview}.
-
-To help frame your paper's review of prior research, consider the "five C’s" of writing a literature review:
 \begin{itemize}
-    \item Cite, so as to keep the primary focus on the literature pertinent to your research problem.
-    \item Compare the various arguments, theories, methodologies, and findings expressed in the literature: what do the authors agree on?
-Who applies similar approaches to analyzing the research problem?
-    \item Contrast the various arguments, themes, methodologies, approaches, and controversies expressed in the literature: describe what are the major areas of disagreement, controversy, or debate among scholars?
-    \item Critique the literature: Which arguments are more persuasive, and why?
-Which approaches, findings, and methodologies seem most reliable, valid, or appropriate, and why?
-Pay attention to the verbs you use to describe what an author says/does [e.g., asserts, demonstrates, argues, etc.].
-    \item Connect the literature to your own area of research and investigation: how does your own work draw upon, depart from, synthesize, or add a new perspective to what has been said in the literature?
+    \item In Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks, Robberts and Toft use GATT attacks to Man-in-the-Middle an application and a lock to conduct Bluetooth attacks.
+Not much digging was done in the way of breaking the cryptographic protocols.
+    \item In Security Vulnerabilities of Bluetooth Low Energy Technology (BLE), O'sullivan found that the communication protocols in BLE were extremely vulnerable to attack.
+    \item There is a lot of focus attacking the GATT and GAP elements of BLE. Some research indicates that the Short Term and Long Term keys are brute forceable, but it has yet to be seen. 
 \end{itemize}
@@
 \section{Preliminary Suppositions \& Implications}
-\begin{itemize}
-    \item A lot of research appears to be out of date in the field of lock security.
-    \item This research will cover Carrier/Lenel's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
-    \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
-    \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
-    \item This research will provide a baseline for future work in evaluating locks from different vendors
-\end{itemize}
-#Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
+Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
 The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation.

### 2020-03-23 paper/sourceSummaries/summary6.tex
prepped for the future summaries
added my section and updated future files
Added summary 6

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 6}
 
@@
 
+\noindent
+\subsection{Bluetooth: With Low Energy comes Low Security}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{rmike13}
+
+\subsubsection{Main Idea}
+
+\noindent
+The simplification of Bluetooth Low Energy to reduce power use caused a number of security issues.
+The author gives an overview of Bluetooth Low Energy, BLE packet injection, and encryption weaknesses.
+
+\subsubsection{Theory}
+
+\noindent
+This paper is utilizing Game Theory. The author attacks the BLE protocol in a zero sum game.
+
+\subsubsection{Method}
+
+\noindent
+The author implements several types of Bluetooth attacks utilizing an Ubertooth: eavesdropping, packet injection, and bypassing encryption.
+He then explores the flaws and devises a number of mitigations to fix the issues present.
+
+\subsubsection{Findings}
+
+\noindent
+The author found that attacking BLE is trivial after a few, small technical hurdles.
+To eavesdrop on a BLE device, an attacker needs to know the hop interval, hop increment, access address, and CRC init.
+Ryan used this information to calculate which of the 37 channels the connection would switch to next.
+There are three types of methods to set up a Temporary Key (TK) for BLE, Just Works, with a key of all zeros, a six digit pin, or OOB, which is an agreed out-of-band 128 bit key.
+The author found that this key could be brute forced in less than a second if the device used a six digit pin.
+He can use the TK to derive the Short Term Key, and that to derive the Long Term Key.
+OOB is far harder for an attacker to crack, but exchanging a key out-of-band is difficult and not practical in practice.
+
+\subsubsection{Future Directions}
+
+\noindent
+The author believes that future researchers should investigate main-in-the-middle attacks against Bluetooth devices to increase the effectiveness of the proposed attacks.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-03-29 paper/sourceSummaries/summary6.tex
added joshua's 6th source summary

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
 
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{{L}ock {P}icking in the {E}ra of {I}nternet of {T}hings}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{8887393}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors perform a security analysis of a common Bluetooth Smart Lock created by a major brand.
+A MasterLock was chosen because of the strong brand recognition in the lock segment, with a smaller emphasis on IOT devices.
+
+\subsubsection{Theory}
+
+\noindent
+Game Theory.  The authors perform an attack on a common lock in order to determine inherent weaknesses in the product.
+
+\subsubsection{Method}
+
+\noindent
+The authors conducted an analysis on the backend server API calls.
+They do this by reverse engineering the mobile application for the product.
+From there, valid requests were sent to determine how the API server would handle various different scenarios.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that guest and master codes are statically generated, meaning that they could not be revoked.
+The authors also found that many APIs could be misused to generate unliimited future access codes from the perspectie of a limited guest account.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors discuss the possibility of investigating the bluetooth connection between the lock and the phone.
+Although a limited amount of bluetooth research was done in the authors' testing, a lot more work can be done in investigating the bluetooth link, particularly on guest accounts.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-03-29 paper/sourceSummaries/summary6.tex

--- 2020-03-23 paper/sourceSummaries/summary6.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{L}ock {P}icking in the {E}ra of {I}nternet of {T}hings}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{8887393}
 
@@
 \noindent
-Main Idea
+The authors perform a security analysis of a common Bluetooth Smart Lock created by a major brand.
+A MasterLock was chosen because of the strong brand recognition in the lock segment, with a smaller emphasis on IOT devices.
 
@@
 \noindent
-Theory
+Game Theory.  The authors perform an attack on a common lock in order to determine inherent weaknesses in the product.
 
@@
 \noindent
-Method
+The authors conducted an analysis on the backend server API calls.
+They do this by reverse engineering the mobile application for the product.
+From there, valid requests were sent to determine how the API server would handle various different scenarios.
 
@@
 \noindent
-Findings
+The authors found that guest and master codes are statically generated, meaning that they could not be revoked.
+The authors also found that many APIs could be misused to generate unliimited future access codes from the perspectie of a limited guest account.
 
@@
 \noindent
-Future Directions
+The authors discuss the possibility of investigating the bluetooth connection between the lock and the phone.
+Although a limited amount of bluetooth research was done in the authors' testing, a lot more work can be done in investigating the bluetooth link, particularly on guest accounts.
 

### 2020-03-29 paper/sourceSummaries/summary6.tex

--- 2020-03-23 paper/sourceSummaries/summary6.tex
@@
 \noindent
-\subsection{Title}
+\subsection{Poster: Power Replay Attack in Electronic Door Locks}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{seongyeolPoster}
 
@@
 \noindent
-Main Idea
+The authors theorize that electronic door locks are susceptible to a power replay attack in which an insider modifies the lock with a bypass circuit.
+This circuit can be triggered to provide power to the locking mechanism and unlock the door remotely.
 
@@
 \noindent
-Theory
+The theory shown is game theory, if the lock is susceptible to this attack then it is bypassable and considered insecure.
 
@@
 \noindent
-Method
+The authors attached a Bluetooth capable circuit and LiPo battery to the internal circuitry of the lock.
+This is wired in parallel with the original locking circuit so that the lock will still perform normally while the implant is in place.
 
@@
 \noindent
-Findings
+The authors found that locks from the manufacturers Gateman, Samsung, Mille, and Hyegang are susceptible to this attack.
+A malicious insider could place these implants without being detected and use it to gain access at a later date.
 
@@
 \noindent
-Future Directions
+The authors recommend adding tamper detection circuitry to the locks in order to detect if they have been opened along with additional hardware to detect changes in the internal capacitance.
+These modifications would make it harder to place an implant like this and allow for an easier detection of an existing implant.
 

### 2020-03-30 paper/sourceSummaries/summary6.tex
summary 6 first commit

@@
 \noindent
-\subsection{Title}
+\subsection{{I}nvestigations of {P}ower {A}nalysis {A}ttacks on {S}martcards}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{messerges_dabbish_sloan_1999}
 
@@
 \noindent
-Main Idea
+The main idea of this paper is to analyze power anylysis techniques that had been used in the past to attack the DES encryption protocol.
+The authors then propose a method to model the signal vs noise ratio.
 
@@
 \noindent
-Theory
+The main theory on display during this analysis is game theory, the authors treat the ability to measue power levels from the reader as a win in this scenario.
 
@@
 \noindent
-Method
+The authors were able to measure the power dissipation of the smartcard by reading from the ground pin with the assisstance of a small resistor in series between the VSS pin on the card and the true ground.
 
@@
 \noindent
-Findings
+The authors confimed "that power analysis attacks can be quite powerful and need to be addressed." They also were able to successfully propose a way to model the noise characteristics of the power signal coming from the smartcard in hopes of inspiring future work to secure smartcard software against power analysis attacks.
 
@@
 \noindent
-Future Directions
+The authors suggest that "Future research in this area will investigate power analysis attacks on hardware encryption devices and publickey cryptosystems." At the time this paper was written, AES had not yet been published so there definately room for more work on this topic.
 

### 2020-03-30 paper/sourceSummaries/summary6.tex

--- 2020-03-30 paper/sourceSummaries/summary6.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{A}n efficient access control scheme for smart lock based on asynchronous communication}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{han2019efficient}
 
@@
 \noindent
-Main Idea
+The authors propose an asynchronous and consistent lock access management scheme to avoid unauthorized access through the lock.
+The authors also present a lightweight and efficient tree-based access control solution to such smart lock network’s problems, which enable cascading deletion.
 
@@
 \noindent
-Theory
+Game Theory. The authors propose mitigation techniques for smart locks to defend against different exploits, primarily evasion attacks.
 
@@
 \noindent
-Method
+The authors proposed secure command transmission and a tree based access control system and then evaluated their proposed systems.
+The secure command transmission system is a device centered system that has two phases, the user-lock phase and the user-cloud phase.
+In the user-lock phase, users give an unlock request or forward the commands from the cloud to the smart lock.
+In the user-cloud phase, users are able to send and receive access control commands from the cloud.
+During this process there is a preprocessor in the smart lock that checks the security of incoming requests and determines how to handle them.
+The tree based access control system (TACS) is stored directly on the smart lock and every command from the owner is performed on this tree.
+The smart lock maintains this tree by executing commands sent by the owner.
+When a user’s request comes to TACS, it checks whether the user is authorized to make that request or not.
 
@@
 \noindent
-Findings
+The authors found that against evasion attacks their scheme forces each user to connect to the cloud to get a valid period, which only then can the user unlock the door.
+However adversaries can still unlock the door within the valid period (authors set it to 24 hours) just after being revoked.
+The authors weren’t able to have all information updated immediately after an owner's command is sent due to their asynchronous communication scheme.
+All operations on the tree took less than 100 milliseconds in the authors experiments and in most cases the tree took up less than 1 MB and could store up to 12 nodes.
 
@@
 \noindent
-Future Directions
+Can the scheme used here for smart locks be expanded into other fields? Is there a way to remove the valid window so that adversaries can’t use the lock immediately upon being revoked?
 

### 2020-04-05 paper/sourceSummaries/summary7.tex
prepped for the future summaries
summary 7 first commit

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 7}
 
@@
 
+\noindent
+\subsection{Extracting the Security Features Implemented in a Bluetooth LE Connection}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{zayas18}
+
+\subsubsection{Main Idea}
+
+\noindent
+Many of the IoT devices adopting Bluetooth do not impliment the security features that Bluetooth Special Interest Group developed.
+To promote visability of this issue, the authors have developed an application to extract the security features of a Bluetooth device to test the security of devices.
+
+\subsubsection{Theory}
+
+\noindent
+The authors are utilizing Systems Theory. They are observing how a device interacts with other Bluetooth devices trying to connect to it.
+
+\subsubsection{Method}
+
+\noindent
+The authors developed an Android application for two smartphones, the Zenfone Max 3 and the OnePlus 6.
+They are using  Lenovo HW02 fitness tracker as the second bluetooth device.
+The app extracts logs from the btsnoop log created by Android devices.
+The app can discover security information about the connection from the logs.
+
+\subsubsection{Findings}
+
+\noindent
+When pairing the tracker to the phones the fitness tracker sent the Long Term Key (LTK) to the tracker with no encryption, even though both are using Bluetooth 4.2.
+When using the app, this was not the case.
+Unfortunately the authors did not go into greater detail about what security features were found, only focusing on the inital transfer of the LTK.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors believe that future research should be done in further improving the security of BLE, as it is here to stay.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{C}onfidence in {S}mart {T}oken {P}roximity: {R}elay {A}ttacks {R}evisited
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{hancke2009confidence}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors revisit the fesibility of implementing both passive and active relay attacks against smart tokens.
+They also discuss the security implications should the attackers succeed.
+Finally, the authors discuss possible actions that device owners could take to mitigate the risk of these attacks.
+
+\subsubsection{Theory}
+
+\noindent
+The authors use game theory to explain the red vs blue scenario, treating a win for red as a breach of information and a win for blue as witholding access control.
+
+\subsubsection{Method}
+
+\noindent
+The authors utilize a proxy-token and proxy-reader to create a virtual clone of the authenticated users access card and relay it to the reader.
+This can be done by creating your own hardware or using existing tools.
+The authors chose to implement their own proxy reader and proxy token for this experiment.
+
+\subsubsection{Findings}
+
+\noindent
+the authors were able to successfully perfom a relay attack against an ISO 14443A contactless system using guidelines in public literature and easily obtainable hardware.
+They also found that timing constraints have little to no effect against relay attacks, and although 2FA is effective if nullifies some of the advantages of smart token systems.
+The authors suggest using distance bounding or monitoring using a trusted interface as more effective methods against this attack, although they warn that these methods are generally more expensive or complex.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors leave open the option for further research on methods against relay attacks since they believe that the methods they proposed could be improved upon.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-04-05 paper/sourceSummaries/summary6.tex
added summary and fixed a bib issues

--- 2020-03-30 paper/sourceSummaries/summary6.tex
@@
 \noindent
-\subsection{{L}ock {P}icking in the {E}ra of {I}nternet of {T}hings}
+\subsection{Title}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{8887393}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The authors perform a security analysis of a common Bluetooth Smart Lock created by a major brand.
-A MasterLock was chosen because of the strong brand recognition in the lock segment, with a smaller emphasis on IOT devices.
+Main Idea
 
@@
 \noindent
-Game Theory.  The authors perform an attack on a common lock in order to determine inherent weaknesses in the product.
+Theory
 
@@
 \noindent
-The authors conducted an analysis on the backend server API calls.
-They do this by reverse engineering the mobile application for the product.
-From there, valid requests were sent to determine how the API server would handle various different scenarios.
+Method
 
@@
 \noindent
-The authors found that guest and master codes are statically generated, meaning that they could not be revoked.
-The authors also found that many APIs could be misused to generate unliimited future access codes from the perspectie of a limited guest account.
+Findings
 
@@
 \noindent
-The authors discuss the possibility of investigating the bluetooth connection between the lock and the phone.
-Although a limited amount of bluetooth research was done in the authors' testing, a lot more work can be done in investigating the bluetooth link, particularly on guest accounts.
+Future Directions
 
@@
 \noindent
-\subsection{{I}nvestigations of {P}ower {A}nalysis {A}ttacks on {S}martcards}
+\subsection{Title}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{messerges_dabbish_sloan_1999}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The main idea of this paper is to analyze power anylysis techniques that had been used in the past to attack the DES encryption protocol.
-The authors then propose a method to model the signal vs noise ratio.
+Main Idea
 
@@
 \noindent
-The main theory on display during this analysis is game theory, the authors treat the ability to measue power levels from the reader as a win in this scenario.
+Theory
 
@@
 \noindent
-The authors were able to measure the power dissipation of the smartcard by reading from the ground pin with the assisstance of a small resistor in series between the VSS pin on the card and the true ground.
+Method
 
@@
 \noindent
-The authors confimed "that power analysis attacks can be quite powerful and need to be addressed." They also were able to successfully propose a way to model the noise characteristics of the power signal coming from the smartcard in hopes of inspiring future work to secure smartcard software against power analysis attacks.
+Findings
 
@@
 \noindent
-The authors suggest that "Future research in this area will investigate power analysis attacks on hardware encryption devices and publickey cryptosystems." At the time this paper was written, AES had not yet been published so there definately room for more work on this topic.
+Future Directions
 
@@
 \noindent
-\subsection{Poster: Power Replay Attack in Electronic Door Locks}
+\subsection{Portable RFID Bumping Device}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{seongyeolPoster}
+\bibentry{dijkPortableBumping}
 
@@
 \noindent
-The authors theorize that electronic door locks are susceptible to a power replay attack in which an insider modifies the lock with a bypass circuit.
-This circuit can be triggered to provide power to the locking mechanism and unlock the door remotely.
+The authors proposed that RFID cards may be vulnerable to a high speed cloning attack performed by bumping into the target.
+They posit that this attach can be used to gain clones of security cards without the target's knowledge or raising suspicion.
 
@@
 \noindent
-The theory shown is game theory, if the lock is susceptible to this attack then it is bypassable and considered insecure.
+Game Theory.  By showing the ease of cloning the cards the authors show that they are broken and need increased security in order to stay useful.
 
@@
 \noindent
-The authors attached a Bluetooth capable circuit and LiPo battery to the internal circuitry of the lock.
-This is wired in parallel with the original locking circuit so that the lock will still perform normally while the implant is in place.
+The authors used a Proxmark 3, a LG Nexus 5 with Nethunter, a Hirose usb cable, MIFARE Classic 1K, and MIFARE Classic EV1 1K.
+The authors wrote a default key to the cards and then a large number of random keys.
+They then generated a large number of random keys to try and gathered a large number of nonces to perform their attack.
 
@@
 \noindent
-The authors found that locks from the manufacturers Gateman, Samsung, Mille, and Hyegang are susceptible to this attack.
-A malicious insider could place these implants without being detected and use it to gain access at a later date.
+The authors found that the HF Hirose Antenna increased the range to 6-8cm.
+They also successfully implemented BTWA to read multiple cards.
+The attacks against the cards were successefully performed against both the Classic and the Classic EV1.
 
@@
 \noindent
-The authors recommend adding tamper detection circuitry to the locks in order to detect if they have been opened along with additional hardware to detect changes in the internal capacitance.
-These modifications would make it harder to place an implant like this and allow for an easier detection of an existing implant.
+The authors posit that more research can be done into the maximum number of cards that can be read at one time.
+They also believes that the attack framework can be extended to support more attacks, optimization can be performed on the keyspace calculation software, attempts can be made to try the attack in an unstable environment, and finally optimazation of the Proxmark firmware.
 

### 2020-04-05 paper/sourceSummaries/summary7.tex

@@
 \noindent
-\subsection{C}onfidence in {S}mart {T}oken {P}roximity: {R}elay {A}ttacks {R}evisited
+\subsection{Title}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{hancke2009confidence}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The authors revisit the fesibility of implementing both passive and active relay attacks against smart tokens.
-They also discuss the security implications should the attackers succeed.
-Finally, the authors discuss possible actions that device owners could take to mitigate the risk of these attacks.
+Main Idea
 
@@
 \noindent
-The authors use game theory to explain the red vs blue scenario, treating a win for red as a breach of information and a win for blue as witholding access control.
+Theory
 
@@
 \noindent
-The authors utilize a proxy-token and proxy-reader to create a virtual clone of the authenticated users access card and relay it to the reader.
-This can be done by creating your own hardware or using existing tools.
-The authors chose to implement their own proxy reader and proxy token for this experiment.
+Method
 
@@
 \noindent
-the authors were able to successfully perfom a relay attack against an ISO 14443A contactless system using guidelines in public literature and easily obtainable hardware.
-They also found that timing constraints have little to no effect against relay attacks, and although 2FA is effective if nullifies some of the advantages of smart token systems.
-The authors suggest using distance bounding or monitoring using a trusted interface as more effective methods against this attack, although they warn that these methods are generally more expensive or complex.
+Findings
 
@@
 \noindent
-The authors leave open the option for further research on methods against relay attacks since they believe that the methods they proposed could be improved upon.
+Future Directions
 

### 2020-04-05 paper/sourceSummaries/summary7.tex
summary 7

--- 2020-04-05 paper/sourceSummaries/summary7.tex
@@
 \noindent
-\subsection{Title}
+\subsection{Portable RFID Bumping Device}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{dijkPortableBumping}
 
@@
 \noindent
-Main Idea
+The authors proposed that RFID cards may be vulnerable to a high speed cloning attack performed by bumping into the target.
+They posit that this attach can be used to gain clones of security cards without the target's knowledge or raising suspicion.
 
@@
 \noindent
-Theory
+Game Theory.  By showing the ease of cloning the cards the authors show that they are broken and need increased security in order to stay useful.
 
@@
 \noindent
-Method
+The authors used a Proxmark 3, a LG Nexus 5 with Nethunter, a Hirose usb cable, MIFARE Classic 1K, and MIFARE Classic EV1 1K.
+The authors wrote a default key to the cards and then a large number of random keys.
+They then generated a large number of random keys to try and gathered a large number of nonces to perform their attack.
 
@@
 \noindent
-Findings
+The authors found that the HF Hirose Antenna increased the range to 6-8cm.
+They also successfully implemented BTWA to read multiple cards.
+The attacks against the cards were successefully performed against both the Classic and the Classic EV1.
 
@@
 \noindent
-Future Directions
+The authors posit that more research can be done into the maximum number of cards that can be read at one time.
+They also believes that the attack framework can be extended to support more attacks, optimization can be performed on the keyspace calculation software, attempts can be made to try the attack in an unstable environment, and finally optimazation of the Proxmark firmware.
 

### 2020-04-05 paper/sourceSummaries/summary7.tex
Source 7 Dan

--- 2020-04-05 paper/sourceSummaries/summary7.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{A} {H}olistic {F}ramework for {O}pen {L}ow-{P}ower {I}nternet of {T}hings {T}echnology {E}cosystems}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{hu2018holistic}
 
@@
 \noindent
-Main Idea
+The authors identify the working framework for low-power Iot ecosystems and find out the principle of driving the future trends in the industry and research community.
+The  authors also take a look at IoT technology ecosystems to find four primary business models that can lead to the proposed ecosystem framework.
 
@@
 \noindent
-Theory
+The authors used Systems Theory. They observed how IoT ecosystems work with each other to identify a framework that is holistic.
 
@@
 \noindent
-Method
+The authors found four primary business models for low-power IoT ecosystems which intersect with one another.
+The first is semiconductor-driven models, the second is data service driven models, the third is a vertical application-driven model, and the fourth is a framework-driven model.
+Using these four models the authors created a holistic framework for low-power IoT ecosystems.
 
@@
 \noindent
-Findings
+The author’s framework contains two parts in the front plane.
+The technical IoT building blocks and the common vertical business segments.
+The horizontal business segments are briefly shown on the top plane of the framework.
+The architecture plane indicates the various systems following an architecture based on the common IoT building blocks.
+On the side plane, the commercial and research maker demands are shown as the market driving force of the elements shown on the front plane.
+The authors concluded that AllJoyn and ARM are the successful IoT ecosystems that fit the previously proposed model and framework.
 
@@
 \noindent
-Future Directions
+Is there a way to apply this holistic framework to a real world ecosystem? How do you identify a business model in an IoT technology ecosystem to integrate these technologies?
 

### 2020-04-06 paper/sourceSummaries/summary7.tex
added joshua's 7th source summary

--- 2020-04-05 paper/sourceSummaries/summary7.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{O}n {B}ad {R}andomness and {C}loning of {C}ontactless {P}ayment and {B}uilding {S}mart {C}ards}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{6565237}
 
@@
 \noindent
-Main Idea
+The authors describe the problems with the Mifare Classic RFID card's random number generator and examine the real life implications of bad key generation.
 
@@
 \noindent
-Theory
+Game Theory.  The authors explore the possibility of directly attacking MiFare cards, through the Random Number Generator and otherwise.
 
@@
 \noindent
-Method
+The authors review recent revelations about MiFare random number generation and describe the problem with entropy.
+They then review the probability distribution of the random number generators for Mifare cards.
 
@@
 \noindent
-Findings
+The authors found that random number generators in small cards like the Mifare are often not secure.
+They found that using problems in random number generators allow for very easily breaking security in many smart cards.
 
@@
 \noindent
-Future Directions
+The authors do not describe any formal future directions, but one obvious future direction would be doing research on more vendors of smart cards.
 
@@
 \noindent
-\subsection{Portable RFID Bumping Device}
+\subsection{Title}
 
@@
 %remove % to show citation, change the name to your entry
-\bibentry{dijkPortableBumping}
+%\bibentry{filizzola2018security}
 
@@
 \noindent
-The authors proposed that RFID cards may be vulnerable to a high speed cloning attack performed by bumping into the target.
-They posit that this attach can be used to gain clones of security cards without the target's knowledge or raising suspicion.
+Main Idea
 
@@
 \noindent
-Game Theory.  By showing the ease of cloning the cards the authors show that they are broken and need increased security in order to stay useful.
+Theory
 
@@
 \noindent
-The authors used a Proxmark 3, a LG Nexus 5 with Nethunter, a Hirose usb cable, MIFARE Classic 1K, and MIFARE Classic EV1 1K.
-The authors wrote a default key to the cards and then a large number of random keys.
-They then generated a large number of random keys to try and gathered a large number of nonces to perform their attack.
+Method
 
@@
 \noindent
-The authors found that the HF Hirose Antenna increased the range to 6-8cm.
-They also successfully implemented BTWA to read multiple cards.
-The attacks against the cards were successefully performed against both the Classic and the Classic EV1.
+Findings
 
@@
 \noindent
-The authors posit that more research can be done into the maximum number of cards that can be read at one time.
-They also believes that the attack framework can be extended to support more attacks, optimization can be performed on the keyspace calculation software, attempts can be made to try the attack in an unstable environment, and finally optimazation of the Proxmark firmware.
+Future Directions
 

### 2020-04-12 paper/sourceSummaries/summary8.tex
prepped for the future summaries
added my section and updated future files
Added week 8 summary

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 8}
 
@@
 
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{rfid15}
+
+\subsubsection{Main Idea}
+
+\noindent
+Many companies and people use RFID technology to secure things. The authors look to detail the basics of RFID technology and methods of attacking it.
+
+\subsubsection{Theory}
+
+\noindent
+The authors are using Game Theory.
+
+\subsubsection{Method}
+
+\noindent
+The authors cover the history, features, components, and standards of RFID reader technology.
+They then cover the basic security of these readers for authentication and encryption.
+Finally they cover some basic attacks against RFID readers and details some potential attack scenarios.
+
+\subsubsection{Findings}
+
+\noindent
+The security of existing RFID solutions is not where it should be.
+Due to manufacturers looking to lower costs, these devices tend to lack the security features needed.
+Many of the RFID attacks presented are trivial to carry out and are a significant problem.
+The feasibility of attacks is also dependent on the use of the device.
+Contactless payment cards are far easier to attack than reading specific RFID identifiers.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors provide no indication of a further direction of study.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-04-12 paper/sourceSummaries/summary8.tex
Added joshua's 8th source summary

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
 
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{{O}n {T}he {P}ower {O}f {A}ctive {R}elay {A}ttacks {U}sing {C}ustom-made {P}roxies}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{6810722}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors use custom made hardware in addition to off-the-shelf smartphones to conduct an active relay attacks.
+
+\subsubsection{Theory}
+
+\noindent
+Game theory.  The authors attack an existing security control by replaying wireless signals.
+
+\subsubsection{Method}
+
+\noindent
+The authors researched different types of relay attacks.
+They then investigated the strengths and weaknesses of using custom hardware compared to using off the shelf equipment like a smartphone.
+Given the tight time constraints of the RFID standard, the authors also investigated the round trip time for different scenarios, such as Bluetooth and Wi-Fi.
+The authors then investigated different restrictions in the standard, non-rooted Android operating system in terms of cloning cards.
+Finally, they used this information to build a custom relay device.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that it is possible to use multiple smartphones on a conventional channel such as Bluetooth or Wi-Fi to relay a RFID card over a long distance using some vulnerabilities in the RFID standard.
+These vulnerabilities allow for the device to slow down the transaction rate using specially crafted packets.
+In addition, the authors built custom hardware that performed very well for these types of attacks.
+The authors compared this custom hardware to that of the ProxMark, or OpenPICC RFID-hacking hardware projects.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors did not specify any future directions.
+However, a logical step here would be to look into different protocols that might theoretically allow for longer range.
+For example, could the Author's solution allow for a relay attack over an LTE connection for longer distance?
+Also looking at other, non-tested types of cards could be a possible future direction.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-04-12 paper/sourceSummaries/summary8.tex

@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{rfid15}
 
@@
 \noindent
-Main Idea
+Many companies and people use RFID technology to secure things. The authors look to detail the basics of RFID technology and methods of attacking it.
 
@@
 \noindent
-Theory
+The authors are using Game Theory.
 
@@
 \noindent
-Method
+The authors cover the history, features, components, and standards of RFID reader technology.
+They then cover the basic security of these readers for authentication and encryption.
+Finally they cover some basic attacks against RFID readers and details some potential attack scenarios.
 
@@
 \noindent
-Findings
+The security of existing RFID solutions is not where it should be.
+Due to manufacturers looking to lower costs, these devices tend to lack the security features needed.
+Many of the RFID attacks presented are trivial to carry out and are a significant problem.
+The feasibility of attacks is also dependent on the use of the device.
+Contactless payment cards are far easier to attack than reading specific RFID identifiers.
 
@@
 \noindent
-Future Directions
+The authors provide no indication of a further direction of study.
 

### 2020-04-12 paper/sourceSummaries/summary8.tex
summary 8 initial commit

--- 2020-04-12 paper/sourceSummaries/summary8.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{BLE} {B}roadcasting {I}mpact in a {R}eal {N}etwork {E}nvironment}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{boric2017ble}
 
@@
 \noindent
-Main Idea
+The Authors examine the traffic sent by individual BLE devices to determine the impact these devices can have on latency in a simulation production environment.
+They also do tests to determine whether or not broadcast advertisement length has any effect on message delivery.
 
@@
 \noindent
-Theory
+The authors use Scientific Theory to observe and explain the outcome of the experiment following numerous tests adhering to the scientific method.
 
@@
 \noindent
-Method
+A Raspberry Pi 2 Model B was used as the base testing hardware for this experiment.
+In order to achieve the results that they did, the authors also had to equip the device with a Bluefruit LE Sniffer and some specific Bluetooth libraries that are not supported out of the box by raspberry pi (libdbus-1-dev,  libdbus-glib-1-dev,  libglib2.0-dev,  libical-dev, libreadline-dev, libudev-dev, libusb-dev)
 
@@
 \noindent
-Findings
+The authors found that the neither the duration of advertisement nor the distance between the advertiser and the collector affect the I/O capabilities of the advertiser if it is alone on the network.
+However, signs of latency began to show themselves while testing a broadcast with 10 other devices on the network.
 
@@
 \noindent
-Future Directions
+The authors suggest future work would include testing advertisement capabilities of devices moving around on the network since they were only testing static location.
+They also suggest testing of a more device dense enviroment to see how the pattern they identified grows with more devices.
 

### 2020-04-12 paper/sourceSummaries/summary8.tex
added summary and fixed errors in references.bib

--- 2020-04-12 paper/sourceSummaries/summary8.tex
@@
 \noindent
-\subsection{Title}
+\subsection{Dismantling iClass and iClass Elite}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{garciaIClass}
 
@@
 \noindent
-Main Idea
+The authors reverse engineer the protocols used in the HID iClass cards in order to find vulnerabilities in the cryptographic algorithms that they implement.
+They posited that since the cards relied on Security Through Obscurity there must be vulnerabilities in the implementation.
 
@@
 \noindent
-Theory
+Game Theory, the others posit that there are vulnerabilities that inherently break the security of the cards.
 
@@
 \noindent
-Method
+The researchers purchased two readers, they discovered that the chipset used can have one block written to which will reset the write only status.
+They then ripped the firmware from the reader for analysis.
+In there analysis of the firmware they discovered multiple vulnerabilities in the cryptographic methods used on the cards.
 
@@
 \noindent
-Findings
+The authors found that the HID iClass cards have weak keys when the three rightmosst bits of each byte are identicle, when updating the key on a card the reader sends the XOR of the old key and the new key which allows for key modification, the readers themselves have privilege escalation weaknesses within the read command, the key diversification algorithm uses DES and a proprietary hash0 which introduce a weak key diversification vulnerability, and they discovered a key recovery attack based off of the key diversification weakness.
+They also found that the iClass Elite cards have a redundant key diversification weakness, a weak key-byte selection within the diversification algorithm, and a key recovery attack based off of those weaknesses.
+The iClass Elite card in fact only needs 15 authentication attempts to recover the master key, something that can be done in under five seconds.
 
@@
 \noindent
-Future Directions
+The authors posit that community reviewed cryptographic algorithms would be better used in the future.
+They also posit that systematic and automated model checking can be implemented in order to detect implementation weaknesses like the privilege escalation vulnerability that was discovered in the iClass cards.
 

### 2020-04-12 paper/sourceSummaries/summary8.tex
Source 8

--- 2020-04-12 paper/sourceSummaries/summary8.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{S}mart-lock security re-engineered using cryptography and steganography}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{bapat2017smart}
 
@@
 \noindent
-Main Idea
+The authors attempt to analyze the MITM vulnerability of BLE and develop a possible solution for designing smart-locks with an increased level of security.
+The authors show that using image steganography and cryptography together helps mitigate vulnerabilities of BLE protocol.
 
@@
 \noindent
-Theory
+Game Theory. The authors propose mitigation techniques for MITM attacks in BLE.
 
@@
 \noindent
-Method
+The authors propose a solution based on using the advantages of both steganography and cryptography which will increase the level of security.
+The techniques of cryptography and steganography are used to provide security to smart locks.
+A user first enters the passkey via the android app.
+Later, an image is selected for the passkey to be embedded into.
+Using AES encryption, the passkey is encrypted and then encoded in the image which all happens on the client side.
+The image is sent over BLE 4.0 to the Raspberry Pi.
+The image is then decoded and decrypted and the passkey is recovered and if it’s correct the smart lock is opened.
+The authors ran tests on the efficiency of the solution.
 
@@
 \noindent
-Findings
+In the authors testing they found that there is a linear relationship between the image size and BLE transfer time which means small images transfer faster.
+For example, the authors found that an 6.97kb image took 19.8 seconds while an image 1100kb took 137 seconds.
+The authors also showed images in the paper before and after encoding and concluded that the images had no visual differences between each other.
 
@@
 \noindent
-Future Directions
+Can we make an implementation for the solution that the authors demonstrate?
+Is there a way to speed up the time constraint without cutting back on security?
+Can this solution be used to protect other systems from MITM attacks or are there any flaws with the solution shown?
 

### 2020-04-12 paper/sourceSummaries/summary8.tex

--- 2020-04-12 paper/sourceSummaries/summary8.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{O}n {T}he {P}ower {O}f {A}ctive {R}elay {A}ttacks {U}sing {C}ustom-made {P}roxies}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{6810722}
 
@@
 \noindent
-Main Idea
+The authors use custom made hardware in addition to off-the-shelf smartphones to conduct an active relay attacks.
 
@@
 \noindent
-Theory
+Game theory.  The authors attack an existing security control by replaying wireless signals.
 
@@
 \noindent
-Method
+The authors researched different types of relay attacks.
+They then investigated the strengths and weaknesses of using custom hardware compared to using off the shelf equipment like a smartphone.
+Given the tight time constraints of the RFID standard, the authors also investigated the round trip time for different scenarios, such as Bluetooth and Wi-Fi.
+The authors then investigated different restrictions in the standard, non-rooted Android operating system in terms of cloning cards.
+Finally, they used this information to build a custom relay device.
 
@@
 \noindent
-Findings
+The authors found that it is possible to use multiple smartphones on a conventional channel such as Bluetooth or Wi-Fi to relay a RFID card over a long distance using some vulnerabilities in the RFID standard.
+These vulnerabilities allow for the device to slow down the transaction rate using specially crafted packets.
+In addition, the authors built custom hardware that performed very well for these types of attacks.
+The authors compared this custom hardware to that of the ProxMark, or OpenPICC RFID-hacking hardware projects.
 
@@
 \noindent
-Future Directions
+The authors did not specify any future directions.
+However, a logical step here would be to look into different protocols that might theoretically allow for longer range.
+For example, could the Author's solution allow for a relay attack over an LTE connection for longer distance?
+Also looking at other, non-tested types of cards could be a possible future direction.
 

### 2020-04-14 paper/sourceSummaries/summary9.tex
prepped for the future summaries
Added summary 9

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 9}
 
@@
 
+\noindent
+\subsection{Classifying RFID attacks and defenses}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{mitrokotsa09}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors classify existing RFID attacks and discuss possible countermeasures.
+
+\subsubsection{Theory}
+
+\noindent
+The authors are using Classification Theory. RFID attacks are being split into subgroups based on similarities and differences.
+
+\subsubsection{Method}
+
+\noindent
+The authors classify attacks based on the layer where the attack takes place: physical layer, network-transport layer, application layer, strategic layer, and multilayer.
+They discuss the attacks and offer possible solutions to the issues.
+
+\subsubsection{Findings}
+
+\noindent
+The authors found that most of the attacks possible against RFID were at the physical layer via passive and active interference methods such as sending KILL commands, replay attacks, or destruction of the tags.
+Multiplayer attacks were only cryptobased attacks.
+Network-Transport layer had the tag attacks that are more common, such as cloning and spoofing.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors offer no indication of a future direction.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-04-19 paper/sourceSummaries/summary10.tex
prepped for the future summaries

--- 2020-02-06 paper/sourceSummaries/summary2.tex
@@
-\section{Summary 2}
+\section{Summary 10}
 
@@
 
+\noindent
+\subsection{Trust and Security in RFID-Based Product Authentication System}
+
+\subsubsection{Group Member}
+
+\noindent
+Connor Leavesley
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+\bibentry{lehtonen07}
+
+\subsubsection{Main Idea}
+
+\noindent
+The authors examine the trust and security of RFID authentication systems using a chain-of-trust model.
+
+\subsubsection{Theory}
+
+\noindent
+The authors are using Classification Theory. A trust model is being constructed based on cases of misuse.
+
+\subsubsection{Method}
+
+\noindent
+The authors first agree on a definition of authentication.
+They use this definition to define a several types of authentication, such as location-based authentication.
+The authors construct the chains of trust and they look at threats and attacks.
+They then look at these chains for the risk of certain paths happening.
+
+\subsubsection{Findings}
+
+\noindent
+RFID trust chains are highly complex and there are many threats faced in each chain.
+These chains are an effective method of mapping out trust and the threats faced to help authentication designers better secure their RFID environment.
+
+\subsubsection{Future Directions}
+
+\noindent
+The authors offer no indication of a future direction of research.
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Joshua Niemann
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Jacob Ruud
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
+
+\noindent
+\subsection{Title}
+
+\subsubsection{Group Member}
+
+\noindent
+Quintin Walters
+
+\noindent
+\subsubsection{Citation}
+
+\Urlmuskip=0mu plus 1mu\relax
+%remove % to show citation, change the name to your entry
+%\bibentry{filizzola2018security}
+
+\subsubsection{Main Idea}
+
+\noindent
+Main Idea
+
+\subsubsection{Theory}
+
+\noindent
+Theory
+
+\subsubsection{Method}
+
+\noindent
+Method
+
+\subsubsection{Findings}
+
+\noindent
+Findings
+
+\subsubsection{Future Directions}
+
+\noindent
+Future Directions
+
+\Urlmuskip=0mu plus 1mu\relax
 \pagebreak

### 2020-04-19 paper/sourceSummaries/summary9.tex
summary 9 initial commit

@@
 \noindent
-\subsection{Title}
+\subsection{{P}ractical {B}luetooth {T}raffic {S}niffing: {S}ystems and {P}rivacy {I}mplications}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{albazrqaoe2016practical}
 
@@
 \noindent
-Main Idea
+The authors discuss privacy concerns that exist with the prevalence of bluetooth sniffing in todays iot landscape.
+During their discussion they propose a device of their own creation that can sniff bluetooth traffic effectively using commercially available bluetooth-compliant radios.
 
@@
 \noindent
-Theory
+Game theory is used in this paper as a method of measuring success of the new reader design; Where a win is represented by the readers ability to sniff blbluetooth traffic.
 
@@
 \noindent
-Method
+The authors improve upon the design of the Ubertooth reciever by modifying the source code to add support for adaptive hop selection and run-time clock synchronization.
+They also found that the firmware implementation of real-time frequency hopping needed updating to achieve the results they were aiming for.
 
@@
 \noindent
-Findings
+The authors found that their ubertooth implementation is significantly more efficiant than any previous implementation, but does not accommadate for low energy traffic.
+Therefore their algorithm would need to be modified in order to sniff Bluetooth Low Energy traffic as effectively as they were able to sniff normal bluetooth traffic.
 
@@
 \noindent
-Future Directions
+The authors point out that their bluetooth sniffer implementation is not configured for BLE traffic.
+They outline in their paper that some modifications would need to be made to their source code in order for this functionality to be added.
 

### 2020-04-20 paper/sourceSummaries/summary9.tex
added summary

--- 2020-04-14 paper/sourceSummaries/summary9.tex
@@
 \noindent
-\subsection{Title}
+\subsection{Securing RFID systems by detecting tag cloning}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{lehtonen09}
 
@@
 \noindent
-Main Idea
+Cloning RFID cards bypasses the security that they provide.  Detecting the use of cloning could increase the security of an RFID card based solution.
 
@@
 \noindent
-Theory
+Game theory, if cards can be cloned then the security of the system is completely compromised.
 
@@
 \noindent
-Method
+The researchers developed a system that would record the synchronized secret on the card.
+It would then check if the secret is identical to the most recent secret written to it.
+They used EPC Class-1 Gen-2 tags from UPM Raflatac and a CAEN A828EU UHF reader.
+Using 100 reads they attempted to use this method to detect cloning.
 
@@
 \noindent
-Findings
+The authors found that a triggered alarm would be valid 50\% of the time and that a 99.15\% of cloned cards would trigger an alarm.
+This has a high false positive rate but a very low false negative rate.
 
@@
 \noindent
-Future Directions
+The authors do not present possible future directions, however, a possible future direction is to test this implementation with more card types and readers along with testing on an active audience to get more accurate results.
 

### 2020-04-20 paper/sourceSummaries/summary9.tex
Summary 9 Daniel Capps

--- 2020-04-19 paper/sourceSummaries/summary9.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{P}rox-{R}{B}{A}{C}: a proximity-based spatially aware {R}{B}{A}{C}}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{kirkpatrick2011prox}
 
@@
 \noindent
-Main Idea
+The authors extend spatially aware role-based access control (RBAC) by defining proximity-based RBAC (Prox-RBAC).
+In the author’s method the access control decisions are made by considering the primary user’s location and the location of every other user in the system.
+The authors introduce a spatial model and proximity constraints.
+The authors also define the Prox-RBAC language which is used to specify policy constraints, introduce their enforcement architecture, and present an informal security analysis.
 
@@
 \noindent
-Theory
+The authors use Game Theory because they have to prove that their implementation is secure against different attack vectors.
 
@@
 \noindent
-Method
+The authors implemented a Prox-RBAC prototype in which they use a centralized authorization server with different clients.
+In their implementation the clients could be either stationary or mobile devices but would be required to provide a high-integrity proof of location.
+The authors Prox-RBAC prototype is built on the interaction between four principals.
+The authorization server (AS) is the centralized server that acts as the policy decision point (PDP).
+The AS maintains a mapping of all users’ locations and all access control policies.
+Each user (subject) s will have an id, a password, and a proximity-connection device that is used for generating the proof of location.
+This device has a secret and a certificate signed by the AS that allows the device to prove they know the secret without the server knowing the secret.
 
@@
 \noindent
-Findings
+The authors developed a prototype of Prox-RBAC to measure the performance of the cryptographic protocols and enforcement algorithms.
+The Prove construct uses the Feige-Fiat-Shamir identification protocol which uses a zero-knowledge proof.
+The Commit and Open primitives use Pedersen commitment.
+For authentication the authors use a salted hash of a password.
+The Hash, Enck, Encpk(c), and Signk primitives use SHA-256, AES-256, 1024-bit RSA, and SHA-1 with DSA in order.
+After 500 tests, the Pedersen commitment (37.9 ms) and RSA (35.9 ms) were the most expensive cryptographic operations while the rest with the exception of DSA signature (9.8 ms) required less than 1 ms to complete on average.
 
@@
 \noindent
-Future Directions
+Is there a better implementation of Feige-Fiat-Shamir and Pedersen that doesn’t use the BigInteger java library so said protocols can be used in different configurations?
+Can we use the results of this paper to construct a usable and efficient proximity-based RBAC system?
 

### 2020-04-20 paper/sourceSummaries/summary9.tex
added joshua's 9th source summary

@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{5116218}
 
@@
 \noindent
-Main Idea
+The authors analyze the encryption of the Bluetooth protocol and highlight insecure elements in the design.  The authors also highlight how these problems could be fixed.
 
@@
 \noindent
-Theory
+Game Theory.  The authors are theoretically attacking the encryption standard used in bluetooth.
 
@@
 \noindent
-Method
+The authors reviewed elements of the Bluetooth encryption stacked, and picked out issues as they found them.
 
@@
 \noindent
-Findings
+The authors found that Bluetooth can not be considered secure compared to conventional fixed networks.  There are too many implementation errors.
 
@@
 \noindent
-Future Directions
+The authors do not specify future directions, but the paper is old by tech standards, and could be updated with information from newer bluetooth standards, like Bluetooth 5.0.
 

### 2020-04-25 paper/sourceSummaries/summary10.tex
summary 10 initial commit

@@
 \noindent
-\subsection{Title}
+\subsection{{Experimental} {Design}}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{kirk2012experimental}
 
@@
 \noindent
-Main Idea
+Author Roger E.
+Kirk explains in depth the process for designing experiments that yield the most significant and meaningful results.
+He builds off of work done by Sir Ronald Fisher in the early 20th century, as well as touches on some items to be wary of when undertaking this process.
 
@@
 \noindent
-Theory
+This paper aims to effectively use scientific theory to aid researchers in properly exploring their research topics.
 
@@
 \noindent
-Method
+The author analyzes numerous types of experimental design with two main goals the mind.
+The first being to establish a causal connection between the independent and dependent variables, and the second being to extract the maximum amount of information with the minimum expenditure of resources.
 
@@
 \noindent
-Findings
+The author presents no clear comparison data as findings to his readers, and instead leaves the decision up to his readers to interperet his data however they see fit for the benefit of their experiment.
 
@@
 \noindent
-Future Directions
+In this section of his reasearch, the author suggests no future directions to continue his work.
 

### 2020-04-26 paper/sourceSummaries/summary10.tex
Last source summary :tear:

--- 2020-04-19 paper/sourceSummaries/summary10.tex
@@
 \noindent
-\subsection{Title}
+\subsection{Designing and implementing malicious hardeware}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{kignDesigning08}
 
@@
 \noindent
-Main Idea
+The authors propose that attackers can design and attack malicious hardware to carry out attacks rather than attack the software.
+They also propose that this attack vector is harder to detect and would bypass security implemented at the software level.
 
@@
 \noindent
-Theory
+Game Theory.  The authors propose and attempt an attack vector that would bypass the security of a system entirely.
 
@@
 \noindent
-Method
+The authors designed two different "Illinois Malicious Processors" to be placed on the victim hardware and they created three attacks to implement with this hardware.
+The IMPs were made using modified Leon3 processors.
+The first design attacked the memory of the victim hardware and their second was a complete hardware shim between the victim hardware and the victim software.
+They then developed a Privilege Escalation attack, a login backdoor, and a password stealer.
 
@@
 \noindent
-Findings
+The authors found that their attacks added less than 0.1 percent more logic gates to the base system and they propose that this would be even less on a larger, more complicated victim.
+They also found that compared to the normal operations of the system a one time attack only increased the operation time by 1.34\% and a persistent attack only increased the operation time by 13.0\%.
 
@@
 \noindent
-Future Directions
+The authors do not propose any specific future work, however, it would be beneficial to continue to develop hardware that would not be detected via current means of supply chain attack detection.
+Most notably analog power analysis, chip identification, and operation timing detection.
 

### 2020-04-26 paper/sourceSummaries/summary10.tex
Added joshua's 10th source summary

--- 2020-04-19 paper/sourceSummaries/summary10.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{R}everse {E}ngineering the {C}ommunications {P}rotocol of an {RFID} {P}ublic {T}ransportation {C}ard}
 
@@
 %remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+\bibentry{7945583}
 
@@
 \noindent
-Main Idea
+The authors use a ProxMark 3 to investigate the feasibility of cloning a two different variants of public transport metro cards used in major cities.
+Both public trasnport cards were from cities based in Spain.
 
@@
 \noindent
-Theory
+Game Theory.  The authors use weaknesses in smart card protocols to allow for easy cloning.
 
@@
 \noindent
-Method
+The authors use a ProxMark 3 RDV to actively scan for RFID cards using a long-range RFID antenna and a ProxMark connected to a laptop in a backpack.
 
@@
 \noindent
-Findings
+The authors did not find a major security issue in the RFID cards they were testing, but instead were concerned with the fact that all communication was done over cleartext channels.
 
@@
 \noindent
-Future Directions
+The authors note that Near Field Communication is partially compatible, and that an Android device may add some interest to future research.
 

### 2020-04-27 paper/sourceSummaries/summary10.tex
source 10

--- 2020-04-26 paper/sourceSummaries/summary10.tex
@@
 \noindent
-\subsection{Title}
+\subsection{{U}nderstanding and improving security and privacy in multi-user smart homes: a design exploration and in-home user study}
 
@@
 \Urlmuskip=0mu plus 1mu\relax
-%remove % to show citation, change the name to your entry
-%\bibentry{filizzola2018security}
+
+\bibentry{zeng2019understanding}
 
@@
 \noindent
-Main Idea
+The authors explore user behaviors, needs and possible solutions to multi-user security and privacy issues in generally non-adversarial smart homes.
+The authors also built a prototype smart home app that includes concrete features like location based access controls, supervisory access controls, and activity notifications.
+The authors tested their prototype with a month long in-home user study which the authors used to re-evaluate their initial design principles and identified challenges and recommendations for smart home designers and researchers.
 
@@
 \noindent
-Theory
+The authors used Game Theory because they’re testing different smart home models against one another and using feedback of users to find the best model by balancing security with usability.
 
@@
 \noindent
-Method
+The authors beginning this paper had two research questions: “How should a smart home be designed to address multi user security and privacy challenges (in generally functional households)?” and “What security and privacy behaviors and needs do these smart home users exhibit in practice?”.
+The authors used initial design principles like access control flexibility, user agency, respect among users, and transparency of smart home behaviors for their smart home model.
+For access control flexibility the authors allowed users to set up multiple access control schemes like role-based, location-based, supervisory, and reactive access control.
+For transparency of smart home behaviors the authors had the users be notified of any changes to the house which include the name of the device, the change in state, and the user or process responsible for causing the change.
+For the user agency the authors used discovery notifications which make clear which devices were nearby and could be used.
 
@@
 \noindent
-Findings
+The authors found in the user study that found misconceptions about their principles.
+For access control flexibility, the authors found that while it’s important to have different access control models available to the user, having too much complexity in the system can cause users to use the minimum security level.
+For user agency and respect, the authors found that most of the houses opted to use social norms to support user agency and minimize conflicts instead of access control.
+For transparency of smart home behaviors, the authors found that they need to look further into the system as users were indifferent to the system.
+Overall the authors showed how complexity can be a barrier to access control use.
 
@@
 \noindent
-Future Directions
+How can we improve the usability of smart home access controls?
+How can we design a smart home model that takes positive household norms into account?
+What security mechanisms can we introduce into this smart house model for adversarial situations?
+How can we create a natural language based access control policy creation for smart homes?
 

### 2020-05-04 paper/paper/paper.tex
updated the citation style
Reformatting paper for premise change

@@
 \begin{abstract}
-The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
 
-An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
-It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding.
-The abstract should be broadly accessible (i.e.
-able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.
-
-Structure the abstract as follows: background and aims, methods, results and conclusion.
-
-Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
 \end{abstract}
@@
 \section*{Keywords}
-Select keywords with care, because they will help users discover your paper.
-To determine appropriate keywords, put yourself in the position of someone who is trying to search for a paper like yours.
-What search terms would you use?
-From those terms, select a list of at least three and no more than five words.
-Include these words in the text of the abstract and if at all possible, in the title of the paper.
+Lenel, BlueDiamond, Bluetooth, BLE, Bluetooth Low Energy, RFID, Wiegand, Reader
 
 \section{Introduction}
-Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself!
-Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it.
-
-Another thing before the introduction; here, I'm going attach a citation to this sentence \cite{latexcompanion}.
-Scroll on down to the bibliography section of the \LaTeX\ code if you'd like to see the other end of the built-in references system.
-The numbering is all handled in-house -- you just have to assign each reference a key, and Overleaf takes care of the rest.
-
-On with the actual introduction!
-The introduction should provide context and background information appropriate for an academic audience.
-It should state a focused research question, define the variables being studied, and make clear the objective, importance, and relevance of the work.
-
-Here is where you'd introduce the context surrounding your study.
-What led you to the question you ended up asking?
-Why is it relevant?
-Which fields of science is your question based around?
-What has previous literature demonstrated?
-
-While the structure of the previous parts of the introduction can be relatively variable, you must make sure to provide a brief overview of the study itself, and the methods you used to accomplish it.
-Obviously, excessive detail is not necessary (that's what the next section is for).
-Lastly, be sure to make mention of the potential implications of your findings, but once again remember that you'll be going into more detail about that in the discussion.
-
-\textbf{For your Auth Paper:} treat your introduction as the initial pitch of an idea or a thorough examination of the significance of a research problem.
-After reading the introduction, your readers should not only have an understanding of what you want to do, but they should also be able to gain a sense of your passion for the topic and to be excited about the study's possible outcomes.
-
-Think about your introduction as a narrative written in \textbf{two to four paragraphs} that succinctly answers the following four questions:
-\begin{enumerate}
-   \item What is the central research problem?
-   \item What is the topic of study related to that research problem?
-    \item What methods should be used to analyze the research problem?
-   \item Why is this important research, what is its significance, and why should someone reading the paper care about the outcomes of the proposed study?
-\end{enumerate}
+Words
 
 \section{Background \& Significance}
-This is where you explain the context of your paper and describe in detail why it's important.
-It can be melded into your introduction or you can create a separate section to help with the organization and narrative flow of your paper.
-Approach writing this section with the thought that you can’t assume your readers will know as much about the research problem as you do.
-Note that this section is not an essay going over everything you have learned about the topic; instead, you must choose what is most relevant in explaining the aims of your research.
-
-To that end, while there are no prescribed rules for establishing the significance of your proposed study, you should attempt to address some or all of the following:
-
-\begin{itemize}
-   \item State the research problem and give a more detailed explanation about the purpose of the study than what you stated in the introduction.
-This is particularly important if the problem is complex or multifaceted.
-    \item Present the rationale of your proposed study and clearly indicate why it is worth doing; be sure to answer the "So What? question [i.e., why should anyone care].
-    \item Describe the major issues or problems to be addressed by your research.
-This can be in the form of questions to be addressed.
-Be sure to note how your proposed study builds on previous assumptions about the research problem.
-    \item Explain the methods you plan to use for conducting your research. Clearly identify the key sources you intend to use and explain how they will contribute to your analysis of the topic.
-   \item Describe the boundaries of your proposed research in order to provide a clear focus.
-Where appropriate, state not only what you plan to study, but what aspects of the research problem will be excluded from the study.
-   \item If necessary, provide definitions of key concepts or terms.
-\end{itemize}
+Words
 
 \section{Related Work}
+Words
 
-Connected to the background and significance of your study is a section of your paper devoted to a more deliberate review and synthesis of prior studies related to the research problem under investigation.
-The purpose here is to place your project within the larger whole of what is currently being explored, while demonstrating to your readers that your work is original and innovative.
-Think about what questions other researchers have asked, what methods they have used, and what is your understanding of their findings and, when stated, their recommendations.
+\section{Research Design \& Methodology}
+Words
 
-Since a literature review is information dense, it is crucial that this section is intelligently structured to enable a reader to grasp the key arguments underpinning your proposed study in relation to that of other researchers.
-A good strategy is to break the literature into "conceptual categories" [themes] rather than systematically or chronologically describing groups of materials one at a time.
-Note that conceptual categories generally reveal themselves after you have read most of the pertinent literature on your topic so adding new categories is an on-going process of discovery as you review more studies.
-How do you know you've covered the key conceptual categories underlying the research literature?
-Generally, you can have confidence that all of the significant conceptual categories have been identified if you start to see repetition in the conclusions or recommendations that are being made.
+\subsection{Definitions}
 
-\textbf{NOTE:} Do not shy away from challenging the conclusions made in prior research as a basis for supporting the need for your paper.
-Assess what you believe is missing and state how previous research has failed to adequately examine the issue that your study addresses.
-For more information on writing literature reviews, go to: \url{https://libguides.usc.edu/writingguide/literaturereview}.
+\subsection{Data Measurement & Analysis}
+Words
 
-To help frame your paper's review of prior research, consider the "five C’s" of writing a literature review:
-\begin{itemize}
-    \item Cite, so as to keep the primary focus on the literature pertinent to your research problem.
-    \item Compare the various arguments, theories, methodologies, and findings expressed in the literature: what do the authors agree on?
-Who applies similar approaches to analyzing the research problem?
-    \item Contrast the various arguments, themes, methodologies, approaches, and controversies expressed in the literature: describe what are the major areas of disagreement, controversy, or debate among scholars?
-    \item Critique the literature: Which arguments are more persuasive, and why?
-Which approaches, findings, and methodologies seem most reliable, valid, or appropriate, and why?
-Pay attention to the verbs you use to describe what an author says/does [e.g., asserts, demonstrates, argues, etc.].
-    \item Connect the literature to your own area of research and investigation: how does your own work draw upon, depart from, synthesize, or add a new perspective to what has been said in the literature?
-\end{itemize}
+\subsection{Procedures}
+Words
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=0.4\textwidth]{test.png}
-%  \caption{Notice how \LaTeX\ automatically numbers this figure.}
-%\end{figure}
+\subsection{Timeline}
+Words
 
-\section{Research Design \& Methods}
-This section must be well-written and logically organized because you are not actually doing the research, yet, your reader must have confidence that it is worth pursuing.
-The reader will never have a study outcome from which to evaluate whether your methodological choices were the correct ones.
-Thus, the objective here is to convince the reader that your overall research design and proposed methods of analysis will correctly address the problem and that the methods will provide the means to effectively interpret the potential results.
-Your design and methods should be unmistakably tied to the specific aims of your study.
-
-Describe the overall research design by building upon and drawing examples from your review of the literature.
-Consider not only methods that other researchers have used but methods of data gathering that have not been used but perhaps could be.
-Be specific about the methodological approaches you plan to undertake to obtain information, the techniques you would use to analyze the data, and the tests of external validity to which you commit yourself [i.e., the trustworthiness by which you can generalize from your study to other people, places, events, and/or periods of time].
-
-When describing the methods you will use, be sure to cover the following:
-\begin{itemize}
-    \item Specify the research process you will undertake and the way you will interpret the results obtained in relation to the research problem.
-Don't just describe what you intend to achieve from applying the methods you choose, but state how you will spend your time while applying these methods [e.g., coding text from interviews to find statements about the need to change school curriculum; running a regression to determine if there is a relationship between campaign advertising on social media sites and election outcomes in Europe].
-    \item Keep in mind that the methodology is not just a list of tasks; it is an argument as to why these tasks add up to the best way to investigate the research problem.
-This is an important point because the mere listing of tasks to be performed does not demonstrate that, collectively, they effectively address the research problem.
-Be sure you clearly explain this.
-    \item Anticipate and acknowledge any potential barriers and pitfalls in carrying out your research design and explain how you plan to address them.
-No method is perfect so you need to describe where you believe challenges may exist in obtaining data or accessing information.
-It's always better to acknowledge this than to have it brought up by your professor.
-    \end{itemize}
-\subsection{Procedures}
-\subsection{Timeline}
 \subsection{Novel Techniques}
+Words
 
 \section{Preliminary Suppositions \& Implications}
-Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications.
-The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation.
-Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking.
-Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.
 
-When thinking about the potential implications of your study, ask the following questions:
-\begin{itemize}
-    \item What might the results mean in regards to challenging the theoretical framework and underlying assumptions that support the study?
-    \item What suggestions for subsequent research could arise from the potential outcomes of the study?
-    \item What will the results mean to practitioners in the natural settings of their workplace?
-    \item Will the results influence programs, methods, and/or forms of intervention?
-    \item How might the results contribute to the solution of social, economic, or other types of problems?
-    \item Will the results influence policy decisions?
-    \item In what way do individuals or groups benefit should your study be pursued?
-    \item What will be improved or changed as a result of the proposed research?
-    \item How will the results of the study be implemented and what innovations or transformative insights could emerge from the process of implementation?
-\end{itemize}
+\subsection{Theoretical Implications}
+Words
 
-\textbf{NOTE:} This section should not delve into idle speculation, opinion, or be formulated on the basis of unclear evidence.
-The purpose is to reflect upon gaps or understudied areas of the current literature and describe how your proposed research contributes to a new understanding of the research problem should the study be implemented as designed.
+\subsection{Practical Implications}
+Words
+
+\section{Expected Outcomes}
 
 \section{Conclusions}
-The conclusion reiterates the importance or significance of your paper and provides a brief summary of the entire study.
-This section should be only one or two paragraphs long, emphasizing why the research problem is worth investigating, why your research study is unique, and how it should advance existing knowledge.
-
-Someone reading this section should come away with an understanding of:
-\begin{itemize}
-    \item Why the study should be done,
-    \item The specific purpose of the study and the research questions it attempts to answer,
-    \item The decision to why the research design and methods used where chosen over other options,
-    \item The potential implications emerging from your proposed study of the research problem, and
-    \item A sense of how your study fits within the broader scholarship about the research problem.
-\end{itemize}
+Words
 
 \section{Acknowledgements}
-In the Acknowledgements section, the author(s) acknowledge or thank any persons or institutions who helped support the work in any way.
-In particular, this section must disclose any funding for the research completed, including the grant number (if a grant was awarded).
+We would like to thank Lenel for access to their BlueDiamond reader and their permission to conduct a test of its security posture.
 
-Anyone to thank/credit for helping your team along the way? This is the place to do it.
-
-\section{Appendix}
-Appendices are optional sections that should include additional tables, figures, or other data beyond what is included in the results section.
-An appendix should be able to stand separately from the prinicpal article.
-Therefore, no references (callouts) to appendix figures or tables should be made in the principal article.
-If required, the appendix should have its own bibliographic reference list with citations to that list confined to the appendix.
-\cite{latexcompanion}
-
-\bibliographystyle{vancouver}
+\bibliographystyle{ieee}
 \bibliography{references}

### 2020-05-05 paper/paper/paper.tex
Added preliminary related work section

@@
 \section{Related Work}
-Words
+There has been much research done into attacking BLE devices.
+Several attacks stood out for their exploitation of vulnerabilities and under developed security features while developing an understanding of the Bluetooth security landscape.
+
+Firstly, Generic Attribute Profile (GATT) attacks are a significant first step in attacking any Bluetooth device.
+By copying the GATT, a Bluetooth device can be mimic and fool applications into connecting to them.
+In Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks, Robberts and Toft utilize gattacker to examine Bluetooth advertisements and discover the services and characteristics of the lock.
+This information is then used to create a copy of the lock and conduct Man-in-the-Middle attacks and test authentication edge cases \cite{KTH}.
+
+O'Sullivan builds on the vulnerabilities present in BLE communication protocol.
+He explains that the BD ADDR field could be fuzzed to determine the source of the communication and forge a connection to it \cite{osullivan}.
+Ryan notes that the underlying encryption protocol of BLE is fundamentally weak and allows for attackers to brute force the Temporary Key.
+That Temporary Key can be used to derive the Long Term Key and break the encryption of the protocol \cite{mryan13}.
+
+Other protocols for IoT communications are not free of issues either.
+Chung shows the Wiegand is still vulnerable to a decade old attack in modern devices.
+An attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server.
+This attack can capture and repeat and authorized card without needing to physically duplicate the card \cite{chung2017wiegand}.
+Hakamaki and Palomaki discuss a number of existing RFID attacks that still exist in modern RFID readers \cite{rfid15}.
 
@@
 \section{Acknowledgements}
-We would like to thank Lenel for access to their BlueDiamond reader and their permission to conduct a test of its security posture.
+We would like to thank Lenel for access to their BlueDiamond reader and their permission to conduct a test of the reader's security posture.
 

### 2020-05-05 paper/paper/paper.tex
fixed problem
add abstract, lets see how many things break

--- 2020-02-25 paper/paper/paper.tex
@@
 \begin{abstract}
-The abstract is in a sense the most important part of your paper, since many readers will scan an abstract first before deciding to invest effort in reading the paper.
-
-An abstract should be about 300 words long at most, and should act as a clear summary of the paper.
-It should state the aim and scope of the research, methods, results and conclusions, and the implications of the paper’s finding.
-The abstract should be broadly accessible (i.e.
-able to be understood by as many people as possible - even those outside the field) and communicate the importance of the work being done.
-
-Structure the abstract as follows: background and aims, methods, results and conclusion.
-
-Examples of some decent abstracts can be found \href{http://journal.stemfellowship.org/userimages/ContentEditor/1451371646443/AbstractExamples.pdf}{here}, with the main ideas highlighted.
+Contactless authentication devices have existed in some capacity since the late 20th century.
+These devices allow users to authenticate themselves using something they have (smart card, proximity card, mobile device, etc) rather than something they know (passcode, combination, security question, etc) making the end-user less responsible for their authentication.
+This puts noticeably more pressure on the manufacturers to provide a product capable of providing confidentiality, integrity, and availability for its users.
+As such, the technology continues to advance as companies come up with newer, more advanced, ways to authenticate securely.
+In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." /cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
+As such, this paper aims to design an experimental process that future researchers may follow to accurately assess the security characteristics of Lenel's BlueDiamond contactless readers.
+This experiment will follow standard scientific procedure, using multiple tests to verify results and standard units of measurement to score success.
+Our analysis of these devices concludes that further testing on the subjects of Wiegand, RFID, Bluetooth, and the physical hardware may uncover significant findings.
 \end{abstract}

### 2020-05-05 paper/paper/paper.tex
i forgot to save my fixes for merge conflicts

--- 2020-05-05 paper/paper/paper.tex
@@
 \begin{abstract}
-
+Contactless authentication devices have existed in some capacity since the late 20th century.
+These devices allow users to authenticate themselves using something they have (smart card, proximity card, mobile device, etc) rather than something they know (passcode, combination, security question, etc) making the end-user less responsible for their authentication.
+This puts noticeably more pressure on the manufacturers to provide a product capable of providing confidentiality, integrity, and availability for its users.
+As such, the technology continues to advance as companies come up with newer, more advanced, ways to authenticate securely.
+In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." /cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
+As such, this paper aims to design an experimental process that future researchers may follow to accurately assess the security characteristics of Lenel's BlueDiamond contactless readers.
+This experiment will follow standard scientific procedure, using multiple tests to verify results and standard units of measurement to score success.
+Our analysis of these devices concludes that further testing on the subjects of Wiegand, RFID, Bluetooth, and the physical hardware may uncover significant findings.
 \end{abstract}
@@
 \subsection{Definitions}
+Words?
 
-\subsection{Data Measurement & Analysis}
+\subsection{Data Measurement \& Analysis}
 Words
@@
 \section{Expected Outcomes}
+Words
 
@@
 
-\bibentry{test}
-
 \end{document}

### 2020-05-05 paper/paper/paper.tex
Changed related research a bit

@@
 Firstly, Generic Attribute Profile (GATT) attacks are a significant first step in attacking any Bluetooth device.
-By copying the GATT, a Bluetooth device can be mimic and fool applications into connecting to them.
-In Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks, Robberts and Toft utilize gattacker to examine Bluetooth advertisements and discover the services and characteristics of the lock.
+By copying the GATT, an attacker can mimic a Bluetooth device and fool applications into connecting to them.
+In Finding Vulnerabilities in IoT Devices: Ethical Hacking of Electronic Locks, Robberts and Toft use gattacker to examine Bluetooth advertisements and discover the services and characteristics of the lock.
 This information is then used to create a copy of the lock and conduct Man-in-the-Middle attacks and test authentication edge cases \cite{KTH}.
@@
 Ryan notes that the underlying encryption protocol of BLE is fundamentally weak and allows for attackers to brute force the Temporary Key.
-That Temporary Key can be used to derive the Long Term Key and break the encryption of the protocol \cite{mryan13}.
+An attacker can use that Temporary Key to derive the Long Term Key and break the encryption of the protocol \cite{mryan13}.
 
+It can be seen in the literature on BLE is very vulnerable to man-in-the-middle attacks, denial of service, packet sniffing, and other vulnerabilities.
+Even though higher levels of security are included in newer BLE versions, such as ECC or out-of-band key exchanges, security settings like PINs are still used by manufacturers \cite{8622000}\cite{jaihc19}\cite{mryan13}.
+A basic attack chain has emerged in the literature where the GATT is copied and an attack is launched to clear the device's Bluetooth pairings \cite{jaihc19}.
+The device is then tricked into pairing with the malicious device.
+The handshake is sniffed by the attacker allowing for encryption to be broken.
 Other protocols for IoT communications are not free of issues either.

### 2020-05-05 paper/paper/paper.tex
Added preliminary data measurement section

@@
 The handshake is sniffed by the attacker allowing for encryption to be broken.
+
 Other protocols for IoT communications are not free of issues either.
@@
 
-\subsection{Definitions}
-Words?
-
 \subsection{Data Measurement \& Analysis}
-Words
+As this is primarily a penetration test of the Lenel BlueDiamond, there are four quantitative metrics of note: number of vulnerabilities, severity, likelihood, and risk.
+A vulnerability is counted if it could be exploited for an unintened effect.
+The severity, likelihood, and risk can be properly measured by the Common Vulnerability Scoring System, or CVSS 3.x.
+This would allow for a more uniform scoring standard inline with what the industry uses.
+Vulnerabilties will be discovered by a number of tools, including devices like the Ubertooth, manual tool usage, and fuzzing.
+Vulnerabilities found would be sorted based on protocol and CVSS score.
+This would allow for a clearer picture into the vulnerabilities for each protocol and the risk associated with using them.
+Once a vulnerability is discovered, an exploit would be attempted to practicality.
+Practicality is to measure the ease of attack.
+It is directly proportional to the likelihood, and provides further insight into likelihood than a CVSS score can.
 
@@
 \section{Preliminary Suppositions \& Implications}
+Words
 

### 2020-05-05 paper/paper/paper.tex
added draft introduction as well as background and significance guide

--- 2020-05-05 paper/paper/paper.tex
@@
 \section{Introduction}
-Words
+Third-party academic research is crucial to ensuring access control devices receive appropriate field testing.
+Untested devices can spell trouble for multiple parties if zero-day vulnerabilities are exploited by unwanted individuals.
+In this case, a breach of access control could lead to unauthorized access to secure facilities and/or compromise of sensitive information.
+Causing potentially fatal damage to organizations without proper backups in place.
+
+Lenel's BlueDiamond technology has been deployed in commercial, academic, and residential settings.
+Making it an ideal target for potential threat actors.
+Our research analyzes these readers from an attackers perspective in an attempt to identify flaws that may lead to unauthorized access.
+We believe this form of research will help improve the overall security posture of these devices as well as provide Lenel with helpful feedback on how their devices can be assessed by the public.
+
+The rest of the paper creates a foundation on which further research may be conducted.
+First we will discuss the background and significance of conducting this research in the first place.
+Second we will discuss related work in this sector that inspired our work on this project.
+Third we will discuss our research design and methodology behind the experiments we chose to recommend.
+Fourth we will discuss recommended data measurement and analysis techniques that we believe will yield the most impactful results.
+Fifth we will discuss preliminary procedure design, novel techniques, and expected timeline to be used in this experiment.
+Sixth, we will make some preliminary, theoretical, and practical implications to help guide the direction of the experiment.
+Finally, we will end with our expected outcomes as well as conclusions to be drawn from this experiment.
 
 \section{Background \& Significance}
-Words
+This  section  should  describe  relevant  security  concepts  related  to  your  topic  and address  historical  work  on  the  subject.
+You  should  assume  that  the  reader  has  a reasonable amount of technical knowledge but is not an expert.
 

### 2020-05-05 paper/paper/paper.tex
Removing novel techniques
Added timeline and procedures

@@
 As such, the technology continues to advance as companies come up with newer, more advanced, ways to authenticate securely.
-In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." /cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
+In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." \cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
 As such, this paper aims to design an experimental process that future researchers may follow to accurately assess the security characteristics of Lenel's BlueDiamond contactless readers.
@@
 \section{Background \& Significance}
-This  section  should  describe  relevant  security  concepts  related  to  your  topic  and address  historical  work  on  the  subject.
-You  should  assume  that  the  reader  has  a reasonable amount of technical knowledge but is not an expert.
+Words
 
@@
 
-It can be seen in the literature on BLE is very vulnerable to man-in-the-middle attacks, denial of service, packet sniffing, and other vulnerabilities.
+It can be seen in the literature on BLE is very vulnerable to man-in-the-middle attacks, denial of service, packet sniffing, and other attacks.
 Even though higher levels of security are included in newer BLE versions, such as ECC or out-of-band key exchanges, security settings like PINs are still used by manufacturers \cite{8622000}\cite{jaihc19}\cite{mryan13}.
@@
 \subsection{Procedures}
-Words
+The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.
+These categories will follow logical attack chains to test a variety of vulnerabilites.
+
+The Bluetooth procedures follow a primary attack chain to test for vulnerabilities.
+The chain starts with either gattacker \cite{GattackingJasek} \cite{BluetoothMITMTal} or CrackLE \cite{10.1145/3190645.3190693} to gain an initial foothold.
+From there, the next step is to test for either injection attacks or injection free attacks \cite{jaihc19} to clear the binding list.
+After the binding list is cleared a man-in-the-middle attack can be attempted \cite{lonzetta2018security} \cite{osullivan} \cite{BluetoothMITMTal}.
+From this point there are multiple attacks that can be attempted.
+The first attack is to attempt to break the long-term key by brute forcing the term key \cite{sevier2019securityofble} \cite{179196}.
+After this replay attacks and active sniffing can be attempted \cite{filizzola2018security} \cite{osullivan}.
+Finally, the protocol could be reverse engineered to try and find vulnerabilities in the implementation.
+
+The primary RFID attack is cloning, it is possible to try to prevent cloning though it is very hard \cite{7888545} \cite{dijkPortableBumping} \cite{mitrokotsa09} \cite{7945583}.
+Secondly, the random number generator used for RFID cards can be tested for vulnerabilities \cite{6565237} \cite{mitrokotsa09}.
+A third possible set of attacks is to try passive and active relay against the reader \cite{hancke2009confidence} \cite{6810722}.
+Another possibility is to examine the RFID card reader for possible injection attacks and remote code execution \cite{garciaIClass}.
+The final attack method would be to attack the RFID chain of trust used in the reader \cite{lehtonen07}.
+
+The Wiegand protocol attacks are relatively simple.
+The first step of the attack chain is to analyze the various Wiegand outputs of the reader.
+After a large enough scans have been made interception and duplication attacks can be made \cite{chung2017wiegand}.
+Finally, a BLEKey \cite{baseggio2015BLEKey} or similar device can be made and tested against the reader.
+As a part of the Wiegand testing, attacks against the optical tamper sensor will need to be created and tested.
+
+These three sets of attacks will cover a large amount of the reader's attack surface.
+The particular kill chains are ordered to effectively build off of previous steps and to test the easier attacks before the more complicated ones.
+The order also is set so that the possible dangerous attacks that could damage the device are run last.
 
 \subsection{Timeline}
-Words
-
-\subsection{Novel Techniques}
-Words
+The timeline for this project assumes a eight week period for testing.
+This eight week period will be broken up into five separate stages for setup, testing, and wrapup.
+Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.
+The first period is one week long and dedicated to setup.
+During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.
+The second period is two weeks in length and dedicated to testing RFID.
+The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.
+The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.
+The fifth and final period is one week in length, unlike the others this period is not for testing.
+The last period is dedicated to writing the report to submit to Carrier for their review.
 
@@
 \section{Acknowledgements}
-We would like to thank Lenel for access to their BlueDiamond reader and their permission to conduct a test of the reader's security posture.
+We would like to thank Carrier for access to their BlueDiamond reader and their permission to conduct a test of the reader's security posture.
 

### 2020-05-06 paper/paper/paper.tex
Implications done

@@
 \section{Preliminary Suppositions \& Implications}
-Words
+A lot of research appears to be out of date in the field of lock security.
+
+This research will cover Lenel/BlueDiamond's particular implementation of BLE, which to the author's knowledge has not been tested in an academic environment before.
+
+This research will extend the Wiegand research prior by attacking newer hardware with better security features.
 
 \subsection{Theoretical Implications}
-Words
+Vulnerabilities present in BLE/RFID/Weigand will be further reaffirmed.
+
+The failure of manufacturers to implement up to date security features in the latest version of BLE/RFID/Weigand will be known.
+
+This research has the potential to affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
+
+If critical vulnerabilities are discovered, these vulnerabilities could potentially be used to take over many organizations that rely on Lenel/BlueDiamond technology for access control.
 
 \subsection{Practical Implications}
-Words
+This research will confirm whether Lenel’s security posture is excellent, average, or bad.
+
+Any vulnerabilities discovered during the testing of this research will be handed over to Lenel for analysis and patching.
+
+Lenel’s security posture will be improved due to outsider knowledge in this research not present inside Lenel.
+
+This research will provide a baseline for future work in evaluating locks from different vendors.
+
+If any critical vulnerabilities are discovered but not swiftly dealt with Lenel’s reputation may lower.
 

### 2020-05-06 paper/paper/paper.tex

--- 2020-05-05 paper/paper/paper.tex
@@
 \section{Preliminary Suppositions \& Implications}
-Words
+This reasearch will expand and refine on the current work available on Lenel readers and readers in general.
+While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication.
+We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them.
+In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}.
+Our work will allow for the creating of a preliminary attack chain for these protocols.
 
-\subsection{Theoretical Implications}
-Words
+Existing attack chains against BLE will also be refined.
+We have seen these chains demonstrated \cite{lonzetta2018security}\cite{BluetoothMITMTal} already, but not laid out and explored beyond simply using the tools.
+These processes and procedures can be laid out and refined in this research allowing for a properly documented attack chain.
 
-\subsection{Practical Implications}
-Words
+Finally, the security of the Lenel BlueDiamond will be affirmed.
+Our testing will allow for third party confirmation that these devices are secure against attacks.
+Lenel will benefit from outsider knowledge that is not present in institutional knowledge.
 

### 2020-05-06 paper/paper/paper.tex
first draft of research design. I think i needs more but starting here

--- 2020-05-05 paper/paper/paper.tex
@@
 As such, the technology continues to advance as companies come up with newer, more advanced, ways to authenticate securely.
-In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." \cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
+In recent years, Lenel corporations has released multiple products under the BlueDiamond name that claim to "enhance freedom of movement in the workplace." /cite{lenelbluediamondwebsite} To date, these devices remain untested by the further research community for vulnerabilities that may lead to a breach of access control.
 As such, this paper aims to design an experimental process that future researchers may follow to accurately assess the security characteristics of Lenel's BlueDiamond contactless readers.
@@
 \section{Background \& Significance}
-Words
 
@@
 
-It can be seen in the literature on BLE is very vulnerable to man-in-the-middle attacks, denial of service, packet sniffing, and other attacks.
+It can be seen in the literature on BLE is very vulnerable to man-in-the-middle attacks, denial of service, packet sniffing, and other vulnerabilities.
 Even though higher levels of security are included in newer BLE versions, such as ECC or out-of-band key exchanges, security settings like PINs are still used by manufacturers \cite{8622000}\cite{jaihc19}\cite{mryan13}.
@@
 \section{Research Design \& Methodology}
-Words
+Our research seeks to analyze the security posture of the readers as they would appear in a customer environment.
+As such, our research design follows a quasi-experimental structure, meaning only pre-existing configurations of the reader will be studied.
+Setup of the reader for testing will require connecting the power and ground wires to a 12v power source and the D0, D1, and tamper wires to a raspberry pi.
+Interfacing with a raspberry pi allows researchers flexible access to perform multiple different tasks such as collecting data or changing configurations.
+Researchers may also choose to set up the BlueDiamond mobile app to allow the ability for testing bluetooth traffic sent and received by the device.
+The attack vector serves as a variable in this equation as its outcome can be scored against others using a common standard.
+Observations of consistency, difficulty, and threat level will allow us to score each attack vector using the Common Vulnerability Scoring System (CVSS) \cite{cvss}.
 
@@
 \subsection{Procedures}
-The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.
-These categories will follow logical attack chains to test a variety of vulnerabilites.
-
-The Bluetooth procedures follow a primary attack chain to test for vulnerabilities.
-The chain starts with either gattacker \cite{GattackingJasek} \cite{BluetoothMITMTal} or CrackLE \cite{10.1145/3190645.3190693} to gain an initial foothold.
-From there, the next step is to test for either injection attacks or injection free attacks \cite{jaihc19} to clear the binding list.
-After the binding list is cleared a man-in-the-middle attack can be attempted \cite{lonzetta2018security} \cite{osullivan} \cite{BluetoothMITMTal}.
-From this point there are multiple attacks that can be attempted.
-The first attack is to attempt to break the long-term key by brute forcing the term key \cite{sevier2019securityofble} \cite{179196}.
-After this replay attacks and active sniffing can be attempted \cite{filizzola2018security} \cite{osullivan}.
-Finally, the protocol could be reverse engineered to try and find vulnerabilities in the implementation.
-
-The primary RFID attack is cloning, it is possible to try to prevent cloning though it is very hard \cite{7888545} \cite{dijkPortableBumping} \cite{mitrokotsa09} \cite{7945583}.
-Secondly, the random number generator used for RFID cards can be tested for vulnerabilities \cite{6565237} \cite{mitrokotsa09}.
-A third possible set of attacks is to try passive and active relay against the reader \cite{hancke2009confidence} \cite{6810722}.
-Another possibility is to examine the RFID card reader for possible injection attacks and remote code execution \cite{garciaIClass}.
-The final attack method would be to attack the RFID chain of trust used in the reader \cite{lehtonen07}.
-
-The Wiegand protocol attacks are relatively simple.
-The first step of the attack chain is to analyze the various Wiegand outputs of the reader.
-After a large enough scans have been made interception and duplication attacks can be made \cite{chung2017wiegand}.
-Finally, a BLEKey \cite{baseggio2015BLEKey} or similar device can be made and tested against the reader.
-As a part of the Wiegand testing, attacks against the optical tamper sensor will need to be created and tested.
-
-These three sets of attacks will cover a large amount of the reader's attack surface.
-The particular kill chains are ordered to effectively build off of previous steps and to test the easier attacks before the more complicated ones.
-The order also is set so that the possible dangerous attacks that could damage the device are run last.
+Words
 
 \subsection{Timeline}
-The timeline for this project assumes a eight week period for testing.
-This eight week period will be broken up into five separate stages for setup, testing, and wrapup.
-Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.
-The first period is one week long and dedicated to setup.
-During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.
-The second period is two weeks in length and dedicated to testing RFID.
-The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.
-The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.
-The fifth and final period is one week in length, unlike the others this period is not for testing.
-The last period is dedicated to writing the report to submit to Carrier for their review.
+Words
+
+\subsection{Novel Techniques}
+Words
 
@@
 \section{Acknowledgements}
-We would like to thank Carrier for access to their BlueDiamond reader and their permission to conduct a test of the reader's security posture.
+We would like to thank Lenel for access to their BlueDiamond reader and their permission to conduct a test of the reader's security posture.
 

### 2020-05-06 paper/paper/paper.tex
added mention of wiegand connection.
Added initial background

@@
 \section{Background \& Significance}
+Throughout history, people have tried to gain access restricted areas.
+\cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.
+The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.
+Bramah had just developed his so called safety lock.
+His lock had safety features that he believed to be completely secure.
+Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.
+Anyone who could break into his new creation would net a cool sum of 20,000 pounds.
+
+While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.
+Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.
+He too, announced a challnge.
+An American Locksmith named A.C.
+Hobbs took up the challenge, and had it open within an hour of touching the lock.
+However, that wasn't the only challenge he accepted.
+Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.
+
+New technology leads to new innovation.
+Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.
+Granting access to a building is as simple as a few button clicks.
+For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.
+
+Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.
+With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.
+These locks aren't invulnerable, but security professionals can certainly help bring them to the point where they can withstand basic attacks.
 
@@
 Interfacing with a raspberry pi allows researchers flexible access to perform multiple different tasks such as collecting data or changing configurations.
+Our proposed connection will allow for easy analysis of the Wiegand hardware within the device.
 Researchers may also choose to set up the BlueDiamond mobile app to allow the ability for testing bluetooth traffic sent and received by the device.

### 2020-05-06 paper/paper/paper.tex
Fixed references, added beginning of expected outcomes

@@
 \section{Expected Outcomes}
-Words
+Not every penetration test finds a massive zero day vulnerability.
+However, that doesn't mean a test isn't completely useless.
+Tests may not often discover massive issues, but smaller issues are often prevalent.
+Issues such as weaker cryptography, bad hardware intrusion detection, and magnetic locking overrides are common in locking hardware.
 
@@
 
-\bibliographystyle{ieee}
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2020-05-06 paper/paper/paper.tex
manually added changes from clev-dev

--- 2020-05-06 paper/paper/paper.tex
@@
 \subsection{Procedures}
-Words
+The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.
+These categories will follow logical attack chains to test a variety of vulnerabilites.
+
+The Bluetooth procedures follow a primary attack chain to test for vulnerabilities.
+The chain starts with either gattacker \cite{GattackingJasek} \cite{BluetoothMITMTal} or CrackLE \cite{10.1145/3190645.3190693} to gain an initial foothold.
+From there, the next step is to test for either injection attacks or injection free attacks \cite{jaihc19} to clear the binding list.
+After the binding list is cleared a man-in-the-middle attack can be attempted \cite{lonzetta2018security} \cite{osullivan} \cite{BluetoothMITMTal}.
+From this point there are multiple attacks that can be attempted.
+The first attack is to attempt to break the long-term key by brute forcing the term key \cite{sevier2019securityofble} \cite{179196}.
+After this replay attacks and active sniffing can be attempted \cite{filizzola2018security} \cite{osullivan}.
+Finally, the protocol could be reverse engineered to try and find vulnerabilities in the implementation.
+
+The primary RFID attack is cloning, it is possible to try to prevent cloning though it is very hard \cite{7888545} \cite{dijkPortableBumping} \cite{mitrokotsa09} \cite{7945583}.
+Secondly, the random number generator used for RFID cards can be tested for vulnerabilities \cite{6565237} \cite{mitrokotsa09}.
+A third possible set of attacks is to try passive and active relay against the reader \cite{hancke2009confidence} \cite{6810722}.
+Another possibility is to examine the RFID card reader for possible injection attacks and remote code execution \cite{garciaIClass}.
+The final attack method would be to attack the RFID chain of trust used in the reader \cite{lehtonen07}.
+
+The Wiegand protocol attacks are relatively simple.
+The first step of the attack chain is to analyze the various Wiegand outputs of the reader.
+After a large enough scans have been made interception and duplication attacks can be made \cite{chung2017wiegand}.
+Finally, a BLEKey \cite{baseggio2015BLEKey} or similar device can be made and tested against the reader.
+As a part of the Wiegand testing, attacks against the optical tamper sensor will need to be created and tested.
+
+These three sets of attacks will cover a large amount of the reader's attack surface.
+The particular kill chains are ordered to effectively build off of previous steps and to test the easier attacks before the more complicated ones.
+The order also is set so that the possible dangerous attacks that could damage the device are run last.
 
 \subsection{Timeline}
-Words
-
-\subsection{Novel Techniques}
-Words
+The timeline for this project assumes a eight week period for testing.
+This eight week period will be broken up into five separate stages for setup, testing, and wrapup.
+Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.
+The first period is one week long and dedicated to setup.
+During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.
+The second period is two weeks in length and dedicated to testing RFID.
+The third period is also two weeks in length, this is dedicated to testing for Bluetooth weaknesses.
+The fourth period is the final two week period, this time dedicated to testing for Wiegand vulnerabilities.
+The fifth and final period is one week in length, unlike the others this period is not for testing.
+The last period is dedicated to writing the report to submit to Carrier for their review.
 
 \section{Preliminary Suppositions \& Implications}
-Words
+This reasearch will expand and refine on the current work available on Lenel readers and readers in general.
+While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication.
+We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them.
+In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}.
+Our work will allow for the creating of a preliminary attack chain for these protocols.
 
 \subsection{Theoretical Implications}
-Words
+Existing attack chains against BLE will also be refined.
+We have seen these chains demonstrated \cite{lonzetta2018security}\cite{BluetoothMITMTal} already, but not laid out and explored beyond simply using the tools.
+These processes and procedures can be laid out and refined in this research allowing for a properly documented attack chain.
 
 \subsection{Practical Implications}
-Words
+Finally, the security of the Lenel BlueDiamond will be affirmed.
+Our testing will allow for third party confirmation that these devices are secure against attacks.
+Lenel will benefit from outsider knowledge that is not present in institutional knowledge.
 

### 2020-05-06 paper/paper/paper.tex
Draft for conclusions/expected outcomes

--- 2020-05-06 paper/paper/paper.tex
@@
 With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.
-These locks aren't invulnerable, but security professionals can certainly help bring them to the point where they can withstand basic attacks.
+These locks aren't invulnerable, and security professionals can certainly help bring them to the point where they can withstand basic attacks.
 
@@
 Tests may not often discover massive issues, but smaller issues are often prevalent.
-Issues such as weaker cryptography, bad hardware intrusion detection, and magnetic locking overrides are common in locking hardware.
+Issues such as weaker cryptography, issues with bad hardware intrusion detection, and bad endpoint security on older protocols are commonplace.
+It should be expected to find several smaller issues rather than major flaws in the firmware or the device itself.
+
+Overall, the authors expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.
+Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.
 
 \section{Conclusions}
-Words
+Throughout this paper, the authors have discussed how to design a testing framework for attacking modern electronic locking technologies.
+The authors listed out different types of attacks that could be run against a bluetooth-enabled locking solution.
+Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.
+
+We also discussed attacking the device from the backend, from the protocols that allow for the lock to communicate securely with an authentication server.
+This includes the Wiegand protocol, which is not designed with a security focus in mind.
+
+Lock picking may not yet be on the decline, but electronic locking mechanisms allow for greater viability for most organizations.
+Overall, electronic locking solutions will be used far into the future.
+It's heavily important to test these locks to verify that the cryptographic and security mechanisms of these locks are structurally sound.
 

### 2020-05-06 paper/paper/paper.tex
removed 'the authors'

@@
 
-Overall, the authors expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.
+Overall, we expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.
 Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.
@@
 \section{Conclusions}
-Throughout this paper, the authors have discussed how to design a testing framework for attacking modern electronic locking technologies.
-The authors listed out different types of attacks that could be run against a bluetooth-enabled locking solution.
+Throughout this paper, we have discussed how to design a testing framework for attacking modern electronic locking technologies.
+We listed out different types of attacks that could be run against a bluetooth-enabled locking solution.
 Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.

### 2020-05-06 paper/paper/paper.tex

--- 2020-05-06 paper/paper/paper.tex
@@
 \section{Background \& Significance}
+Throughout history, people have tried to gain access restricted areas.
+\cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.
+The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.
+Bramah had just developed his so called safety lock.
+His lock had safety features that he believed to be completely secure.
+Obviously, nothing is ever completely secure, but Bramah put it to the test by announcing a contest.
+Anyone who could break into his new creation would net a cool sum of 20,000 pounds.
+
+While the Bramah challenge was still in place, another locksmith caught wind of Bramah's idea.
+Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.
+He too, announced a challnge.
+An American Locksmith named A.C.
+Hobbs took up the challenge, and had it open within an hour of touching the lock.
+However, that wasn't the only challenge he accepted.
+Chubb took a trip over to Hobbs' locksmithing shop, and 70 years later, picked the Bramah security lock.
+
+New technology leads to new innovation.
+Almost overnight, businesses and organizations started using electronic locking systems for their ease of use and simplicity in granting or denying access.
+Granting access to a building is as simple as a few button clicks.
+For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.
+
+Lock Picking may be a thing of the past, but the security of electronic locks still need to be audited.
+With most RFID-based systems, like those in locks, cloning cards is easier than ever due to new tools like the ProxMark RFID toolkit.\cite{7945583}  Even though the physical element of locks and lock picking may not stay the same with these newer electronic locking systems, the spirit stays alive in the hacking community.
+These locks aren't invulnerable, and security professionals can certainly help bring them to the point where they can withstand basic attacks.
 
@@
 \section{Expected Outcomes}
-Words
+Not every penetration test finds a massive zero day vulnerability.
+However, that doesn't mean a test isn't completely useless.
+Tests may not often discover massive issues, but smaller issues are often prevalent.
+Issues such as weaker cryptography, issues with bad hardware intrusion detection, and bad endpoint security on older protocols are commonplace.
+It should be expected to find several smaller issues rather than major flaws in the firmware or the device itself.
+
+Overall, we expect such a test to provide a concrete and detailed analysis on the Physical, Weigand, RFID, Bluetooth, and Networking stacks embedded in the device.
+Such a test would outline how these protocols work on a device, and provide concrete analysis of potential vulnerabilities and weaknesses found in the implementation.
 
 \section{Conclusions}
-Words
+Throughout this paper, we have discussed how to design a testing framework for attacking modern electronic locking technologies.
+We listed out different types of attacks that could be run against a bluetooth-enabled locking solution.
+Bluetooth attacks were discussed, along with RFID attacks, and the cryptographic attacks underneath both attack vectors.
+
+We also discussed attacking the device from the backend, from the protocols that allow for the lock to communicate securely with an authentication server.
+This includes the Wiegand protocol, which is not designed with a security focus in mind.
+
+Lock picking may not yet be on the decline, but electronic locking mechanisms allow for greater viability for most organizations.
+Overall, electronic locking solutions will be used far into the future.
+It's heavily important to test these locks to verify that the cryptographic and security mechanisms of these locks are structurally sound.
 

### 2020-05-07 paper/paper/paper.tex
fixing minor issues

@@
 \section{Background \& Significance}
-Throughout history, people have tried to gain access restricted areas.
+Throughout history, people have tried to gain access to restricted areas.
 \cite{lockpickinghistory}  Locks were created in order to restrict access, but locksmiths were often skeptical of their inventions, and if they could be bypassed.
-The first documented case of lock picking was a challenge released by Joseph Bramah, an Enlish locksmith.
-Bramah had just developed his so called safety lock.
+The first documented case of lock picking was a challenge released by Joseph Bramah, an English locksmith.
+Bramah had just developed his so-called safety lock.
 His lock had safety features that he believed to be completely secure.
@@
 Jeremiah Chubb built a lock that would alert an owner if any sort of picking had been detected.
-He too, announced a challnge.
+He too, announced a challenge.
 An American Locksmith named A.C.
@@
 Granting access to a building is as simple as a few button clicks.
-For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to re-key a lock every single time an employee leaves the organization.
+For most organizations, it is much easier to spend the extra money for a digital system with computer-controlled access control than to rekey a lock every single time an employee leaves the organization.
 
@@
 An attacker can intercept and then duplicate the signals sent by a Wiegand device to the control server.
-This attack can capture and repeat and authorized card without needing to physically duplicate the card \cite{chung2017wiegand}.
+This attack can capture and repeat an authorized card without needing to physically duplicate the card \cite{chung2017wiegand}.
 Hakamaki and Palomaki discuss a number of existing RFID attacks that still exist in modern RFID readers \cite{rfid15}.
@@
 As this is primarily a penetration test of the Lenel BlueDiamond, there are four quantitative metrics of note: number of vulnerabilities, severity, likelihood, and risk.
-A vulnerability is counted if it could be exploited for an unintened effect.
+A vulnerability is counted if it could be exploited for an unintended effect.
 The severity, likelihood, and risk can be properly measured by the Common Vulnerability Scoring System, or CVSS 3.x.
 This would allow for a more uniform scoring standard inline with what the industry uses.
-Vulnerabilties will be discovered by a number of tools, including devices like the Ubertooth, manual tool usage, and fuzzing.
+Vulnerabilities will be discovered by a number of tools, including devices like the Ubertooth, manual tool usage, and fuzzing.
 Vulnerabilities found would be sorted based on protocol and CVSS score.
@@
 The testing performed against the readers would be broken into three primary categories: Bluetooth, RFID, and Wiegand.
-These categories will follow logical attack chains to test a variety of vulnerabilites.
+These categories will follow logical attack chains to test a variety of vulnerabilities.
 
@@
 \subsection{Timeline}
-The timeline for this project assumes a eight week period for testing.
-This eight week period will be broken up into five separate stages for setup, testing, and wrapup.
+The timeline for this project assumes an eight week period for testing.
+This eight week period will be broken up into five separate stages for setup, testing, and wrap up.
 Eight weeks should be more than adequate to perform the necessary testing and provide a complete report.
-The first period is one week long and dedicated to setup.
+The first period is one week long and dedicated to set up.
 During this time a test lab would be built with the necessary equipment to test RFID, Bluetooth, and Wiegand.
@@
 \section{Preliminary Suppositions \& Implications}
-This reasearch will expand and refine on the current work available on Lenel readers and readers in general.
+This research will expand and refine on the current work available on Lenel readers and readers in general.
 While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication.
-We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them.
+We have a opportunity to add insight on examining multi-protocol readers and how to approached examining and attacking them.
 In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}.
